\section{Debugger}\label{debugger}

\begin{quote}
Stability: 2 - Stable
\end{quote}

Node.js includes a command-line debugging utility. The Node.js debugger
client is not a full-featured debugger, but simple stepping and
inspection are possible.

To use it, start Node.js with the \texttt{inspect} argument followed by
the path to the script to debug.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ node inspect myscript.js}
\NormalTok{\textless{} Debugger listening on ws://127.0.0.1:9229/621111f9{-}ffcb{-}4e82{-}b718{-}48a145fa5db8}
\NormalTok{\textless{} For help, see: https://nodejs.org/en/docs/inspector}
\NormalTok{\textless{}}
\NormalTok{connecting to 127.0.0.1:9229 ... ok}
\NormalTok{\textless{} Debugger attached.}
\NormalTok{\textless{}}
\NormalTok{ ok}
\NormalTok{Break on start in myscript.js:2}
\NormalTok{  1 // myscript.js}
\NormalTok{\textgreater{} 2 global.x = 5;}
\NormalTok{  3 setTimeout(() =\textgreater{} \{}
\NormalTok{  4   debugger;}
\NormalTok{debug\textgreater{}}
\end{Highlighting}
\end{Shaded}

The debugger automatically breaks on the first executable line. To
instead run until the first breakpoint (specified by a
\href{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/debugger}{\texttt{debugger}}
statement), set the \texttt{NODE\_INSPECT\_RESUME\_ON\_START}
environment variable to \texttt{1}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ cat myscript.js}
\NormalTok{// myscript.js}
\NormalTok{global.x = 5;}
\NormalTok{setTimeout(() =\textgreater{} \{}
\NormalTok{  debugger;}
\NormalTok{  console.log(\textquotesingle{}world\textquotesingle{});}
\NormalTok{\}, 1000);}
\NormalTok{console.log(\textquotesingle{}hello\textquotesingle{});}
\NormalTok{$ NODE\_INSPECT\_RESUME\_ON\_START=1 node inspect myscript.js}
\NormalTok{\textless{} Debugger listening on ws://127.0.0.1:9229/f1ed133e{-}7876{-}495b{-}83ae{-}c32c6fc319c2}
\NormalTok{\textless{} For help, see: https://nodejs.org/en/docs/inspector}
\NormalTok{\textless{}}
\NormalTok{connecting to 127.0.0.1:9229 ... ok}
\NormalTok{\textless{} Debugger attached.}
\NormalTok{\textless{}}
\NormalTok{\textless{} hello}
\NormalTok{\textless{}}
\NormalTok{break in myscript.js:4}
\NormalTok{  2 global.x = 5;}
\NormalTok{  3 setTimeout(() =\textgreater{} \{}
\NormalTok{\textgreater{} 4   debugger;}
\NormalTok{  5   console.log(\textquotesingle{}world\textquotesingle{});}
\NormalTok{  6 \}, 1000);}
\NormalTok{debug\textgreater{} next}
\NormalTok{break in myscript.js:5}
\NormalTok{  3 setTimeout(() =\textgreater{} \{}
\NormalTok{  4   debugger;}
\NormalTok{\textgreater{} 5   console.log(\textquotesingle{}world\textquotesingle{});}
\NormalTok{  6 \}, 1000);}
\NormalTok{  7 console.log(\textquotesingle{}hello\textquotesingle{});}
\NormalTok{debug\textgreater{} repl}
\NormalTok{Press Ctrl+C to leave debug repl}
\NormalTok{\textgreater{} x}
\NormalTok{5}
\NormalTok{\textgreater{} 2 + 2}
\NormalTok{4}
\NormalTok{debug\textgreater{} next}
\NormalTok{\textless{} world}
\NormalTok{\textless{}}
\NormalTok{break in myscript.js:6}
\NormalTok{  4   debugger;}
\NormalTok{  5   console.log(\textquotesingle{}world\textquotesingle{});}
\NormalTok{\textgreater{} 6 \}, 1000);}
\NormalTok{  7 console.log(\textquotesingle{}hello\textquotesingle{});}
\NormalTok{  8}
\NormalTok{debug\textgreater{} .exit}
\NormalTok{$}
\end{Highlighting}
\end{Shaded}

The \texttt{repl} command allows code to be evaluated remotely. The
\texttt{next} command steps to the next line. Type \texttt{help} to see
what other commands are available.

Pressing \texttt{enter} without typing a command will repeat the
previous debugger command.

\subsection{Watchers}\label{watchers}

It is possible to watch expression and variable values while debugging.
On every breakpoint, each expression from the watchers list will be
evaluated in the current context and displayed immediately before the
breakpoint's source code listing.

To begin watching an expression, type
\texttt{watch(\textquotesingle{}my\_expression\textquotesingle{})}. The
command \texttt{watchers} will print the active watchers. To remove a
watcher, type
\texttt{unwatch(\textquotesingle{}my\_expression\textquotesingle{})}.

\subsection{Command reference}\label{command-reference}

\subsubsection{Stepping}\label{stepping}

\begin{itemize}
\tightlist
\item
  \texttt{cont}, \texttt{c}: Continue execution
\item
  \texttt{next}, \texttt{n}: Step next
\item
  \texttt{step}, \texttt{s}: Step in
\item
  \texttt{out}, \texttt{o}: Step out
\item
  \texttt{pause}: Pause running code (like pause button in Developer
  Tools)
\end{itemize}

\subsubsection{Breakpoints}\label{breakpoints}

\begin{itemize}
\tightlist
\item
  \texttt{setBreakpoint()}, \texttt{sb()}: Set breakpoint on current
  line
\item
  \texttt{setBreakpoint(line)}, \texttt{sb(line)}: Set breakpoint on
  specific line
\item
  \texttt{setBreakpoint(\textquotesingle{}fn()\textquotesingle{})},
  \texttt{sb(...)}: Set breakpoint on a first statement in function's
  body
\item
  \texttt{setBreakpoint(\textquotesingle{}script.js\textquotesingle{},\ 1)},
  \texttt{sb(...)}: Set breakpoint on first line of \texttt{script.js}
\item
  \texttt{setBreakpoint(\textquotesingle{}script.js\textquotesingle{},\ 1,\ \textquotesingle{}num\ \textless{}\ 4\textquotesingle{})},
  \texttt{sb(...)}: Set conditional breakpoint on first line of
  \texttt{script.js} that only breaks when \texttt{num\ \textless{}\ 4}
  evaluates to \texttt{true}
\item
  \texttt{clearBreakpoint(\textquotesingle{}script.js\textquotesingle{},\ 1)},
  \texttt{cb(...)}: Clear breakpoint in \texttt{script.js} on line 1
\end{itemize}

It is also possible to set a breakpoint in a file (module) that is not
loaded yet:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ node inspect main.js}
\NormalTok{\textless{} Debugger listening on ws://127.0.0.1:9229/48a5b28a{-}550c{-}471b{-}b5e1{-}d13dd7165df9}
\NormalTok{\textless{} For help, see: https://nodejs.org/en/docs/inspector}
\NormalTok{\textless{}}
\NormalTok{connecting to 127.0.0.1:9229 ... ok}
\NormalTok{\textless{} Debugger attached.}
\NormalTok{\textless{}}
\NormalTok{Break on start in main.js:1}
\NormalTok{\textgreater{} 1 const mod = require(\textquotesingle{}./mod.js\textquotesingle{});}
\NormalTok{  2 mod.hello();}
\NormalTok{  3 mod.hello();}
\NormalTok{debug\textgreater{} setBreakpoint(\textquotesingle{}mod.js\textquotesingle{}, 22)}
\NormalTok{Warning: script \textquotesingle{}mod.js\textquotesingle{} was not loaded yet.}
\NormalTok{debug\textgreater{} c}
\NormalTok{break in mod.js:22}
\NormalTok{ 20 // USE OR OTHER DEALINGS IN THE SOFTWARE.}
\NormalTok{ 21}
\NormalTok{\textgreater{}22 exports.hello = function() \{}
\NormalTok{ 23   return \textquotesingle{}hello from module\textquotesingle{};}
\NormalTok{ 24 \};}
\NormalTok{debug\textgreater{}}
\end{Highlighting}
\end{Shaded}

It is also possible to set a conditional breakpoint that only breaks
when a given expression evaluates to \texttt{true}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ node inspect main.js}
\NormalTok{\textless{} Debugger listening on ws://127.0.0.1:9229/ce24daa8{-}3816{-}44d4{-}b8ab{-}8273c8a66d35}
\NormalTok{\textless{} For help, see: https://nodejs.org/en/docs/inspector}
\NormalTok{\textless{}}
\NormalTok{connecting to 127.0.0.1:9229 ... ok}
\NormalTok{\textless{} Debugger attached.}
\NormalTok{Break on start in main.js:7}
\NormalTok{  5 \}}
\NormalTok{  6}
\NormalTok{\textgreater{} 7 addOne(10);}
\NormalTok{  8 addOne({-}1);}
\NormalTok{  9}
\NormalTok{debug\textgreater{} setBreakpoint(\textquotesingle{}main.js\textquotesingle{}, 4, \textquotesingle{}num \textless{} 0\textquotesingle{})}
\NormalTok{  1 \textquotesingle{}use strict\textquotesingle{};}
\NormalTok{  2}
\NormalTok{  3 function addOne(num) \{}
\NormalTok{\textgreater{} 4   return num + 1;}
\NormalTok{  5 \}}
\NormalTok{  6}
\NormalTok{  7 addOne(10);}
\NormalTok{  8 addOne({-}1);}
\NormalTok{  9}
\NormalTok{debug\textgreater{} cont}
\NormalTok{break in main.js:4}
\NormalTok{  2}
\NormalTok{  3 function addOne(num) \{}
\NormalTok{\textgreater{} 4   return num + 1;}
\NormalTok{  5 \}}
\NormalTok{  6}
\NormalTok{debug\textgreater{} exec(\textquotesingle{}num\textquotesingle{})}
\NormalTok{{-}1}
\NormalTok{debug\textgreater{}}
\end{Highlighting}
\end{Shaded}

\subsubsection{Information}\label{information}

\begin{itemize}
\tightlist
\item
  \texttt{backtrace}, \texttt{bt}: Print backtrace of current execution
  frame
\item
  \texttt{list(5)}: List scripts source code with 5 line context (5
  lines before and after)
\item
  \texttt{watch(expr)}: Add expression to watch list
\item
  \texttt{unwatch(expr)}: Remove expression from watch list
\item
  \texttt{unwatch(index)}: Remove expression at specific index from
  watch list
\item
  \texttt{watchers}: List all watchers and their values (automatically
  listed on each breakpoint)
\item
  \texttt{repl}: Open debugger's repl for evaluation in debugging
  script's context
\item
  \texttt{exec\ expr}, \texttt{p\ expr}: Execute an expression in
  debugging script's context and print its value
\item
  \texttt{profile}: Start CPU profiling session
\item
  \texttt{profileEnd}: Stop current CPU profiling session
\item
  \texttt{profiles}: List all completed CPU profiling sessions
\item
  \texttt{profiles{[}n{]}.save(filepath\ =\ \textquotesingle{}node.cpuprofile\textquotesingle{})}:
  Save CPU profiling session to disk as JSON
\item
  \texttt{takeHeapSnapshot(filepath\ =\ \textquotesingle{}node.heapsnapshot\textquotesingle{})}:
  Take a heap snapshot and save to disk as JSON
\end{itemize}

\subsubsection{Execution control}\label{execution-control}

\begin{itemize}
\tightlist
\item
  \texttt{run}: Run script (automatically runs on debugger's start)
\item
  \texttt{restart}: Restart script
\item
  \texttt{kill}: Kill script
\end{itemize}

\subsubsection{Various}\label{various}

\begin{itemize}
\tightlist
\item
  \texttt{scripts}: List all loaded scripts
\item
  \texttt{version}: Display V8's version
\end{itemize}

\subsection{Advanced usage}\label{advanced-usage}

\subsubsection{V8 inspector integration for
Node.js}\label{v8-inspector-integration-for-node.js}

V8 Inspector integration allows attaching Chrome DevTools to Node.js
instances for debugging and profiling. It uses the
\href{https://chromedevtools.github.io/devtools-protocol/}{Chrome
DevTools Protocol}.

V8 Inspector can be enabled by passing the \texttt{-\/-inspect} flag
when starting a Node.js application. It is also possible to supply a
custom port with that flag, e.g.~\texttt{-\/-inspect=9222} will accept
DevTools connections on port 9222.

To break on the first line of the application code, pass the
\texttt{-\/-inspect-brk} flag instead of \texttt{-\/-inspect}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ node {-}{-}inspect index.js}
\NormalTok{Debugger listening on ws://127.0.0.1:9229/dc9010dd{-}f8b8{-}4ac5{-}a510{-}c1a114ec7d29}
\NormalTok{For help, see: https://nodejs.org/en/docs/inspector}
\end{Highlighting}
\end{Shaded}

(In the example above, the UUID dc9010dd-f8b8-4ac5-a510-c1a114ec7d29 at
the end of the URL is generated on the fly, it varies in different
debugging sessions.)

If the Chrome browser is older than 66.0.3345.0, use
\texttt{inspector.html} instead of \texttt{js\_app.html} in the above
URL.

Chrome DevTools doesn't support debugging
\href{worker_threads.md}{worker threads} yet.
\href{https://github.com/GoogleChromeLabs/ndb/}{ndb} can be used to
debug them.
