\section{Global objects}\label{global-objects}

These objects are available in all modules. The following variables may
appear to be global but are not. They exist only in the scope of
modules, see the \href{modules.md}{module system documentation}:

\begin{itemize}
\tightlist
\item
  \href{modules.md\#__dirname}{\texttt{\_\_dirname}}
\item
  \href{modules.md\#__filename}{\texttt{\_\_filename}}
\item
  \href{modules.md\#exports}{\texttt{exports}}
\item
  \href{modules.md\#module}{\texttt{module}}
\item
  \href{modules.md\#requireid}{\texttt{require()}}
\end{itemize}

The objects listed here are specific to Node.js. There are
\href{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global_Objects}{built-in
objects} that are part of the JavaScript language itself, which are also
globally accessible.

\subsection{\texorpdfstring{Class:
\texttt{AbortController}}{Class: AbortController}}\label{class-abortcontroller}

A utility class used to signal cancelation in selected
\texttt{Promise}-based APIs. The API is based on the Web API
\href{https://developer.mozilla.org/en-US/docs/Web/API/AbortController}{\texttt{AbortController}}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ ac }\OperatorTok{=} \KeywordTok{new} \FunctionTok{AbortController}\NormalTok{()}\OperatorTok{;}

\NormalTok{ac}\OperatorTok{.}\AttributeTok{signal}\OperatorTok{.}\FunctionTok{addEventListener}\NormalTok{(}\StringTok{\textquotesingle{}abort\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}} \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}Aborted!\textquotesingle{}}\NormalTok{)}\OperatorTok{,}
\NormalTok{                           \{ }\DataTypeTok{once}\OperatorTok{:} \KeywordTok{true}\NormalTok{ \})}\OperatorTok{;}

\NormalTok{ac}\OperatorTok{.}\FunctionTok{abort}\NormalTok{()}\OperatorTok{;}

\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(ac}\OperatorTok{.}\AttributeTok{signal}\OperatorTok{.}\AttributeTok{aborted}\NormalTok{)}\OperatorTok{;}  \CommentTok{// Prints true}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{abortController.abort({[}reason{]})}}{abortController.abort({[}reason{]})}}\label{abortcontroller.abortreason}

\begin{itemize}
\tightlist
\item
  \texttt{reason} \{any\} An optional reason, retrievable on the
  \texttt{AbortSignal}'s \texttt{reason} property.
\end{itemize}

Triggers the abort signal, causing the \texttt{abortController.signal}
to emit the \texttt{\textquotesingle{}abort\textquotesingle{}} event.

\subsubsection{\texorpdfstring{\texttt{abortController.signal}}{abortController.signal}}\label{abortcontroller.signal}

\begin{itemize}
\tightlist
\item
  Type: \{AbortSignal\}
\end{itemize}

\subsubsection{\texorpdfstring{Class:
\texttt{AbortSignal}}{Class: AbortSignal}}\label{class-abortsignal}

\begin{itemize}
\tightlist
\item
  Extends: \{EventTarget\}
\end{itemize}

The \texttt{AbortSignal} is used to notify observers when the
\texttt{abortController.abort()} method is called.

\paragraph{\texorpdfstring{Static method:
\texttt{AbortSignal.abort({[}reason{]})}}{Static method: AbortSignal.abort({[}reason{]})}}\label{static-method-abortsignal.abortreason}

\begin{itemize}
\tightlist
\item
  \texttt{reason}: \{any\}
\item
  Returns: \{AbortSignal\}
\end{itemize}

Returns a new already aborted \texttt{AbortSignal}.

\paragraph{\texorpdfstring{Static method:
\texttt{AbortSignal.timeout(delay)}}{Static method: AbortSignal.timeout(delay)}}\label{static-method-abortsignal.timeoutdelay}

\begin{itemize}
\tightlist
\item
  \texttt{delay} \{number\} The number of milliseconds to wait before
  triggering the AbortSignal.
\end{itemize}

Returns a new \texttt{AbortSignal} which will be aborted in
\texttt{delay} milliseconds.

\paragraph{\texorpdfstring{Static method:
\texttt{AbortSignal.any(signals)}}{Static method: AbortSignal.any(signals)}}\label{static-method-abortsignal.anysignals}

\begin{itemize}
\tightlist
\item
  \texttt{signals} \{AbortSignal{[}{]}\} The \texttt{AbortSignal}s of
  which to compose a new \texttt{AbortSignal}.
\end{itemize}

Returns a new \texttt{AbortSignal} which will be aborted if any of the
provided signals are aborted. Its
\hyperref[abortsignalreason]{\texttt{abortSignal.reason}} will be set to
whichever one of the \texttt{signals} caused it to be aborted.

\paragraph{\texorpdfstring{Event:
\texttt{\textquotesingle{}abort\textquotesingle{}}}{Event: \textquotesingle abort\textquotesingle{}}}\label{event-abort}

The \texttt{\textquotesingle{}abort\textquotesingle{}} event is emitted
when the \texttt{abortController.abort()} method is called. The callback
is invoked with a single object argument with a single \texttt{type}
property set to \texttt{\textquotesingle{}abort\textquotesingle{}}:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ ac }\OperatorTok{=} \KeywordTok{new} \FunctionTok{AbortController}\NormalTok{()}\OperatorTok{;}

\CommentTok{// Use either the onabort property...}
\NormalTok{ac}\OperatorTok{.}\AttributeTok{signal}\OperatorTok{.}\AttributeTok{onabort} \OperatorTok{=}\NormalTok{ () }\KeywordTok{=\textgreater{}} \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}aborted!\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\CommentTok{// Or the EventTarget API...}
\NormalTok{ac}\OperatorTok{.}\AttributeTok{signal}\OperatorTok{.}\FunctionTok{addEventListener}\NormalTok{(}\StringTok{\textquotesingle{}abort\textquotesingle{}}\OperatorTok{,}\NormalTok{ (}\BuiltInTok{event}\NormalTok{) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\BuiltInTok{event}\OperatorTok{.}\AttributeTok{type}\NormalTok{)}\OperatorTok{;}  \CommentTok{// Prints \textquotesingle{}abort\textquotesingle{}}
\NormalTok{\}}\OperatorTok{,}\NormalTok{ \{ }\DataTypeTok{once}\OperatorTok{:} \KeywordTok{true}\NormalTok{ \})}\OperatorTok{;}

\NormalTok{ac}\OperatorTok{.}\FunctionTok{abort}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

The \texttt{AbortController} with which the \texttt{AbortSignal} is
associated will only ever trigger the
\texttt{\textquotesingle{}abort\textquotesingle{}} event once. We
recommended that code check that the \texttt{abortSignal.aborted}
attribute is \texttt{false} before adding an
\texttt{\textquotesingle{}abort\textquotesingle{}} event listener.

Any event listeners attached to the \texttt{AbortSignal} should use the
\texttt{\{\ once:\ true\ \}} option (or, if using the
\texttt{EventEmitter} APIs to attach a listener, use the \texttt{once()}
method) to ensure that the event listener is removed as soon as the
\texttt{\textquotesingle{}abort\textquotesingle{}} event is handled.
Failure to do so may result in memory leaks.

\paragraph{\texorpdfstring{\texttt{abortSignal.aborted}}{abortSignal.aborted}}\label{abortsignal.aborted}

\begin{itemize}
\tightlist
\item
  Type: \{boolean\} True after the \texttt{AbortController} has been
  aborted.
\end{itemize}

\paragraph{\texorpdfstring{\texttt{abortSignal.onabort}}{abortSignal.onabort}}\label{abortsignal.onabort}

\begin{itemize}
\tightlist
\item
  Type: \{Function\}
\end{itemize}

An optional callback function that may be set by user code to be
notified when the \texttt{abortController.abort()} function has been
called.

\paragraph{\texorpdfstring{\texttt{abortSignal.reason}}{abortSignal.reason}}\label{abortsignal.reason}

\begin{itemize}
\tightlist
\item
  Type: \{any\}
\end{itemize}

An optional reason specified when the \texttt{AbortSignal} was
triggered.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ ac }\OperatorTok{=} \KeywordTok{new} \FunctionTok{AbortController}\NormalTok{()}\OperatorTok{;}
\NormalTok{ac}\OperatorTok{.}\FunctionTok{abort}\NormalTok{(}\KeywordTok{new} \BuiltInTok{Error}\NormalTok{(}\StringTok{\textquotesingle{}boom!\textquotesingle{}}\NormalTok{))}\OperatorTok{;}
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(ac}\OperatorTok{.}\AttributeTok{signal}\OperatorTok{.}\AttributeTok{reason}\NormalTok{)}\OperatorTok{;}  \CommentTok{// Error: boom!}
\end{Highlighting}
\end{Shaded}

\paragraph{\texorpdfstring{\texttt{abortSignal.throwIfAborted()}}{abortSignal.throwIfAborted()}}\label{abortsignal.throwifaborted}

If \texttt{abortSignal.aborted} is \texttt{true}, throws
\texttt{abortSignal.reason}.

\subsection{\texorpdfstring{Class:
\texttt{Blob}}{Class: Blob}}\label{class-blob}

See \{Blob\}.

\subsection{\texorpdfstring{Class:
\texttt{Buffer}}{Class: Buffer}}\label{class-buffer}

\begin{itemize}
\tightlist
\item
  \{Function\}
\end{itemize}

Used to handle binary data. See the \href{buffer.md}{buffer section}.

\subsection{\texorpdfstring{Class:
\texttt{ByteLengthQueuingStrategy}}{Class: ByteLengthQueuingStrategy}}\label{class-bytelengthqueuingstrategy}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-bytelengthqueuingstrategy}{\texttt{ByteLengthQueuingStrategy}}.

\subsection{\texorpdfstring{\texttt{\_\_dirname}}{\_\_dirname}}\label{dirname}

This variable may appear to be global but is not. See
\href{modules.md\#__dirname}{\texttt{\_\_dirname}}.

\subsection{\texorpdfstring{\texttt{\_\_filename}}{\_\_filename}}\label{filename}

This variable may appear to be global but is not. See
\href{modules.md\#__filename}{\texttt{\_\_filename}}.

\subsection{\texorpdfstring{\texttt{atob(data)}}{atob(data)}}\label{atobdata}

\begin{quote}
Stability: 3 - Legacy. Use
\texttt{Buffer.from(data,\ \textquotesingle{}base64\textquotesingle{})}
instead.
\end{quote}

Global alias for
\href{buffer.md\#bufferatobdata}{\texttt{buffer.atob()}}.

\subsection{\texorpdfstring{\texttt{BroadcastChannel}}{BroadcastChannel}}\label{broadcastchannel}

See \{BroadcastChannel\}.

\subsection{\texorpdfstring{\texttt{btoa(data)}}{btoa(data)}}\label{btoadata}

\begin{quote}
Stability: 3 - Legacy. Use
\texttt{buf.toString(\textquotesingle{}base64\textquotesingle{})}
instead.
\end{quote}

Global alias for
\href{buffer.md\#bufferbtoadata}{\texttt{buffer.btoa()}}.

\subsection{\texorpdfstring{\texttt{clearImmediate(immediateObject)}}{clearImmediate(immediateObject)}}\label{clearimmediateimmediateobject}

\href{timers.md\#clearimmediateimmediate}{\texttt{clearImmediate}} is
described in the \href{timers.md}{timers} section.

\subsection{\texorpdfstring{\texttt{clearInterval(intervalObject)}}{clearInterval(intervalObject)}}\label{clearintervalintervalobject}

\href{timers.md\#clearintervaltimeout}{\texttt{clearInterval}} is
described in the \href{timers.md}{timers} section.

\subsection{\texorpdfstring{\texttt{clearTimeout(timeoutObject)}}{clearTimeout(timeoutObject)}}\label{cleartimeouttimeoutobject}

\href{timers.md\#cleartimeouttimeout}{\texttt{clearTimeout}} is
described in the \href{timers.md}{timers} section.

\subsection{\texorpdfstring{Class:
\texttt{CompressionStream}}{Class: CompressionStream}}\label{class-compressionstream}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-compressionstream}{\texttt{CompressionStream}}.

\subsection{\texorpdfstring{\texttt{console}}{console}}\label{console}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

Used to print to stdout and stderr. See the
\href{console.md}{\texttt{console}} section.

\subsection{\texorpdfstring{Class:
\texttt{CountQueuingStrategy}}{Class: CountQueuingStrategy}}\label{class-countqueuingstrategy}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-countqueuingstrategy}{\texttt{CountQueuingStrategy}}.

\subsection{\texorpdfstring{\texttt{Crypto}}{Crypto}}\label{crypto}

\begin{quote}
Stability: 1 - Experimental. Disable this API with the
\href{cli.md\#--no-experimental-global-webcrypto}{\texttt{-\/-no-experimental-global-webcrypto}}
CLI flag.
\end{quote}

A browser-compatible implementation of \{Crypto\}. This global is
available only if the Node.js binary was compiled with including support
for the \texttt{node:crypto} module.

\subsection{\texorpdfstring{\texttt{crypto}}{crypto}}\label{crypto-1}

\begin{quote}
Stability: 1 - Experimental. Disable this API with the
\href{cli.md\#--no-experimental-global-webcrypto}{\texttt{-\/-no-experimental-global-webcrypto}}
CLI flag.
\end{quote}

A browser-compatible implementation of the \href{webcrypto.md}{Web
Crypto API}.

\subsection{\texorpdfstring{\texttt{CryptoKey}}{CryptoKey}}\label{cryptokey}

\begin{quote}
Stability: 1 - Experimental. Disable this API with the
\href{cli.md\#--no-experimental-global-webcrypto}{\texttt{-\/-no-experimental-global-webcrypto}}
CLI flag.
\end{quote}

A browser-compatible implementation of \{CryptoKey\}. This global is
available only if the Node.js binary was compiled with including support
for the \texttt{node:crypto} module.

\subsection{\texorpdfstring{\texttt{CustomEvent}}{CustomEvent}}\label{customevent}

\begin{quote}
Stability: 1 - Experimental. Disable this API with the
\href{cli.md\#--no-experimental-global-customevent}{\texttt{-\/-no-experimental-global-customevent}}
CLI flag.
\end{quote}

A browser-compatible implementation of the
\href{https://dom.spec.whatwg.org/\#customevent}{\texttt{CustomEvent}
Web API}.

\subsection{\texorpdfstring{Class:
\texttt{DecompressionStream}}{Class: DecompressionStream}}\label{class-decompressionstream}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-decompressionstream}{\texttt{DecompressionStream}}.

\subsection{\texorpdfstring{\texttt{Event}}{Event}}\label{event}

A browser-compatible implementation of the \texttt{Event} class. See
\href{events.md\#eventtarget-and-event-api}{\texttt{EventTarget} and
\texttt{Event} API} for more details.

\subsection{\texorpdfstring{\texttt{EventTarget}}{EventTarget}}\label{eventtarget}

A browser-compatible implementation of the \texttt{EventTarget} class.
See \href{events.md\#eventtarget-and-event-api}{\texttt{EventTarget} and
\texttt{Event} API} for more details.

\subsection{\texorpdfstring{\texttt{exports}}{exports}}\label{exports}

This variable may appear to be global but is not. See
\href{modules.md\#exports}{\texttt{exports}}.

\subsection{\texorpdfstring{\texttt{fetch}}{fetch}}\label{fetch}

\begin{quote}
Stability: 2 - Stable
\end{quote}

A browser-compatible implementation of the
\href{https://developer.mozilla.org/en-US/docs/Web/API/fetch}{\texttt{fetch()}}
function.

\subsection{\texorpdfstring{Class:
\texttt{File}}{Class: File}}\label{class-file}

See \{File\}.

\subsection{\texorpdfstring{Class
\texttt{FormData}}{Class FormData}}\label{class-formdata}

\begin{quote}
Stability: 2 - Stable
\end{quote}

A browser-compatible implementation of \{FormData\}.

\subsection{\texorpdfstring{\texttt{global}}{global}}\label{global}

\begin{quote}
Stability: 3 - Legacy. Use
\href{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global_Objects/globalThis}{\texttt{globalThis}}
instead.
\end{quote}

\begin{itemize}
\tightlist
\item
  \{Object\} The global namespace object.
\end{itemize}

In browsers, the top-level scope has traditionally been the global
scope. This means that \texttt{var\ something} will define a new global
variable, except within ECMAScript modules. In Node.js, this is
different. The top-level scope is not the global scope;
\texttt{var\ something} inside a Node.js module will be local to that
module, regardless of whether it is a \href{modules.md}{CommonJS module}
or an \href{esm.md}{ECMAScript module}.

\subsection{\texorpdfstring{Class
\texttt{Headers}}{Class Headers}}\label{class-headers}

\begin{quote}
Stability: 2 - Stable
\end{quote}

A browser-compatible implementation of \{Headers\}.

\subsection{\texorpdfstring{\texttt{MessageChannel}}{MessageChannel}}\label{messagechannel}

The \texttt{MessageChannel} class. See
\href{worker_threads.md\#class-messagechannel}{\texttt{MessageChannel}}
for more details.

\subsection{\texorpdfstring{\texttt{MessageEvent}}{MessageEvent}}\label{messageevent}

The \texttt{MessageEvent} class. See
\href{https://developer.mozilla.org/en-US/docs/Web/API/MessageEvent/MessageEvent}{\texttt{MessageEvent}}
for more details.

\subsection{\texorpdfstring{\texttt{MessagePort}}{MessagePort}}\label{messageport}

The \texttt{MessagePort} class. See
\href{worker_threads.md\#class-messageport}{\texttt{MessagePort}} for
more details.

\subsection{\texorpdfstring{\texttt{module}}{module}}\label{module}

This variable may appear to be global but is not. See
\href{modules.md\#module}{\texttt{module}}.

\subsection{\texorpdfstring{\texttt{Navigator}}{Navigator}}\label{navigator}

\begin{quote}
Stability: 1.1 - Active development. Disable this API with the
\href{cli.md\#--no-experimental-global-navigator}{\texttt{-\/-no-experimental-global-navigator}}
CLI flag.
\end{quote}

A partial implementation of the
\href{https://html.spec.whatwg.org/multipage/system-state.html\#the-navigator-object}{Navigator
API}.

\subsection{\texorpdfstring{\texttt{navigator}}{navigator}}\label{navigator-1}

\begin{quote}
Stability: 1.1 - Active development. Disable this API with the
\href{cli.md\#--no-experimental-global-navigator}{\texttt{-\/-no-experimental-global-navigator}}
CLI flag.
\end{quote}

A partial implementation of
\href{https://developer.mozilla.org/en-US/docs/Web/API/Window/navigator}{\texttt{window.navigator}}.

\subsubsection{\texorpdfstring{\texttt{navigator.hardwareConcurrency}}{navigator.hardwareConcurrency}}\label{navigator.hardwareconcurrency}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

The \texttt{navigator.hardwareConcurrency} read-only property returns
the number of logical processors available to the current Node.js
instance.

\begin{Shaded}
\begin{Highlighting}[]
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}This process is running on }\SpecialCharTok{$\{}\BuiltInTok{navigator}\OperatorTok{.}\AttributeTok{hardwareConcurrency}\SpecialCharTok{\}}\VerbatimStringTok{ logical processors\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{navigator.language}}{navigator.language}}\label{navigator.language}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

The \texttt{navigator.language} read-only property returns a string
representing the preferred language of the Node.js instance. The
language will be determined by the ICU library used by Node.js at
runtime based on the default language of the operating system.

The value is representing the language version as defined in
\href{https://www.rfc-editor.org/rfc/rfc5646.txt}{RFC 5646}.

The fallback value on builds without ICU is
\texttt{\textquotesingle{}en-US\textquotesingle{}}.

\begin{Shaded}
\begin{Highlighting}[]
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}The preferred language of the Node.js instance has the tag \textquotesingle{}}\SpecialCharTok{$\{}\BuiltInTok{navigator}\OperatorTok{.}\AttributeTok{language}\SpecialCharTok{\}}\VerbatimStringTok{\textquotesingle{}\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{navigator.languages}}{navigator.languages}}\label{navigator.languages}

\begin{itemize}
\tightlist
\item
  \{Array\}
\end{itemize}

The \texttt{navigator.languages} read-only property returns an array of
strings representing the preferred languages of the Node.js instance. By
default \texttt{navigator.languages} contains only the value of
\texttt{navigator.language}, which will be determined by the ICU library
used by Node.js at runtime based on the default language of the
operating system.

The fallback value on builds without ICU is
\texttt{{[}\textquotesingle{}en-US\textquotesingle{}{]}}.

\begin{Shaded}
\begin{Highlighting}[]
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}The preferred languages are \textquotesingle{}}\SpecialCharTok{$\{}\BuiltInTok{navigator}\OperatorTok{.}\AttributeTok{languages}\SpecialCharTok{\}}\VerbatimStringTok{\textquotesingle{}\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{navigator.platform}}{navigator.platform}}\label{navigator.platform}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

The \texttt{navigator.platform} read-only property returns a string
identifying the platform on which the Node.js instance is running.

\begin{Shaded}
\begin{Highlighting}[]
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}This process is running on }\SpecialCharTok{$\{}\BuiltInTok{navigator}\OperatorTok{.}\AttributeTok{platform}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{navigator.userAgent}}{navigator.userAgent}}\label{navigator.useragent}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

The \texttt{navigator.userAgent} read-only property returns user agent
consisting of the runtime name and major version number.

\begin{Shaded}
\begin{Highlighting}[]
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}The user{-}agent is }\SpecialCharTok{$\{}\BuiltInTok{navigator}\OperatorTok{.}\AttributeTok{userAgent}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;} \CommentTok{// Prints "Node.js/21"}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{\texttt{PerformanceEntry}}{PerformanceEntry}}\label{performanceentry}

The \texttt{PerformanceEntry} class. See
\href{perf_hooks.md\#class-performanceentry}{\texttt{PerformanceEntry}}
for more details.

\subsection{\texorpdfstring{\texttt{PerformanceMark}}{PerformanceMark}}\label{performancemark}

The \texttt{PerformanceMark} class. See
\href{perf_hooks.md\#class-performancemark}{\texttt{PerformanceMark}}
for more details.

\subsection{\texorpdfstring{\texttt{PerformanceMeasure}}{PerformanceMeasure}}\label{performancemeasure}

The \texttt{PerformanceMeasure} class. See
\href{perf_hooks.md\#class-performancemeasure}{\texttt{PerformanceMeasure}}
for more details.

\subsection{\texorpdfstring{\texttt{PerformanceObserver}}{PerformanceObserver}}\label{performanceobserver}

The \texttt{PerformanceObserver} class. See
\href{perf_hooks.md\#class-performanceobserver}{\texttt{PerformanceObserver}}
for more details.

\subsection{\texorpdfstring{\texttt{PerformanceObserverEntryList}}{PerformanceObserverEntryList}}\label{performanceobserverentrylist}

The \texttt{PerformanceObserverEntryList} class. See
\href{perf_hooks.md\#class-performanceobserverentrylist}{\texttt{PerformanceObserverEntryList}}
for more details.

\subsection{\texorpdfstring{\texttt{PerformanceResourceTiming}}{PerformanceResourceTiming}}\label{performanceresourcetiming}

The \texttt{PerformanceResourceTiming} class. See
\href{perf_hooks.md\#class-performanceresourcetiming}{\texttt{PerformanceResourceTiming}}
for more details.

\subsection{\texorpdfstring{\texttt{performance}}{performance}}\label{performance}

The
\href{perf_hooks.md\#perf_hooksperformance}{\texttt{perf\_hooks.performance}}
object.

\subsection{\texorpdfstring{\texttt{process}}{process}}\label{process}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

The process object. See the \href{process.md\#process}{\texttt{process}
object} section.

\subsection{\texorpdfstring{\texttt{queueMicrotask(callback)}}{queueMicrotask(callback)}}\label{queuemicrotaskcallback}

\begin{itemize}
\tightlist
\item
  \texttt{callback} \{Function\} Function to be queued.
\end{itemize}

The \texttt{queueMicrotask()} method queues a microtask to invoke
\texttt{callback}. If \texttt{callback} throws an exception, the
\href{process.md\#process}{\texttt{process} object}
\texttt{\textquotesingle{}uncaughtException\textquotesingle{}} event
will be emitted.

The microtask queue is managed by V8 and may be used in a similar manner
to the
\href{process.md\#processnexttickcallback-args}{\texttt{process.nextTick()}}
queue, which is managed by Node.js. The \texttt{process.nextTick()}
queue is always processed before the microtask queue within each turn of
the Node.js event loop.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{// Here, \textasciigrave{}queueMicrotask()\textasciigrave{} is used to ensure the \textquotesingle{}load\textquotesingle{} event is always}
\CommentTok{// emitted asynchronously, and therefore consistently. Using}
\CommentTok{// \textasciigrave{}process.nextTick()\textasciigrave{} here would result in the \textquotesingle{}load\textquotesingle{} event always emitting}
\CommentTok{// before any other promise jobs.}

\NormalTok{DataHandler}\OperatorTok{.}\AttributeTok{prototype}\OperatorTok{.}\AttributeTok{load} \OperatorTok{=} \KeywordTok{async} \KeywordTok{function} \FunctionTok{load}\NormalTok{(key) \{}
  \KeywordTok{const}\NormalTok{ hit }\OperatorTok{=} \KeywordTok{this}\OperatorTok{.}\AttributeTok{\_cache}\OperatorTok{.}\FunctionTok{get}\NormalTok{(key)}\OperatorTok{;}
  \ControlFlowTok{if}\NormalTok{ (hit }\OperatorTok{!==} \KeywordTok{undefined}\NormalTok{) \{}
    \FunctionTok{queueMicrotask}\NormalTok{(() }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \KeywordTok{this}\OperatorTok{.}\FunctionTok{emit}\NormalTok{(}\StringTok{\textquotesingle{}load\textquotesingle{}}\OperatorTok{,}\NormalTok{ hit)}\OperatorTok{;}
\NormalTok{    \})}\OperatorTok{;}
    \ControlFlowTok{return}\OperatorTok{;}
\NormalTok{  \}}

  \KeywordTok{const}\NormalTok{ data }\OperatorTok{=} \ControlFlowTok{await} \FunctionTok{fetchData}\NormalTok{(key)}\OperatorTok{;}
  \KeywordTok{this}\OperatorTok{.}\AttributeTok{\_cache}\OperatorTok{.}\FunctionTok{set}\NormalTok{(key}\OperatorTok{,}\NormalTok{ data)}\OperatorTok{;}
  \KeywordTok{this}\OperatorTok{.}\FunctionTok{emit}\NormalTok{(}\StringTok{\textquotesingle{}load\textquotesingle{}}\OperatorTok{,}\NormalTok{ data)}\OperatorTok{;}
\NormalTok{\}}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{Class:
\texttt{ReadableByteStreamController}}{Class: ReadableByteStreamController}}\label{class-readablebytestreamcontroller}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-readablebytestreamcontroller}{\texttt{ReadableByteStreamController}}.

\subsection{\texorpdfstring{Class:
\texttt{ReadableStream}}{Class: ReadableStream}}\label{class-readablestream}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-readablestream}{\texttt{ReadableStream}}.

\subsection{\texorpdfstring{Class:
\texttt{ReadableStreamBYOBReader}}{Class: ReadableStreamBYOBReader}}\label{class-readablestreambyobreader}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-readablestreambyobreader}{\texttt{ReadableStreamBYOBReader}}.

\subsection{\texorpdfstring{Class:
\texttt{ReadableStreamBYOBRequest}}{Class: ReadableStreamBYOBRequest}}\label{class-readablestreambyobrequest}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-readablestreambyobrequest}{\texttt{ReadableStreamBYOBRequest}}.

\subsection{\texorpdfstring{Class:
\texttt{ReadableStreamDefaultController}}{Class: ReadableStreamDefaultController}}\label{class-readablestreamdefaultcontroller}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-readablestreamdefaultcontroller}{\texttt{ReadableStreamDefaultController}}.

\subsection{\texorpdfstring{Class:
\texttt{ReadableStreamDefaultReader}}{Class: ReadableStreamDefaultReader}}\label{class-readablestreamdefaultreader}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-readablestreamdefaultreader}{\texttt{ReadableStreamDefaultReader}}.

\subsection{\texorpdfstring{\texttt{require()}}{require()}}\label{require}

This variable may appear to be global but is not. See
\href{modules.md\#requireid}{\texttt{require()}}.

\subsection{\texorpdfstring{\texttt{Response}}{Response}}\label{response}

\begin{quote}
Stability: 2 - Stable
\end{quote}

A browser-compatible implementation of \{Response\}.

\subsection{\texorpdfstring{\texttt{Request}}{Request}}\label{request}

\begin{quote}
Stability: 2 - Stable
\end{quote}

A browser-compatible implementation of \{Request\}.

\subsection{\texorpdfstring{\texttt{setImmediate(callback{[},\ ...args{]})}}{setImmediate(callback{[}, ...args{]})}}\label{setimmediatecallback-...args}

\href{timers.md\#setimmediatecallback-args}{\texttt{setImmediate}} is
described in the \href{timers.md}{timers} section.

\subsection{\texorpdfstring{\texttt{setInterval(callback,\ delay{[},\ ...args{]})}}{setInterval(callback, delay{[}, ...args{]})}}\label{setintervalcallback-delay-...args}

\href{timers.md\#setintervalcallback-delay-args}{\texttt{setInterval}}
is described in the \href{timers.md}{timers} section.

\subsection{\texorpdfstring{\texttt{setTimeout(callback,\ delay{[},\ ...args{]})}}{setTimeout(callback, delay{[}, ...args{]})}}\label{settimeoutcallback-delay-...args}

\href{timers.md\#settimeoutcallback-delay-args}{\texttt{setTimeout}} is
described in the \href{timers.md}{timers} section.

\subsection{\texorpdfstring{\texttt{structuredClone(value{[},\ options{]})}}{structuredClone(value{[}, options{]})}}\label{structuredclonevalue-options}

The WHATWG
\href{https://developer.mozilla.org/en-US/docs/Web/API/structuredClone}{\texttt{structuredClone}}
method.

\subsection{\texorpdfstring{\texttt{SubtleCrypto}}{SubtleCrypto}}\label{subtlecrypto}

\begin{quote}
Stability: 1 - Experimental. Disable this API with the
\href{cli.md\#--no-experimental-global-webcrypto}{\texttt{-\/-no-experimental-global-webcrypto}}
CLI flag.
\end{quote}

A browser-compatible implementation of \{SubtleCrypto\}. This global is
available only if the Node.js binary was compiled with including support
for the \texttt{node:crypto} module.

\subsection{\texorpdfstring{\texttt{DOMException}}{DOMException}}\label{domexception}

The WHATWG \texttt{DOMException} class. See
\href{https://developer.mozilla.org/en-US/docs/Web/API/DOMException}{\texttt{DOMException}}
for more details.

\subsection{\texorpdfstring{\texttt{TextDecoder}}{TextDecoder}}\label{textdecoder}

The WHATWG \texttt{TextDecoder} class. See the
\href{util.md\#class-utiltextdecoder}{\texttt{TextDecoder}} section.

\subsection{\texorpdfstring{Class:
\texttt{TextDecoderStream}}{Class: TextDecoderStream}}\label{class-textdecoderstream}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-textdecoderstream}{\texttt{TextDecoderStream}}.

\subsection{\texorpdfstring{\texttt{TextEncoder}}{TextEncoder}}\label{textencoder}

The WHATWG \texttt{TextEncoder} class. See the
\href{util.md\#class-utiltextencoder}{\texttt{TextEncoder}} section.

\subsection{\texorpdfstring{Class:
\texttt{TextEncoderStream}}{Class: TextEncoderStream}}\label{class-textencoderstream}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-textencoderstream}{\texttt{TextEncoderStream}}.

\subsection{\texorpdfstring{Class:
\texttt{TransformStream}}{Class: TransformStream}}\label{class-transformstream}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-transformstream}{\texttt{TransformStream}}.

\subsection{\texorpdfstring{Class:
\texttt{TransformStreamDefaultController}}{Class: TransformStreamDefaultController}}\label{class-transformstreamdefaultcontroller}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-transformstreamdefaultcontroller}{\texttt{TransformStreamDefaultController}}.

\subsection{\texorpdfstring{\texttt{URL}}{URL}}\label{url}

The WHATWG \texttt{URL} class. See the
\href{url.md\#class-url}{\texttt{URL}} section.

\subsection{\texorpdfstring{\texttt{URLSearchParams}}{URLSearchParams}}\label{urlsearchparams}

The WHATWG \texttt{URLSearchParams} class. See the
\href{url.md\#class-urlsearchparams}{\texttt{URLSearchParams}} section.

\subsection{\texorpdfstring{\texttt{WebAssembly}}{WebAssembly}}\label{webassembly}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

The object that acts as the namespace for all W3C
\href{https://webassembly.org}{WebAssembly} related functionality. See
the \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{Mozilla
Developer Network} for usage and compatibility.

\subsection{\texorpdfstring{\texttt{WebSocket}}{WebSocket}}\label{websocket}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{https://developer.mozilla.org/en-US/docs/Web/API/WebSocket}{\texttt{WebSocket}}.
Enable this API with the
\href{cli.md\#--experimental-websocket}{\texttt{-\/-experimental-websocket}}
CLI flag.

\subsection{\texorpdfstring{Class:
\texttt{WritableStream}}{Class: WritableStream}}\label{class-writablestream}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-writablestream}{\texttt{WritableStream}}.

\subsection{\texorpdfstring{Class:
\texttt{WritableStreamDefaultController}}{Class: WritableStreamDefaultController}}\label{class-writablestreamdefaultcontroller}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-writablestreamdefaultcontroller}{\texttt{WritableStreamDefaultController}}.

\subsection{\texorpdfstring{Class:
\texttt{WritableStreamDefaultWriter}}{Class: WritableStreamDefaultWriter}}\label{class-writablestreamdefaultwriter}

\begin{quote}
Stability: 1 - Experimental.
\end{quote}

A browser-compatible implementation of
\href{webstreams.md\#class-writablestreamdefaultwriter}{\texttt{WritableStreamDefaultWriter}}.
