\section{HTTP}\label{http}

\begin{quote}
Stability: 2 - Stable
\end{quote}

To use the HTTP server and client one must
\texttt{require(\textquotesingle{}node:http\textquotesingle{})}.

The HTTP interfaces in Node.js are designed to support many features of
the protocol which have been traditionally difficult to use. In
particular, large, possibly chunk-encoded, messages. The interface is
careful to never buffer entire requests or responses, so the user is
able to stream data.

HTTP message headers are represented by an object like this:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{\{} \DataTypeTok{"content{-}length"}\FunctionTok{:} \StringTok{"123"}\FunctionTok{,}
  \DataTypeTok{"content{-}type"}\FunctionTok{:} \StringTok{"text/plain"}\FunctionTok{,}
  \DataTypeTok{"connection"}\FunctionTok{:} \StringTok{"keep{-}alive"}\FunctionTok{,}
  \DataTypeTok{"host"}\FunctionTok{:} \StringTok{"example.com"}\FunctionTok{,}
  \DataTypeTok{"accept"}\FunctionTok{:} \StringTok{"*/*"} \FunctionTok{\}}
\end{Highlighting}
\end{Shaded}

Keys are lowercased. Values are not modified.

In order to support the full spectrum of possible HTTP applications, the
Node.js HTTP API is very low-level. It deals with stream handling and
message parsing only. It parses a message into headers and body but it
does not parse the actual headers or the body.

See \hyperref[messageheaders]{\texttt{message.headers}} for details on
how duplicate headers are handled.

The raw headers as they were received are retained in the
\texttt{rawHeaders} property, which is an array of
\texttt{{[}key,\ value,\ key2,\ value2,\ ...{]}}. For example, the
previous message header object might have a \texttt{rawHeaders} list
like the following:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{[ }\StringTok{\textquotesingle{}ConTent{-}Length\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}123456\textquotesingle{}}\OperatorTok{,}
  \StringTok{\textquotesingle{}content{-}LENGTH\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}123\textquotesingle{}}\OperatorTok{,}
  \StringTok{\textquotesingle{}content{-}type\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\OperatorTok{,}
  \StringTok{\textquotesingle{}CONNECTION\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}keep{-}alive\textquotesingle{}}\OperatorTok{,}
  \StringTok{\textquotesingle{}Host\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}example.com\textquotesingle{}}\OperatorTok{,}
  \StringTok{\textquotesingle{}accepT\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}*/*\textquotesingle{}}\NormalTok{ ]}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{Class:
\texttt{http.Agent}}{Class: http.Agent}}\label{class-http.agent}

An \texttt{Agent} is responsible for managing connection persistence and
reuse for HTTP clients. It maintains a queue of pending requests for a
given host and port, reusing a single socket connection for each until
the queue is empty, at which time the socket is either destroyed or put
into a pool where it is kept to be used again for requests to the same
host and port. Whether it is destroyed or pooled depends on the
\texttt{keepAlive} \hyperref[new-agentoptions]{option}.

Pooled connections have TCP Keep-Alive enabled for them, but servers may
still close idle connections, in which case they will be removed from
the pool and a new connection will be made when a new HTTP request is
made for that host and port. Servers may also refuse to allow multiple
requests over the same connection, in which case the connection will
have to be remade for every request and cannot be pooled. The
\texttt{Agent} will still make the requests to that server, but each one
will occur over a new connection.

When a connection is closed by the client or the server, it is removed
from the pool. Any unused sockets in the pool will be unrefed so as not
to keep the Node.js process running when there are no outstanding
requests. (see \href{net.md\#socketunref}{\texttt{socket.unref()}}).

It is good practice, to \hyperref[agentdestroy]{\texttt{destroy()}} an
\texttt{Agent} instance when it is no longer in use, because unused
sockets consume OS resources.

Sockets are removed from an agent when the socket emits either a
\texttt{\textquotesingle{}close\textquotesingle{}} event or an
\texttt{\textquotesingle{}agentRemove\textquotesingle{}} event. When
intending to keep one HTTP request open for a long time without keeping
it in the agent, something like the following may be done:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{http}\OperatorTok{.}\FunctionTok{get}\NormalTok{(options}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \CommentTok{// Do stuff}
\NormalTok{\})}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}socket\textquotesingle{}}\OperatorTok{,}\NormalTok{ (socket) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  socket}\OperatorTok{.}\FunctionTok{emit}\NormalTok{(}\StringTok{\textquotesingle{}agentRemove\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

An agent may also be used for an individual request. By providing
\texttt{\{agent:\ false\}} as an option to the \texttt{http.get()} or
\texttt{http.request()} functions, a one-time use \texttt{Agent} with
default options will be used for the client connection.

\texttt{agent:false}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{http}\OperatorTok{.}\FunctionTok{get}\NormalTok{(\{}
  \DataTypeTok{hostname}\OperatorTok{:} \StringTok{\textquotesingle{}localhost\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{port}\OperatorTok{:} \DecValTok{80}\OperatorTok{,}
  \DataTypeTok{path}\OperatorTok{:} \StringTok{\textquotesingle{}/\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{agent}\OperatorTok{:} \KeywordTok{false}\OperatorTok{,}  \CommentTok{// Create a new agent just for this one request}
\NormalTok{\}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \CommentTok{// Do stuff with response}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{new\ Agent({[}options{]})}}{new Agent({[}options{]})}}\label{new-agentoptions}

\begin{itemize}
\tightlist
\item
  \texttt{options} \{Object\} Set of configurable options to set on the
  agent. Can have the following fields:

  \begin{itemize}
  \tightlist
  \item
    \texttt{keepAlive} \{boolean\} Keep sockets around even when there
    are no outstanding requests, so they can be used for future requests
    without having to reestablish a TCP connection. Not to be confused
    with the \texttt{keep-alive} value of the \texttt{Connection}
    header. The \texttt{Connection:\ keep-alive} header is always sent
    when using an agent except when the \texttt{Connection} header is
    explicitly specified or when the \texttt{keepAlive} and
    \texttt{maxSockets} options are respectively set to \texttt{false}
    and \texttt{Infinity}, in which case \texttt{Connection:\ close}
    will be used. \textbf{Default:} \texttt{false}.
  \item
    \texttt{keepAliveMsecs} \{number\} When using the \texttt{keepAlive}
    option, specifies the
    \href{net.md\#socketsetkeepaliveenable-initialdelay}{initial delay}
    for TCP Keep-Alive packets. Ignored when the \texttt{keepAlive}
    option is \texttt{false} or \texttt{undefined}. \textbf{Default:}
    \texttt{1000}.
  \item
    \texttt{maxSockets} \{number\} Maximum number of sockets to allow
    per host. If the same host opens multiple concurrent connections,
    each request will use new socket until the \texttt{maxSockets} value
    is reached. If the host attempts to open more connections than
    \texttt{maxSockets}, the additional requests will enter into a
    pending request queue, and will enter active connection state when
    an existing connection terminates. This makes sure there are at most
    \texttt{maxSockets} active connections at any point in time, from a
    given host. \textbf{Default:} \texttt{Infinity}.
  \item
    \texttt{maxTotalSockets} \{number\} Maximum number of sockets
    allowed for all hosts in total. Each request will use a new socket
    until the maximum is reached. \textbf{Default:} \texttt{Infinity}.
  \item
    \texttt{maxFreeSockets} \{number\} Maximum number of sockets per
    host to leave open in a free state. Only relevant if
    \texttt{keepAlive} is set to \texttt{true}. \textbf{Default:}
    \texttt{256}.
  \item
    \texttt{scheduling} \{string\} Scheduling strategy to apply when
    picking the next free socket to use. It can be
    \texttt{\textquotesingle{}fifo\textquotesingle{}} or
    \texttt{\textquotesingle{}lifo\textquotesingle{}}. The main
    difference between the two scheduling strategies is that
    \texttt{\textquotesingle{}lifo\textquotesingle{}} selects the most
    recently used socket, while
    \texttt{\textquotesingle{}fifo\textquotesingle{}} selects the least
    recently used socket. In case of a low rate of request per second,
    the \texttt{\textquotesingle{}lifo\textquotesingle{}} scheduling
    will lower the risk of picking a socket that might have been closed
    by the server due to inactivity. In case of a high rate of request
    per second, the \texttt{\textquotesingle{}fifo\textquotesingle{}}
    scheduling will maximize the number of open sockets, while the
    \texttt{\textquotesingle{}lifo\textquotesingle{}} scheduling will
    keep it as low as possible. \textbf{Default:}
    \texttt{\textquotesingle{}lifo\textquotesingle{}}.
  \item
    \texttt{timeout} \{number\} Socket timeout in milliseconds. This
    will set the timeout when the socket is created.
  \end{itemize}
\end{itemize}

\texttt{options} in
\href{net.md\#socketconnectoptions-connectlistener}{\texttt{socket.connect()}}
are also supported.

The default \hyperref[httpglobalagent]{\texttt{http.globalAgent}} that
is used by
\hyperref[httprequestoptions-callback]{\texttt{http.request()}} has all
of these values set to their respective defaults.

To configure any of them, a custom
\hyperref[class-httpagent]{\texttt{http.Agent}} instance must be
created.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ \{ Agent}\OperatorTok{,}\NormalTok{ request \} }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ keepAliveAgent }\OperatorTok{=} \KeywordTok{new} \FunctionTok{Agent}\NormalTok{(\{ }\DataTypeTok{keepAlive}\OperatorTok{:} \KeywordTok{true}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{options}\OperatorTok{.}\AttributeTok{agent} \OperatorTok{=}\NormalTok{ keepAliveAgent}\OperatorTok{;}
\FunctionTok{request}\NormalTok{(options}\OperatorTok{,}\NormalTok{ onResponseCallback)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ keepAliveAgent }\OperatorTok{=} \KeywordTok{new}\NormalTok{ http}\OperatorTok{.}\FunctionTok{Agent}\NormalTok{(\{ }\DataTypeTok{keepAlive}\OperatorTok{:} \KeywordTok{true}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{options}\OperatorTok{.}\AttributeTok{agent} \OperatorTok{=}\NormalTok{ keepAliveAgent}\OperatorTok{;}
\NormalTok{http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options}\OperatorTok{,}\NormalTok{ onResponseCallback)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{agent.createConnection(options{[},\ callback{]})}}{agent.createConnection(options{[}, callback{]})}}\label{agent.createconnectionoptions-callback}

\begin{itemize}
\tightlist
\item
  \texttt{options} \{Object\} Options containing connection details.
  Check
  \href{net.md\#netcreateconnectionoptions-connectlistener}{\texttt{net.createConnection()}}
  for the format of the options
\item
  \texttt{callback} \{Function\} Callback function that receives the
  created socket
\item
  Returns: \{stream.Duplex\}
\end{itemize}

Produces a socket/stream to be used for HTTP requests.

By default, this function is the same as
\href{net.md\#netcreateconnectionoptions-connectlistener}{\texttt{net.createConnection()}}.
However, custom agents may override this method in case greater
flexibility is desired.

A socket/stream can be supplied in one of two ways: by returning the
socket/stream from this function, or by passing the socket/stream to
\texttt{callback}.

This method is guaranteed to return an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

\texttt{callback} has a signature of \texttt{(err,\ stream)}.

\subsubsection{\texorpdfstring{\texttt{agent.keepSocketAlive(socket)}}{agent.keepSocketAlive(socket)}}\label{agent.keepsocketalivesocket}

\begin{itemize}
\tightlist
\item
  \texttt{socket} \{stream.Duplex\}
\end{itemize}

Called when \texttt{socket} is detached from a request and could be
persisted by the \texttt{Agent}. Default behavior is to:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{socket}\OperatorTok{.}\FunctionTok{setKeepAlive}\NormalTok{(}\KeywordTok{true}\OperatorTok{,} \KeywordTok{this}\OperatorTok{.}\AttributeTok{keepAliveMsecs}\NormalTok{)}\OperatorTok{;}
\NormalTok{socket}\OperatorTok{.}\FunctionTok{unref}\NormalTok{()}\OperatorTok{;}
\ControlFlowTok{return} \KeywordTok{true}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

This method can be overridden by a particular \texttt{Agent} subclass.
If this method returns a falsy value, the socket will be destroyed
instead of persisting it for use with the next request.

The \texttt{socket} argument can be an instance of \{net.Socket\}, a
subclass of \{stream.Duplex\}.

\subsubsection{\texorpdfstring{\texttt{agent.reuseSocket(socket,\ request)}}{agent.reuseSocket(socket, request)}}\label{agent.reusesocketsocket-request}

\begin{itemize}
\tightlist
\item
  \texttt{socket} \{stream.Duplex\}
\item
  \texttt{request} \{http.ClientRequest\}
\end{itemize}

Called when \texttt{socket} is attached to \texttt{request} after being
persisted because of the keep-alive options. Default behavior is to:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{socket}\OperatorTok{.}\FunctionTok{ref}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

This method can be overridden by a particular \texttt{Agent} subclass.

The \texttt{socket} argument can be an instance of \{net.Socket\}, a
subclass of \{stream.Duplex\}.

\subsubsection{\texorpdfstring{\texttt{agent.destroy()}}{agent.destroy()}}\label{agent.destroy}

Destroy any sockets that are currently in use by the agent.

It is usually not necessary to do this. However, if using an agent with
\texttt{keepAlive} enabled, then it is best to explicitly shut down the
agent when it is no longer needed. Otherwise, sockets might stay open
for quite a long time before the server terminates them.

\subsubsection{\texorpdfstring{\texttt{agent.freeSockets}}{agent.freeSockets}}\label{agent.freesockets}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

An object which contains arrays of sockets currently awaiting use by the
agent when \texttt{keepAlive} is enabled. Do not modify.

Sockets in the \texttt{freeSockets} list will be automatically destroyed
and removed from the array on
\texttt{\textquotesingle{}timeout\textquotesingle{}}.

\subsubsection{\texorpdfstring{\texttt{agent.getName({[}options{]})}}{agent.getName({[}options{]})}}\label{agent.getnameoptions}

\begin{itemize}
\tightlist
\item
  \texttt{options} \{Object\} A set of options providing information for
  name generation

  \begin{itemize}
  \tightlist
  \item
    \texttt{host} \{string\} A domain name or IP address of the server
    to issue the request to
  \item
    \texttt{port} \{number\} Port of remote server
  \item
    \texttt{localAddress} \{string\} Local interface to bind for network
    connections when issuing the request
  \item
    \texttt{family} \{integer\} Must be 4 or 6 if this doesn't equal
    \texttt{undefined}.
  \end{itemize}
\item
  Returns: \{string\}
\end{itemize}

Get a unique name for a set of request options, to determine whether a
connection can be reused. For an HTTP agent, this returns
\texttt{host:port:localAddress} or
\texttt{host:port:localAddress:family}. For an HTTPS agent, the name
includes the CA, cert, ciphers, and other HTTPS/TLS-specific options
that determine socket reusability.

\subsubsection{\texorpdfstring{\texttt{agent.maxFreeSockets}}{agent.maxFreeSockets}}\label{agent.maxfreesockets}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

By default set to 256. For agents with \texttt{keepAlive} enabled, this
sets the maximum number of sockets that will be left open in the free
state.

\subsubsection{\texorpdfstring{\texttt{agent.maxSockets}}{agent.maxSockets}}\label{agent.maxsockets}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

By default set to \texttt{Infinity}. Determines how many concurrent
sockets the agent can have open per origin. Origin is the returned value
of \hyperref[agentgetnameoptions]{\texttt{agent.getName()}}.

\subsubsection{\texorpdfstring{\texttt{agent.maxTotalSockets}}{agent.maxTotalSockets}}\label{agent.maxtotalsockets}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

By default set to \texttt{Infinity}. Determines how many concurrent
sockets the agent can have open. Unlike \texttt{maxSockets}, this
parameter applies across all origins.

\subsubsection{\texorpdfstring{\texttt{agent.requests}}{agent.requests}}\label{agent.requests}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

An object which contains queues of requests that have not yet been
assigned to sockets. Do not modify.

\subsubsection{\texorpdfstring{\texttt{agent.sockets}}{agent.sockets}}\label{agent.sockets}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

An object which contains arrays of sockets currently in use by the
agent. Do not modify.

\subsection{\texorpdfstring{Class:
\texttt{http.ClientRequest}}{Class: http.ClientRequest}}\label{class-http.clientrequest}

\begin{itemize}
\tightlist
\item
  Extends: \{http.OutgoingMessage\}
\end{itemize}

This object is created internally and returned from
\hyperref[httprequestoptions-callback]{\texttt{http.request()}}. It
represents an \emph{in-progress} request whose header has already been
queued. The header is still mutable using the
\hyperref[requestsetheadername-value]{\texttt{setHeader(name,\ value)}},
\hyperref[requestgetheadername]{\texttt{getHeader(name)}},
\hyperref[requestremoveheadername]{\texttt{removeHeader(name)}} API. The
actual header will be sent along with the first data chunk or when
calling
\hyperref[requestenddata-encoding-callback]{\texttt{request.end()}}.

To get the response, add a listener for
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
to the request object.
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
will be emitted from the request object when the response headers have
been received. The
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
event is executed with one argument which is an instance of
\hyperref[class-httpincomingmessage]{\texttt{http.IncomingMessage}}.

During the
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
event, one can add listeners to the response object; particularly to
listen for the \texttt{\textquotesingle{}data\textquotesingle{}} event.

If no
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
handler is added, then the response will be entirely discarded. However,
if a
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
event handler is added, then the data from the response object
\textbf{must} be consumed, either by calling \texttt{response.read()}
whenever there is a
\texttt{\textquotesingle{}readable\textquotesingle{}} event, or by
adding a \texttt{\textquotesingle{}data\textquotesingle{}} handler, or
by calling the \texttt{.resume()} method. Until the data is consumed,
the \texttt{\textquotesingle{}end\textquotesingle{}} event will not
fire. Also, until the data is read it will consume memory that can
eventually lead to a `process out of memory' error.

For backward compatibility, \texttt{res} will only emit
\texttt{\textquotesingle{}error\textquotesingle{}} if there is an
\texttt{\textquotesingle{}error\textquotesingle{}} listener registered.

Set \texttt{Content-Length} header to limit the response body size. If
\hyperref[responsestrictcontentlength]{\texttt{response.strictContentLength}}
is set to \texttt{true}, mismatching the \texttt{Content-Length} header
value will result in an \texttt{Error} being thrown, identified by
\texttt{code:}
\href{errors.md\#err_http_content_length_mismatch}{\texttt{\textquotesingle{}ERR\_HTTP\_CONTENT\_LENGTH\_MISMATCH\textquotesingle{}}}.

\texttt{Content-Length} value should be in bytes, not characters. Use
\href{buffer.md\#static-method-bufferbytelengthstring-encoding}{\texttt{Buffer.byteLength()}}
to determine the length of the body in bytes.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}abort\textquotesingle{}}}{Event: \textquotesingle abort\textquotesingle{}}}\label{event-abort}

\begin{quote}
Stability: 0 - Deprecated. Listen for the
\texttt{\textquotesingle{}close\textquotesingle{}} event instead.
\end{quote}

Emitted when the request has been aborted by the client. This event is
only emitted on the first call to \texttt{abort()}.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}close\textquotesingle{}}}{Event: \textquotesingle close\textquotesingle{}}}\label{event-close}

Indicates that the request is completed, or its underlying connection
was terminated prematurely (before the response completion).

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}connect\textquotesingle{}}}{Event: \textquotesingle connect\textquotesingle{}}}\label{event-connect}

\begin{itemize}
\tightlist
\item
  \texttt{response} \{http.IncomingMessage\}
\item
  \texttt{socket} \{stream.Duplex\}
\item
  \texttt{head} \{Buffer\}
\end{itemize}

Emitted each time a server responds to a request with a \texttt{CONNECT}
method. If this event is not being listened for, clients receiving a
\texttt{CONNECT} method will have their connections closed.

This event is guaranteed to be passed an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

A client and server pair demonstrating how to listen for the
\texttt{\textquotesingle{}connect\textquotesingle{}} event:

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ \{ createServer}\OperatorTok{,}\NormalTok{ request \} }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}
\ImportTok{import}\NormalTok{ \{ connect \} }\ImportTok{from} \StringTok{\textquotesingle{}node:net\textquotesingle{}}\OperatorTok{;}
\ImportTok{import}\NormalTok{ \{ URL \} }\ImportTok{from} \StringTok{\textquotesingle{}node:url\textquotesingle{}}\OperatorTok{;}

\CommentTok{// Create an HTTP tunneling proxy}
\KeywordTok{const}\NormalTok{ proxy }\OperatorTok{=} \FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}okay\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{proxy}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}connect\textquotesingle{}}\OperatorTok{,}\NormalTok{ (req}\OperatorTok{,}\NormalTok{ clientSocket}\OperatorTok{,}\NormalTok{ head) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \CommentTok{// Connect to an origin server}
  \KeywordTok{const}\NormalTok{ \{ port}\OperatorTok{,}\NormalTok{ hostname \} }\OperatorTok{=} \KeywordTok{new} \FunctionTok{URL}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}http://}\SpecialCharTok{$\{}\NormalTok{req}\OperatorTok{.}\AttributeTok{url}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
  \KeywordTok{const}\NormalTok{ serverSocket }\OperatorTok{=} \FunctionTok{connect}\NormalTok{(port }\OperatorTok{||} \DecValTok{80}\OperatorTok{,}\NormalTok{ hostname}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{    clientSocket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}HTTP/1.1 200 Connection Established}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                    \StringTok{\textquotesingle{}Proxy{-}agent: Node.js{-}Proxy}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                    \StringTok{\textquotesingle{}}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    serverSocket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(head)}\OperatorTok{;}
\NormalTok{    serverSocket}\OperatorTok{.}\FunctionTok{pipe}\NormalTok{(clientSocket)}\OperatorTok{;}
\NormalTok{    clientSocket}\OperatorTok{.}\FunctionTok{pipe}\NormalTok{(serverSocket)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\CommentTok{// Now that proxy is running}
\NormalTok{proxy}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{1337}\OperatorTok{,} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}

  \CommentTok{// Make a request to a tunneling proxy}
  \KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
    \DataTypeTok{port}\OperatorTok{:} \DecValTok{1337}\OperatorTok{,}
    \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}
    \DataTypeTok{method}\OperatorTok{:} \StringTok{\textquotesingle{}CONNECT\textquotesingle{}}\OperatorTok{,}
    \DataTypeTok{path}\OperatorTok{:} \StringTok{\textquotesingle{}www.google.com:80\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \}}\OperatorTok{;}

  \KeywordTok{const}\NormalTok{ req }\OperatorTok{=} \FunctionTok{request}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{  req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}

\NormalTok{  req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}connect\textquotesingle{}}\OperatorTok{,}\NormalTok{ (res}\OperatorTok{,}\NormalTok{ socket}\OperatorTok{,}\NormalTok{ head) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}got connected!\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

    \CommentTok{// Make a request over an HTTP tunnel}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}GET / HTTP/1.1}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                 \StringTok{\textquotesingle{}Host: www.google.com:80}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                 \StringTok{\textquotesingle{}Connection: close}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                 \StringTok{\textquotesingle{}}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}data\textquotesingle{}}\OperatorTok{,}\NormalTok{ (chunk) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(chunk}\OperatorTok{.}\FunctionTok{toString}\NormalTok{())}\OperatorTok{;}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}end\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{      proxy}\OperatorTok{.}\FunctionTok{close}\NormalTok{()}\OperatorTok{;}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ net }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:net\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ \{ URL \} }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:url\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\CommentTok{// Create an HTTP tunneling proxy}
\KeywordTok{const}\NormalTok{ proxy }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}okay\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{proxy}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}connect\textquotesingle{}}\OperatorTok{,}\NormalTok{ (req}\OperatorTok{,}\NormalTok{ clientSocket}\OperatorTok{,}\NormalTok{ head) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \CommentTok{// Connect to an origin server}
  \KeywordTok{const}\NormalTok{ \{ port}\OperatorTok{,}\NormalTok{ hostname \} }\OperatorTok{=} \KeywordTok{new} \FunctionTok{URL}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}http://}\SpecialCharTok{$\{}\NormalTok{req}\OperatorTok{.}\AttributeTok{url}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
  \KeywordTok{const}\NormalTok{ serverSocket }\OperatorTok{=}\NormalTok{ net}\OperatorTok{.}\FunctionTok{connect}\NormalTok{(port }\OperatorTok{||} \DecValTok{80}\OperatorTok{,}\NormalTok{ hostname}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{    clientSocket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}HTTP/1.1 200 Connection Established}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                    \StringTok{\textquotesingle{}Proxy{-}agent: Node.js{-}Proxy}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                    \StringTok{\textquotesingle{}}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    serverSocket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(head)}\OperatorTok{;}
\NormalTok{    serverSocket}\OperatorTok{.}\FunctionTok{pipe}\NormalTok{(clientSocket)}\OperatorTok{;}
\NormalTok{    clientSocket}\OperatorTok{.}\FunctionTok{pipe}\NormalTok{(serverSocket)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\CommentTok{// Now that proxy is running}
\NormalTok{proxy}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{1337}\OperatorTok{,} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}

  \CommentTok{// Make a request to a tunneling proxy}
  \KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
    \DataTypeTok{port}\OperatorTok{:} \DecValTok{1337}\OperatorTok{,}
    \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}
    \DataTypeTok{method}\OperatorTok{:} \StringTok{\textquotesingle{}CONNECT\textquotesingle{}}\OperatorTok{,}
    \DataTypeTok{path}\OperatorTok{:} \StringTok{\textquotesingle{}www.google.com:80\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \}}\OperatorTok{;}

  \KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{  req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}

\NormalTok{  req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}connect\textquotesingle{}}\OperatorTok{,}\NormalTok{ (res}\OperatorTok{,}\NormalTok{ socket}\OperatorTok{,}\NormalTok{ head) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}got connected!\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

    \CommentTok{// Make a request over an HTTP tunnel}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}GET / HTTP/1.1}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                 \StringTok{\textquotesingle{}Host: www.google.com:80}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                 \StringTok{\textquotesingle{}Connection: close}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                 \StringTok{\textquotesingle{}}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}data\textquotesingle{}}\OperatorTok{,}\NormalTok{ (chunk) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(chunk}\OperatorTok{.}\FunctionTok{toString}\NormalTok{())}\OperatorTok{;}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}end\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{      proxy}\OperatorTok{.}\FunctionTok{close}\NormalTok{()}\OperatorTok{;}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}continue\textquotesingle{}}}{Event: \textquotesingle continue\textquotesingle{}}}\label{event-continue}

Emitted when the server sends a `100 Continue' HTTP response, usually
because the request contained `Expect: 100-continue'. This is an
instruction that the client should send the request body.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}finish\textquotesingle{}}}{Event: \textquotesingle finish\textquotesingle{}}}\label{event-finish}

Emitted when the request has been sent. More specifically, this event is
emitted when the last segment of the response headers and body have been
handed off to the operating system for transmission over the network. It
does not imply that the server has received anything yet.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}information\textquotesingle{}}}{Event: \textquotesingle information\textquotesingle{}}}\label{event-information}

\begin{itemize}
\tightlist
\item
  \texttt{info} \{Object\}

  \begin{itemize}
  \tightlist
  \item
    \texttt{httpVersion} \{string\}
  \item
    \texttt{httpVersionMajor} \{integer\}
  \item
    \texttt{httpVersionMinor} \{integer\}
  \item
    \texttt{statusCode} \{integer\}
  \item
    \texttt{statusMessage} \{string\}
  \item
    \texttt{headers} \{Object\}
  \item
    \texttt{rawHeaders} \{string{[}{]}\}
  \end{itemize}
\end{itemize}

Emitted when the server sends a 1xx intermediate response (excluding 101
Upgrade). The listeners of this event will receive an object containing
the HTTP version, status code, status message, key-value headers object,
and array with the raw header names followed by their respective values.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ \{ request \} }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
  \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{port}\OperatorTok{:} \DecValTok{8080}\OperatorTok{,}
  \DataTypeTok{path}\OperatorTok{:} \StringTok{\textquotesingle{}/length\_request\textquotesingle{}}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{;}

\CommentTok{// Make a request}
\KeywordTok{const}\NormalTok{ req }\OperatorTok{=} \FunctionTok{request}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}

\NormalTok{req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}information\textquotesingle{}}\OperatorTok{,}\NormalTok{ (info) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}Got information prior to main response: }\SpecialCharTok{$\{}\NormalTok{info}\OperatorTok{.}\AttributeTok{statusCode}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
  \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{port}\OperatorTok{:} \DecValTok{8080}\OperatorTok{,}
  \DataTypeTok{path}\OperatorTok{:} \StringTok{\textquotesingle{}/length\_request\textquotesingle{}}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{;}

\CommentTok{// Make a request}
\KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}

\NormalTok{req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}information\textquotesingle{}}\OperatorTok{,}\NormalTok{ (info) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}Got information prior to main response: }\SpecialCharTok{$\{}\NormalTok{info}\OperatorTok{.}\AttributeTok{statusCode}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

101 Upgrade statuses do not fire this event due to their break from the
traditional HTTP request/response chain, such as web sockets, in-place
TLS upgrades, or HTTP 2.0. To be notified of 101 Upgrade notices, listen
for the
\hyperref[event-upgrade]{\texttt{\textquotesingle{}upgrade\textquotesingle{}}}
event instead.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}response\textquotesingle{}}}{Event: \textquotesingle response\textquotesingle{}}}\label{event-response}

\begin{itemize}
\tightlist
\item
  \texttt{response} \{http.IncomingMessage\}
\end{itemize}

Emitted when a response is received to this request. This event is
emitted only once.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}socket\textquotesingle{}}}{Event: \textquotesingle socket\textquotesingle{}}}\label{event-socket}

\begin{itemize}
\tightlist
\item
  \texttt{socket} \{stream.Duplex\}
\end{itemize}

This event is guaranteed to be passed an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}timeout\textquotesingle{}}}{Event: \textquotesingle timeout\textquotesingle{}}}\label{event-timeout}

Emitted when the underlying socket times out from inactivity. This only
notifies that the socket has been idle. The request must be destroyed
manually.

See also:
\hyperref[requestsettimeouttimeout-callback]{\texttt{request.setTimeout()}}.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}upgrade\textquotesingle{}}}{Event: \textquotesingle upgrade\textquotesingle{}}}\label{event-upgrade}

\begin{itemize}
\tightlist
\item
  \texttt{response} \{http.IncomingMessage\}
\item
  \texttt{socket} \{stream.Duplex\}
\item
  \texttt{head} \{Buffer\}
\end{itemize}

Emitted each time a server responds to a request with an upgrade. If
this event is not being listened for and the response status code is 101
Switching Protocols, clients receiving an upgrade header will have their
connections closed.

This event is guaranteed to be passed an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

A client server pair demonstrating how to listen for the
\texttt{\textquotesingle{}upgrade\textquotesingle{}} event.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}
\ImportTok{import} \BuiltInTok{process} \ImportTok{from} \StringTok{\textquotesingle{}node:process\textquotesingle{}}\OperatorTok{;}

\CommentTok{// Create an HTTP server}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}okay\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{server}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}upgrade\textquotesingle{}}\OperatorTok{,}\NormalTok{ (req}\OperatorTok{,}\NormalTok{ socket}\OperatorTok{,}\NormalTok{ head) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  socket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}HTTP/1.1 101 Web Socket Protocol Handshake}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
               \StringTok{\textquotesingle{}Upgrade: WebSocket}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
               \StringTok{\textquotesingle{}Connection: Upgrade}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
               \StringTok{\textquotesingle{}}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\NormalTok{  socket}\OperatorTok{.}\FunctionTok{pipe}\NormalTok{(socket)}\OperatorTok{;} \CommentTok{// echo back}
\NormalTok{\})}\OperatorTok{;}

\CommentTok{// Now that server is running}
\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{1337}\OperatorTok{,} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}

  \CommentTok{// make a request}
  \KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
    \DataTypeTok{port}\OperatorTok{:} \DecValTok{1337}\OperatorTok{,}
    \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}
    \DataTypeTok{headers}\OperatorTok{:}\NormalTok{ \{}
      \StringTok{\textquotesingle{}Connection\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}Upgrade\textquotesingle{}}\OperatorTok{,}
      \StringTok{\textquotesingle{}Upgrade\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}websocket\textquotesingle{}}\OperatorTok{,}
\NormalTok{    \}}\OperatorTok{,}
\NormalTok{  \}}\OperatorTok{;}

  \KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{  req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}

\NormalTok{  req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}upgrade\textquotesingle{}}\OperatorTok{,}\NormalTok{ (res}\OperatorTok{,}\NormalTok{ socket}\OperatorTok{,}\NormalTok{ upgradeHead) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}got upgraded!\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
    \BuiltInTok{process}\OperatorTok{.}\FunctionTok{exit}\NormalTok{(}\DecValTok{0}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\CommentTok{// Create an HTTP server}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}okay\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{server}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}upgrade\textquotesingle{}}\OperatorTok{,}\NormalTok{ (req}\OperatorTok{,}\NormalTok{ socket}\OperatorTok{,}\NormalTok{ head) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  socket}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}HTTP/1.1 101 Web Socket Protocol Handshake}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
               \StringTok{\textquotesingle{}Upgrade: WebSocket}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
               \StringTok{\textquotesingle{}Connection: Upgrade}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
               \StringTok{\textquotesingle{}}\SpecialCharTok{\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\NormalTok{  socket}\OperatorTok{.}\FunctionTok{pipe}\NormalTok{(socket)}\OperatorTok{;} \CommentTok{// echo back}
\NormalTok{\})}\OperatorTok{;}

\CommentTok{// Now that server is running}
\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{1337}\OperatorTok{,} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}

  \CommentTok{// make a request}
  \KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
    \DataTypeTok{port}\OperatorTok{:} \DecValTok{1337}\OperatorTok{,}
    \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}
    \DataTypeTok{headers}\OperatorTok{:}\NormalTok{ \{}
      \StringTok{\textquotesingle{}Connection\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}Upgrade\textquotesingle{}}\OperatorTok{,}
      \StringTok{\textquotesingle{}Upgrade\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}websocket\textquotesingle{}}\OperatorTok{,}
\NormalTok{    \}}\OperatorTok{,}
\NormalTok{  \}}\OperatorTok{;}

  \KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{  req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}

\NormalTok{  req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}upgrade\textquotesingle{}}\OperatorTok{,}\NormalTok{ (res}\OperatorTok{,}\NormalTok{ socket}\OperatorTok{,}\NormalTok{ upgradeHead) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}got upgraded!\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    socket}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
    \BuiltInTok{process}\OperatorTok{.}\FunctionTok{exit}\NormalTok{(}\DecValTok{0}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.abort()}}{request.abort()}}\label{request.abort}

\begin{quote}
Stability: 0 - Deprecated: Use
\hyperref[requestdestroyerror]{\texttt{request.destroy()}} instead.
\end{quote}

Marks the request as aborting. Calling this will cause remaining data in
the response to be dropped and the socket to be destroyed.

\subsubsection{\texorpdfstring{\texttt{request.aborted}}{request.aborted}}\label{request.aborted}

\begin{quote}
Stability: 0 - Deprecated. Check
\hyperref[requestdestroyed]{\texttt{request.destroyed}} instead.
\end{quote}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

The \texttt{request.aborted} property will be \texttt{true} if the
request has been aborted.

\subsubsection{\texorpdfstring{\texttt{request.connection}}{request.connection}}\label{request.connection}

\begin{quote}
Stability: 0 - Deprecated. Use
\hyperref[requestsocket]{\texttt{request.socket}}.
\end{quote}

\begin{itemize}
\tightlist
\item
  \{stream.Duplex\}
\end{itemize}

See \hyperref[requestsocket]{\texttt{request.socket}}.

\subsubsection{\texorpdfstring{\texttt{request.cork()}}{request.cork()}}\label{request.cork}

See \href{stream.md\#writablecork}{\texttt{writable.cork()}}.

\subsubsection{\texorpdfstring{\texttt{request.end({[}data{[},\ encoding{]}{]}{[},\ callback{]})}}{request.end({[}data{[}, encoding{]}{]}{[}, callback{]})}}\label{request.enddata-encoding-callback}

\begin{itemize}
\tightlist
\item
  \texttt{data} \{string\textbar Buffer\textbar Uint8Array\}
\item
  \texttt{encoding} \{string\}
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{this\}
\end{itemize}

Finishes sending the request. If any parts of the body are unsent, it
will flush them to the stream. If the request is chunked, this will send
the terminating
\texttt{\textquotesingle{}0\textbackslash{}r\textbackslash{}n\textbackslash{}r\textbackslash{}n\textquotesingle{}}.

If \texttt{data} is specified, it is equivalent to calling
\hyperref[requestwritechunk-encoding-callback]{\texttt{request.write(data,\ encoding)}}
followed by \texttt{request.end(callback)}.

If \texttt{callback} is specified, it will be called when the request
stream is finished.

\subsubsection{\texorpdfstring{\texttt{request.destroy({[}error{]})}}{request.destroy({[}error{]})}}\label{request.destroyerror}

\begin{itemize}
\tightlist
\item
  \texttt{error} \{Error\} Optional, an error to emit with
  \texttt{\textquotesingle{}error\textquotesingle{}} event.
\item
  Returns: \{this\}
\end{itemize}

Destroy the request. Optionally emit an
\texttt{\textquotesingle{}error\textquotesingle{}} event, and emit a
\texttt{\textquotesingle{}close\textquotesingle{}} event. Calling this
will cause remaining data in the response to be dropped and the socket
to be destroyed.

See \href{stream.md\#writabledestroyerror}{\texttt{writable.destroy()}}
for further details.

\paragraph{\texorpdfstring{\texttt{request.destroyed}}{request.destroyed}}\label{request.destroyed}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Is \texttt{true} after
\hyperref[requestdestroyerror]{\texttt{request.destroy()}} has been
called.

See \href{stream.md\#writabledestroyed}{\texttt{writable.destroyed}} for
further details.

\subsubsection{\texorpdfstring{\texttt{request.finished}}{request.finished}}\label{request.finished}

\begin{quote}
Stability: 0 - Deprecated. Use
\hyperref[requestwritableended]{\texttt{request.writableEnded}}.
\end{quote}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

The \texttt{request.finished} property will be \texttt{true} if
\hyperref[requestenddata-encoding-callback]{\texttt{request.end()}} has
been called. \texttt{request.end()} will automatically be called if the
request was initiated via
\hyperref[httpgetoptions-callback]{\texttt{http.get()}}.

\subsubsection{\texorpdfstring{\texttt{request.flushHeaders()}}{request.flushHeaders()}}\label{request.flushheaders}

Flushes the request headers.

For efficiency reasons, Node.js normally buffers the request headers
until \texttt{request.end()} is called or the first chunk of request
data is written. It then tries to pack the request headers and data into
a single TCP packet.

That's usually desired (it saves a TCP round-trip), but not when the
first data is not sent until possibly much later.
\texttt{request.flushHeaders()} bypasses the optimization and kickstarts
the request.

\subsubsection{\texorpdfstring{\texttt{request.getHeader(name)}}{request.getHeader(name)}}\label{request.getheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  Returns: \{any\}
\end{itemize}

Reads out a header on the request. The name is case-insensitive. The
type of the return value depends on the arguments provided to
\hyperref[requestsetheadername-value]{\texttt{request.setHeader()}}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}content{-}type\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}text/html\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Length\textquotesingle{}}\OperatorTok{,} \BuiltInTok{Buffer}\OperatorTok{.}\FunctionTok{byteLength}\NormalTok{(body))}\OperatorTok{;}
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}type=ninja\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}language=javascript\textquotesingle{}}\NormalTok{])}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ contentType }\OperatorTok{=}\NormalTok{ request}\OperatorTok{.}\FunctionTok{getHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\CommentTok{// \textquotesingle{}contentType\textquotesingle{} is \textquotesingle{}text/html\textquotesingle{}}
\KeywordTok{const}\NormalTok{ contentLength }\OperatorTok{=}\NormalTok{ request}\OperatorTok{.}\FunctionTok{getHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Length\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\CommentTok{// \textquotesingle{}contentLength\textquotesingle{} is of type number}
\KeywordTok{const}\NormalTok{ cookie }\OperatorTok{=}\NormalTok{ request}\OperatorTok{.}\FunctionTok{getHeader}\NormalTok{(}\StringTok{\textquotesingle{}Cookie\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\CommentTok{// \textquotesingle{}cookie\textquotesingle{} is of type string[]}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.getHeaderNames()}}{request.getHeaderNames()}}\label{request.getheadernames}

\begin{itemize}
\tightlist
\item
  Returns: \{string{[}{]}\}
\end{itemize}

Returns an array containing the unique names of the current outgoing
headers. All header names are lowercase.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}foo=bar\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar=baz\textquotesingle{}}\NormalTok{])}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ headerNames }\OperatorTok{=}\NormalTok{ request}\OperatorTok{.}\FunctionTok{getHeaderNames}\NormalTok{()}\OperatorTok{;}
\CommentTok{// headerNames === [\textquotesingle{}foo\textquotesingle{}, \textquotesingle{}cookie\textquotesingle{}]}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.getHeaders()}}{request.getHeaders()}}\label{request.getheaders}

\begin{itemize}
\tightlist
\item
  Returns: \{Object\}
\end{itemize}

Returns a shallow copy of the current outgoing headers. Since a shallow
copy is used, array values may be mutated without additional calls to
various header-related http module methods. The keys of the returned
object are the header names and the values are the respective header
values. All header names are lowercase.

The object returned by the \texttt{request.getHeaders()} method
\emph{does not} prototypically inherit from the JavaScript
\texttt{Object}. This means that typical \texttt{Object} methods such as
\texttt{obj.toString()}, \texttt{obj.hasOwnProperty()}, and others are
not defined and \emph{will not work}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}foo=bar\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar=baz\textquotesingle{}}\NormalTok{])}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ headers }\OperatorTok{=}\NormalTok{ request}\OperatorTok{.}\FunctionTok{getHeaders}\NormalTok{()}\OperatorTok{;}
\CommentTok{// headers === \{ foo: \textquotesingle{}bar\textquotesingle{}, \textquotesingle{}cookie\textquotesingle{}: [\textquotesingle{}foo=bar\textquotesingle{}, \textquotesingle{}bar=baz\textquotesingle{}] \}}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.getRawHeaderNames()}}{request.getRawHeaderNames()}}\label{request.getrawheadernames}

\begin{itemize}
\tightlist
\item
  Returns: \{string{[}{]}\}
\end{itemize}

Returns an array containing the unique names of the current outgoing raw
headers. Header names are returned with their exact casing being set.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Set{-}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}foo=bar\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar=baz\textquotesingle{}}\NormalTok{])}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ headerNames }\OperatorTok{=}\NormalTok{ request}\OperatorTok{.}\FunctionTok{getRawHeaderNames}\NormalTok{()}\OperatorTok{;}
\CommentTok{// headerNames === [\textquotesingle{}Foo\textquotesingle{}, \textquotesingle{}Set{-}Cookie\textquotesingle{}]}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.hasHeader(name)}}{request.hasHeader(name)}}\label{request.hasheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  Returns: \{boolean\}
\end{itemize}

Returns \texttt{true} if the header identified by \texttt{name} is
currently set in the outgoing headers. The header name matching is
case-insensitive.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ hasContentType }\OperatorTok{=}\NormalTok{ request}\OperatorTok{.}\FunctionTok{hasHeader}\NormalTok{(}\StringTok{\textquotesingle{}content{-}type\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.maxHeadersCount}}{request.maxHeadersCount}}\label{request.maxheaderscount}

\begin{itemize}
\tightlist
\item
  \{number\} \textbf{Default:} \texttt{2000}
\end{itemize}

Limits maximum response headers count. If set to 0, no limit will be
applied.

\subsubsection{\texorpdfstring{\texttt{request.path}}{request.path}}\label{request.path}

\begin{itemize}
\tightlist
\item
  \{string\} The request path.
\end{itemize}

\subsubsection{\texorpdfstring{\texttt{request.method}}{request.method}}\label{request.method}

\begin{itemize}
\tightlist
\item
  \{string\} The request method.
\end{itemize}

\subsubsection{\texorpdfstring{\texttt{request.host}}{request.host}}\label{request.host}

\begin{itemize}
\tightlist
\item
  \{string\} The request host.
\end{itemize}

\subsubsection{\texorpdfstring{\texttt{request.protocol}}{request.protocol}}\label{request.protocol}

\begin{itemize}
\tightlist
\item
  \{string\} The request protocol.
\end{itemize}

\subsubsection{\texorpdfstring{\texttt{request.removeHeader(name)}}{request.removeHeader(name)}}\label{request.removeheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\end{itemize}

Removes a header that's already defined into headers object.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{request}\OperatorTok{.}\FunctionTok{removeHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.reusedSocket}}{request.reusedSocket}}\label{request.reusedsocket}

\begin{itemize}
\tightlist
\item
  \{boolean\} Whether the request is send through a reused socket.
\end{itemize}

When sending request through a keep-alive enabled agent, the underlying
socket might be reused. But if server closes connection at unfortunate
time, client may run into a `ECONNRESET' error.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}

\CommentTok{// Server has a 5 seconds keep{-}alive timeout by default}
\NormalTok{http}
  \OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{    res}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}hello}\SpecialCharTok{\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    res}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\NormalTok{  \})}
  \OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{3000}\NormalTok{)}\OperatorTok{;}

\PreprocessorTok{setInterval}\NormalTok{(() }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \CommentTok{// Adapting a keep{-}alive agent}
\NormalTok{  http}\OperatorTok{.}\FunctionTok{get}\NormalTok{(}\StringTok{\textquotesingle{}http://localhost:3000\textquotesingle{}}\OperatorTok{,}\NormalTok{ \{ agent \}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{    res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}data\textquotesingle{}}\OperatorTok{,}\NormalTok{ (data) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \CommentTok{// Do nothing}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\}}\OperatorTok{,} \DecValTok{5000}\NormalTok{)}\OperatorTok{;} \CommentTok{// Sending request on 5s interval so it\textquotesingle{}s easy to hit idle timeout}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\CommentTok{// Server has a 5 seconds keep{-}alive timeout by default}
\NormalTok{http}
  \OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{    res}\OperatorTok{.}\FunctionTok{write}\NormalTok{(}\StringTok{\textquotesingle{}hello}\SpecialCharTok{\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{    res}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\NormalTok{  \})}
  \OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{3000}\NormalTok{)}\OperatorTok{;}

\PreprocessorTok{setInterval}\NormalTok{(() }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \CommentTok{// Adapting a keep{-}alive agent}
\NormalTok{  http}\OperatorTok{.}\FunctionTok{get}\NormalTok{(}\StringTok{\textquotesingle{}http://localhost:3000\textquotesingle{}}\OperatorTok{,}\NormalTok{ \{ agent \}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{    res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}data\textquotesingle{}}\OperatorTok{,}\NormalTok{ (data) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \CommentTok{// Do nothing}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\}}\OperatorTok{,} \DecValTok{5000}\NormalTok{)}\OperatorTok{;} \CommentTok{// Sending request on 5s interval so it\textquotesingle{}s easy to hit idle timeout}
\end{Highlighting}
\end{Shaded}

By marking a request whether it reused socket or not, we can do
automatic error retry base on it.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ agent }\OperatorTok{=} \KeywordTok{new}\NormalTok{ http}\OperatorTok{.}\FunctionTok{Agent}\NormalTok{(\{ }\DataTypeTok{keepAlive}\OperatorTok{:} \KeywordTok{true}\NormalTok{ \})}\OperatorTok{;}

\KeywordTok{function} \FunctionTok{retriableRequest}\NormalTok{() \{}
  \KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}
    \OperatorTok{.}\FunctionTok{get}\NormalTok{(}\StringTok{\textquotesingle{}http://localhost:3000\textquotesingle{}}\OperatorTok{,}\NormalTok{ \{ agent \}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \CommentTok{// ...}
\NormalTok{    \})}
    \OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}error\textquotesingle{}}\OperatorTok{,}\NormalTok{ (err) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \CommentTok{// Check if retry is needed}
      \ControlFlowTok{if}\NormalTok{ (req}\OperatorTok{.}\AttributeTok{reusedSocket} \OperatorTok{\&\&}\NormalTok{ err}\OperatorTok{.}\AttributeTok{code} \OperatorTok{===} \StringTok{\textquotesingle{}ECONNRESET\textquotesingle{}}\NormalTok{) \{}
        \FunctionTok{retriableRequest}\NormalTok{()}\OperatorTok{;}
\NormalTok{      \}}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{\}}

\FunctionTok{retriableRequest}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ agent }\OperatorTok{=} \KeywordTok{new}\NormalTok{ http}\OperatorTok{.}\FunctionTok{Agent}\NormalTok{(\{ }\DataTypeTok{keepAlive}\OperatorTok{:} \KeywordTok{true}\NormalTok{ \})}\OperatorTok{;}

\KeywordTok{function} \FunctionTok{retriableRequest}\NormalTok{() \{}
  \KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}
    \OperatorTok{.}\FunctionTok{get}\NormalTok{(}\StringTok{\textquotesingle{}http://localhost:3000\textquotesingle{}}\OperatorTok{,}\NormalTok{ \{ agent \}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \CommentTok{// ...}
\NormalTok{    \})}
    \OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}error\textquotesingle{}}\OperatorTok{,}\NormalTok{ (err) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
      \CommentTok{// Check if retry is needed}
      \ControlFlowTok{if}\NormalTok{ (req}\OperatorTok{.}\AttributeTok{reusedSocket} \OperatorTok{\&\&}\NormalTok{ err}\OperatorTok{.}\AttributeTok{code} \OperatorTok{===} \StringTok{\textquotesingle{}ECONNRESET\textquotesingle{}}\NormalTok{) \{}
        \FunctionTok{retriableRequest}\NormalTok{()}\OperatorTok{;}
\NormalTok{      \}}
\NormalTok{    \})}\OperatorTok{;}
\NormalTok{\}}

\FunctionTok{retriableRequest}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.setHeader(name,\ value)}}{request.setHeader(name, value)}}\label{request.setheadername-value}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  \texttt{value} \{any\}
\end{itemize}

Sets a single header value for headers object. If this header already
exists in the to-be-sent headers, its value will be replaced. Use an
array of strings here to send multiple headers with the same name.
Non-string values will be stored without modification. Therefore,
\hyperref[requestgetheadername]{\texttt{request.getHeader()}} may return
non-string values. However, the non-string values will be converted to
strings for network transmission.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

or

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}type=ninja\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}language=javascript\textquotesingle{}}\NormalTok{])}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

When the value is a string an exception will be thrown if it contains
characters outside the \texttt{latin1} encoding.

If you need to pass UTF-8 characters in the value please encode the
value using the \href{https://www.rfc-editor.org/rfc/rfc8187.txt}{RFC
8187} standard.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ filename }\OperatorTok{=} \StringTok{\textquotesingle{}Rock .txt\textquotesingle{}}\OperatorTok{;}
\NormalTok{request}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Disposition\textquotesingle{}}\OperatorTok{,} \VerbatimStringTok{\textasciigrave{}attachment; filename*=utf{-}8\textquotesingle{}\textquotesingle{}}\SpecialCharTok{$\{}\PreprocessorTok{encodeURIComponent}\NormalTok{(filename)}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{request.setNoDelay({[}noDelay{]})}}{request.setNoDelay({[}noDelay{]})}}\label{request.setnodelaynodelay}

\begin{itemize}
\tightlist
\item
  \texttt{noDelay} \{boolean\}
\end{itemize}

Once a socket is assigned to this request and is connected
\href{net.md\#socketsetnodelaynodelay}{\texttt{socket.setNoDelay()}}
will be called.

\subsubsection{\texorpdfstring{\texttt{request.setSocketKeepAlive({[}enable{]}{[},\ initialDelay{]})}}{request.setSocketKeepAlive({[}enable{]}{[}, initialDelay{]})}}\label{request.setsocketkeepaliveenable-initialdelay}

\begin{itemize}
\tightlist
\item
  \texttt{enable} \{boolean\}
\item
  \texttt{initialDelay} \{number\}
\end{itemize}

Once a socket is assigned to this request and is connected
\href{net.md\#socketsetkeepaliveenable-initialdelay}{\texttt{socket.setKeepAlive()}}
will be called.

\subsubsection{\texorpdfstring{\texttt{request.setTimeout(timeout{[},\ callback{]})}}{request.setTimeout(timeout{[}, callback{]})}}\label{request.settimeouttimeout-callback}

\begin{itemize}
\tightlist
\item
  \texttt{timeout} \{number\} Milliseconds before a request times out.
\item
  \texttt{callback} \{Function\} Optional function to be called when a
  timeout occurs. Same as binding to the
  \texttt{\textquotesingle{}timeout\textquotesingle{}} event.
\item
  Returns: \{http.ClientRequest\}
\end{itemize}

Once a socket is assigned to this request and is connected
\href{net.md\#socketsettimeouttimeout-callback}{\texttt{socket.setTimeout()}}
will be called.

\subsubsection{\texorpdfstring{\texttt{request.socket}}{request.socket}}\label{request.socket}

\begin{itemize}
\tightlist
\item
  \{stream.Duplex\}
\end{itemize}

Reference to the underlying socket. Usually users will not want to
access this property. In particular, the socket will not emit
\texttt{\textquotesingle{}readable\textquotesingle{}} events because of
how the protocol parser attaches to the socket.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
  \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}www.google.com\textquotesingle{}}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{get}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{once}\NormalTok{(}\StringTok{\textquotesingle{}response\textquotesingle{}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \KeywordTok{const}\NormalTok{ ip }\OperatorTok{=}\NormalTok{ req}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{localAddress}\OperatorTok{;}
  \KeywordTok{const}\NormalTok{ port }\OperatorTok{=}\NormalTok{ req}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{localPort}\OperatorTok{;}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}Your IP address is }\SpecialCharTok{$\{}\NormalTok{ip}\SpecialCharTok{\}}\VerbatimStringTok{ and your source port is }\SpecialCharTok{$\{}\NormalTok{port}\SpecialCharTok{\}}\VerbatimStringTok{.\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
  \CommentTok{// Consume response object}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
  \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}www.google.com\textquotesingle{}}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{get}\NormalTok{(options)}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{once}\NormalTok{(}\StringTok{\textquotesingle{}response\textquotesingle{}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \KeywordTok{const}\NormalTok{ ip }\OperatorTok{=}\NormalTok{ req}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{localAddress}\OperatorTok{;}
  \KeywordTok{const}\NormalTok{ port }\OperatorTok{=}\NormalTok{ req}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{localPort}\OperatorTok{;}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}Your IP address is }\SpecialCharTok{$\{}\NormalTok{ip}\SpecialCharTok{\}}\VerbatimStringTok{ and your source port is }\SpecialCharTok{$\{}\NormalTok{port}\SpecialCharTok{\}}\VerbatimStringTok{.\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
  \CommentTok{// Consume response object}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

This property is guaranteed to be an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specified a
socket type other than \{net.Socket\}.

\subsubsection{\texorpdfstring{\texttt{request.uncork()}}{request.uncork()}}\label{request.uncork}

See \href{stream.md\#writableuncork}{\texttt{writable.uncork()}}.

\subsubsection{\texorpdfstring{\texttt{request.writableEnded}}{request.writableEnded}}\label{request.writableended}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Is \texttt{true} after
\hyperref[requestenddata-encoding-callback]{\texttt{request.end()}} has
been called. This property does not indicate whether the data has been
flushed, for this use
\hyperref[requestwritablefinished]{\texttt{request.writableFinished}}
instead.

\subsubsection{\texorpdfstring{\texttt{request.writableFinished}}{request.writableFinished}}\label{request.writablefinished}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Is \texttt{true} if all data has been flushed to the underlying system,
immediately before the
\hyperref[event-finish]{\texttt{\textquotesingle{}finish\textquotesingle{}}}
event is emitted.

\subsubsection{\texorpdfstring{\texttt{request.write(chunk{[},\ encoding{]}{[},\ callback{]})}}{request.write(chunk{[}, encoding{]}{[}, callback{]})}}\label{request.writechunk-encoding-callback}

\begin{itemize}
\tightlist
\item
  \texttt{chunk} \{string\textbar Buffer\textbar Uint8Array\}
\item
  \texttt{encoding} \{string\}
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{boolean\}
\end{itemize}

Sends a chunk of the body. This method can be called multiple times. If
no \texttt{Content-Length} is set, data will automatically be encoded in
HTTP Chunked transfer encoding, so that server knows when the data ends.
The \texttt{Transfer-Encoding:\ chunked} header is added. Calling
\hyperref[requestenddata-encoding-callback]{\texttt{request.end()}} is
necessary to finish sending the request.

The \texttt{encoding} argument is optional and only applies when
\texttt{chunk} is a string. Defaults to
\texttt{\textquotesingle{}utf8\textquotesingle{}}.

The \texttt{callback} argument is optional and will be called when this
chunk of data is flushed, but only if the chunk is non-empty.

Returns \texttt{true} if the entire data was flushed successfully to the
kernel buffer. Returns \texttt{false} if all or part of the data was
queued in user memory.
\texttt{\textquotesingle{}drain\textquotesingle{}} will be emitted when
the buffer is free again.

When \texttt{write} function is called with empty string or buffer, it
does nothing and waits for more input.

\subsection{\texorpdfstring{Class:
\texttt{http.Server}}{Class: http.Server}}\label{class-http.server}

\begin{itemize}
\tightlist
\item
  Extends: \{net.Server\}
\end{itemize}

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}checkContinue\textquotesingle{}}}{Event: \textquotesingle checkContinue\textquotesingle{}}}\label{event-checkcontinue}

\begin{itemize}
\tightlist
\item
  \texttt{request} \{http.IncomingMessage\}
\item
  \texttt{response} \{http.ServerResponse\}
\end{itemize}

Emitted each time a request with an HTTP \texttt{Expect:\ 100-continue}
is received. If this event is not listened for, the server will
automatically respond with a \texttt{100\ Continue} as appropriate.

Handling this event involves calling
\hyperref[responsewritecontinue]{\texttt{response.writeContinue()}} if
the client should continue to send the request body, or generating an
appropriate HTTP response (e.g.~400 Bad Request) if the client should
not continue to send the request body.

When this event is emitted and handled, the
\hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
event will not be emitted.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}checkExpectation\textquotesingle{}}}{Event: \textquotesingle checkExpectation\textquotesingle{}}}\label{event-checkexpectation}

\begin{itemize}
\tightlist
\item
  \texttt{request} \{http.IncomingMessage\}
\item
  \texttt{response} \{http.ServerResponse\}
\end{itemize}

Emitted each time a request with an HTTP \texttt{Expect} header is
received, where the value is not \texttt{100-continue}. If this event is
not listened for, the server will automatically respond with a
\texttt{417\ Expectation\ Failed} as appropriate.

When this event is emitted and handled, the
\hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
event will not be emitted.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}clientError\textquotesingle{}}}{Event: \textquotesingle clientError\textquotesingle{}}}\label{event-clienterror}

\begin{itemize}
\tightlist
\item
  \texttt{exception} \{Error\}
\item
  \texttt{socket} \{stream.Duplex\}
\end{itemize}

If a client connection emits an
\texttt{\textquotesingle{}error\textquotesingle{}} event, it will be
forwarded here. Listener of this event is responsible for
closing/destroying the underlying socket. For example, one may wish to
more gracefully close the socket with a custom HTTP response instead of
abruptly severing the connection. The socket \textbf{must be closed or
destroyed} before the listener ends.

This event is guaranteed to be passed an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

Default behavior is to try close the socket with a HTTP `400 Bad
Request', or a HTTP `431 Request Header Fields Too Large' in the case of
a \href{errors.md\#hpe_header_overflow}{\texttt{HPE\_HEADER\_OVERFLOW}}
error. If the socket is not writable or headers of the current attached
\hyperref[class-httpserverresponse]{\texttt{http.ServerResponse}} has
been sent, it is immediately destroyed.

\texttt{socket} is the
\href{net.md\#class-netsocket}{\texttt{net.Socket}} object that the
error originated from.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{server}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}clientError\textquotesingle{}}\OperatorTok{,}\NormalTok{ (err}\OperatorTok{,}\NormalTok{ socket) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  socket}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}HTTP/1.1 400 Bad Request}\SpecialCharTok{\textbackslash{}r\textbackslash{}n\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{8000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{server}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}clientError\textquotesingle{}}\OperatorTok{,}\NormalTok{ (err}\OperatorTok{,}\NormalTok{ socket) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  socket}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}HTTP/1.1 400 Bad Request}\SpecialCharTok{\textbackslash{}r\textbackslash{}n\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{8000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

When the \texttt{\textquotesingle{}clientError\textquotesingle{}} event
occurs, there is no \texttt{request} or \texttt{response} object, so any
HTTP response sent, including response headers and payload, \emph{must}
be written directly to the \texttt{socket} object. Care must be taken to
ensure the response is a properly formatted HTTP response message.

\texttt{err} is an instance of \texttt{Error} with two extra columns:

\begin{itemize}
\tightlist
\item
  \texttt{bytesParsed}: the bytes count of request packet that Node.js
  may have parsed correctly;
\item
  \texttt{rawPacket}: the raw packet of current request.
\end{itemize}

In some cases, the client has already received the response and/or the
socket has already been destroyed, like in case of \texttt{ECONNRESET}
errors. Before trying to send data to the socket, it is better to check
that it is still writable.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{server}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}clientError\textquotesingle{}}\OperatorTok{,}\NormalTok{ (err}\OperatorTok{,}\NormalTok{ socket) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \ControlFlowTok{if}\NormalTok{ (err}\OperatorTok{.}\AttributeTok{code} \OperatorTok{===} \StringTok{\textquotesingle{}ECONNRESET\textquotesingle{}} \OperatorTok{||} \OperatorTok{!}\NormalTok{socket}\OperatorTok{.}\AttributeTok{writable}\NormalTok{) \{}
    \ControlFlowTok{return}\OperatorTok{;}
\NormalTok{  \}}

\NormalTok{  socket}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}HTTP/1.1 400 Bad Request}\SpecialCharTok{\textbackslash{}r\textbackslash{}n\textbackslash{}r\textbackslash{}n}\StringTok{\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}close\textquotesingle{}}}{Event: \textquotesingle close\textquotesingle{}}}\label{event-close-1}

Emitted when the server closes.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}connect\textquotesingle{}}}{Event: \textquotesingle connect\textquotesingle{}}}\label{event-connect-1}

\begin{itemize}
\tightlist
\item
  \texttt{request} \{http.IncomingMessage\} Arguments for the HTTP
  request, as it is in the
  \hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
  event
\item
  \texttt{socket} \{stream.Duplex\} Network socket between the server
  and client
\item
  \texttt{head} \{Buffer\} The first packet of the tunneling stream (may
  be empty)
\end{itemize}

Emitted each time a client requests an HTTP \texttt{CONNECT} method. If
this event is not listened for, then clients requesting a
\texttt{CONNECT} method will have their connections closed.

This event is guaranteed to be passed an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

After this event is emitted, the request's socket will not have a
\texttt{\textquotesingle{}data\textquotesingle{}} event listener,
meaning it will need to be bound in order to handle data sent to the
server on that socket.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}connection\textquotesingle{}}}{Event: \textquotesingle connection\textquotesingle{}}}\label{event-connection}

\begin{itemize}
\tightlist
\item
  \texttt{socket} \{stream.Duplex\}
\end{itemize}

This event is emitted when a new TCP stream is established.
\texttt{socket} is typically an object of type
\href{net.md\#class-netsocket}{\texttt{net.Socket}}. Usually users will
not want to access this event. In particular, the socket will not emit
\texttt{\textquotesingle{}readable\textquotesingle{}} events because of
how the protocol parser attaches to the socket. The \texttt{socket} can
also be accessed at \texttt{request.socket}.

This event can also be explicitly emitted by users to inject connections
into the HTTP server. In that case, any
\href{stream.md\#class-streamduplex}{\texttt{Duplex}} stream can be
passed.

If \texttt{socket.setTimeout()} is called here, the timeout will be
replaced with \texttt{server.keepAliveTimeout} when the socket has
served a request (if \texttt{server.keepAliveTimeout} is non-zero).

This event is guaranteed to be passed an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}dropRequest\textquotesingle{}}}{Event: \textquotesingle dropRequest\textquotesingle{}}}\label{event-droprequest}

\begin{itemize}
\tightlist
\item
  \texttt{request} \{http.IncomingMessage\} Arguments for the HTTP
  request, as it is in the
  \hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
  event
\item
  \texttt{socket} \{stream.Duplex\} Network socket between the server
  and client
\end{itemize}

When the number of requests on a socket reaches the threshold of
\texttt{server.maxRequestsPerSocket}, the server will drop new requests
and emit \texttt{\textquotesingle{}dropRequest\textquotesingle{}} event
instead, then send \texttt{503} to client.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}request\textquotesingle{}}}{Event: \textquotesingle request\textquotesingle{}}}\label{event-request}

\begin{itemize}
\tightlist
\item
  \texttt{request} \{http.IncomingMessage\}
\item
  \texttt{response} \{http.ServerResponse\}
\end{itemize}

Emitted each time there is a request. There may be multiple requests per
connection (in the case of HTTP Keep-Alive connections).

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}upgrade\textquotesingle{}}}{Event: \textquotesingle upgrade\textquotesingle{}}}\label{event-upgrade-1}

\begin{itemize}
\tightlist
\item
  \texttt{request} \{http.IncomingMessage\} Arguments for the HTTP
  request, as it is in the
  \hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
  event
\item
  \texttt{socket} \{stream.Duplex\} Network socket between the server
  and client
\item
  \texttt{head} \{Buffer\} The first packet of the upgraded stream (may
  be empty)
\end{itemize}

Emitted each time a client requests an HTTP upgrade. Listening to this
event is optional and clients cannot insist on a protocol change.

After this event is emitted, the request's socket will not have a
\texttt{\textquotesingle{}data\textquotesingle{}} event listener,
meaning it will need to be bound in order to handle data sent to the
server on that socket.

This event is guaranteed to be passed an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specifies a
socket type other than \{net.Socket\}.

\subsubsection{\texorpdfstring{\texttt{server.close({[}callback{]})}}{server.close({[}callback{]})}}\label{server.closecallback}

\begin{itemize}
\tightlist
\item
  \texttt{callback} \{Function\}
\end{itemize}

Stops the server from accepting new connections and closes all
connections connected to this server which are not sending a request or
waiting for a response. See
\href{net.md\#serverclosecallback}{\texttt{net.Server.close()}}.

\subsubsection{\texorpdfstring{\texttt{server.closeAllConnections()}}{server.closeAllConnections()}}\label{server.closeallconnections}

Closes all connections connected to this server.

\subsubsection{\texorpdfstring{\texttt{server.closeIdleConnections()}}{server.closeIdleConnections()}}\label{server.closeidleconnections}

Closes all connections connected to this server which are not sending a
request or waiting for a response.

\subsubsection{\texorpdfstring{\texttt{server.headersTimeout}}{server.headersTimeout}}\label{server.headerstimeout}

\begin{itemize}
\tightlist
\item
  \{number\} \textbf{Default:} The minimum between
  \hyperref[serverrequesttimeout]{\texttt{server.requestTimeout}} or
  \texttt{60000}.
\end{itemize}

Limit the amount of time the parser will wait to receive the complete
HTTP headers.

If the timeout expires, the server responds with status 408 without
forwarding the request to the request listener and then closes the
connection.

It must be set to a non-zero value (e.g.~120 seconds) to protect against
potential Denial-of-Service attacks in case the server is deployed
without a reverse proxy in front.

\subsubsection{\texorpdfstring{\texttt{server.listen()}}{server.listen()}}\label{server.listen}

Starts the HTTP server listening for connections. This method is
identical to \href{net.md\#serverlisten}{\texttt{server.listen()}} from
\href{net.md\#class-netserver}{\texttt{net.Server}}.

\subsubsection{\texorpdfstring{\texttt{server.listening}}{server.listening}}\label{server.listening}

\begin{itemize}
\tightlist
\item
  \{boolean\} Indicates whether or not the server is listening for
  connections.
\end{itemize}

\subsubsection{\texorpdfstring{\texttt{server.maxHeadersCount}}{server.maxHeadersCount}}\label{server.maxheaderscount}

\begin{itemize}
\tightlist
\item
  \{number\} \textbf{Default:} \texttt{2000}
\end{itemize}

Limits maximum incoming headers count. If set to 0, no limit will be
applied.

\subsubsection{\texorpdfstring{\texttt{server.requestTimeout}}{server.requestTimeout}}\label{server.requesttimeout}

\begin{itemize}
\tightlist
\item
  \{number\} \textbf{Default:} \texttt{300000}
\end{itemize}

Sets the timeout value in milliseconds for receiving the entire request
from the client.

If the timeout expires, the server responds with status 408 without
forwarding the request to the request listener and then closes the
connection.

It must be set to a non-zero value (e.g.~120 seconds) to protect against
potential Denial-of-Service attacks in case the server is deployed
without a reverse proxy in front.

\subsubsection{\texorpdfstring{\texttt{server.setTimeout({[}msecs{]}{[},\ callback{]})}}{server.setTimeout({[}msecs{]}{[}, callback{]})}}\label{server.settimeoutmsecs-callback}

\begin{itemize}
\tightlist
\item
  \texttt{msecs} \{number\} \textbf{Default:} 0 (no timeout)
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{http.Server\}
\end{itemize}

Sets the timeout value for sockets, and emits a
\texttt{\textquotesingle{}timeout\textquotesingle{}} event on the Server
object, passing the socket as an argument, if a timeout occurs.

If there is a \texttt{\textquotesingle{}timeout\textquotesingle{}} event
listener on the Server object, then it will be called with the timed-out
socket as an argument.

By default, the Server does not timeout sockets. However, if a callback
is assigned to the Server's
\texttt{\textquotesingle{}timeout\textquotesingle{}} event, timeouts
must be handled explicitly.

\subsubsection{\texorpdfstring{\texttt{server.maxRequestsPerSocket}}{server.maxRequestsPerSocket}}\label{server.maxrequestspersocket}

\begin{itemize}
\tightlist
\item
  \{number\} Requests per socket. \textbf{Default:} 0 (no limit)
\end{itemize}

The maximum number of requests socket can handle before closing keep
alive connection.

A value of \texttt{0} will disable the limit.

When the limit is reached it will set the \texttt{Connection} header
value to \texttt{close}, but will not actually close the connection,
subsequent requests sent after the limit is reached will get
\texttt{503\ Service\ Unavailable} as a response.

\subsubsection{\texorpdfstring{\texttt{server.timeout}}{server.timeout}}\label{server.timeout}

\begin{itemize}
\tightlist
\item
  \{number\} Timeout in milliseconds. \textbf{Default:} 0 (no timeout)
\end{itemize}

The number of milliseconds of inactivity before a socket is presumed to
have timed out.

A value of \texttt{0} will disable the timeout behavior on incoming
connections.

The socket timeout logic is set up on connection, so changing this value
only affects new connections to the server, not any existing
connections.

\subsubsection{\texorpdfstring{\texttt{server.keepAliveTimeout}}{server.keepAliveTimeout}}\label{server.keepalivetimeout}

\begin{itemize}
\tightlist
\item
  \{number\} Timeout in milliseconds. \textbf{Default:} \texttt{5000} (5
  seconds).
\end{itemize}

The number of milliseconds of inactivity a server needs to wait for
additional incoming data, after it has finished writing the last
response, before a socket will be destroyed. If the server receives new
data before the keep-alive timeout has fired, it will reset the regular
inactivity timeout, i.e.,
\hyperref[servertimeout]{\texttt{server.timeout}}.

A value of \texttt{0} will disable the keep-alive timeout behavior on
incoming connections. A value of \texttt{0} makes the http server behave
similarly to Node.js versions prior to 8.0.0, which did not have a
keep-alive timeout.

The socket timeout logic is set up on connection, so changing this value
only affects new connections to the server, not any existing
connections.

\subsubsection{\texorpdfstring{\texttt{server{[}Symbol.asyncDispose{]}()}}{server{[}Symbol.asyncDispose{]}()}}\label{serversymbol.asyncdispose}

\begin{quote}
Stability: 1 - Experimental
\end{quote}

Calls \hyperref[serverclosecallback]{\texttt{server.close()}} and
returns a promise that fulfills when the server has closed.

\subsection{\texorpdfstring{Class:
\texttt{http.ServerResponse}}{Class: http.ServerResponse}}\label{class-http.serverresponse}

\begin{itemize}
\tightlist
\item
  Extends: \{http.OutgoingMessage\}
\end{itemize}

This object is created internally by an HTTP server, not by the user. It
is passed as the second parameter to the
\hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
event.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}close\textquotesingle{}}}{Event: \textquotesingle close\textquotesingle{}}}\label{event-close-2}

Indicates that the response is completed, or its underlying connection
was terminated prematurely (before the response completion).

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}finish\textquotesingle{}}}{Event: \textquotesingle finish\textquotesingle{}}}\label{event-finish-1}

Emitted when the response has been sent. More specifically, this event
is emitted when the last segment of the response headers and body have
been handed off to the operating system for transmission over the
network. It does not imply that the client has received anything yet.

\subsubsection{\texorpdfstring{\texttt{response.addTrailers(headers)}}{response.addTrailers(headers)}}\label{response.addtrailersheaders}

\begin{itemize}
\tightlist
\item
  \texttt{headers} \{Object\}
\end{itemize}

This method adds HTTP trailing headers (a header but at the end of the
message) to the response.

Trailers will \textbf{only} be emitted if chunked encoding is used for
the response; if it is not (e.g.~if the request was HTTP/1.0), they will
be silently discarded.

HTTP requires the \texttt{Trailer} header to be sent in order to emit
trailers, with a list of the header fields in its value. E.g.,

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\OperatorTok{,}
                          \StringTok{\textquotesingle{}Trailer\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}Content{-}MD5\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{write}\NormalTok{(fileData)}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{addTrailers}\NormalTok{(\{ }\StringTok{\textquotesingle{}Content{-}MD5\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}7895bf4b8828b55ceaf47747b4bca667\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

Attempting to set a header field name or value that contains invalid
characters will result in a
\href{errors.md\#class-typeerror}{\texttt{TypeError}} being thrown.

\subsubsection{\texorpdfstring{\texttt{response.connection}}{response.connection}}\label{response.connection}

\begin{quote}
Stability: 0 - Deprecated. Use
\hyperref[responsesocket]{\texttt{response.socket}}.
\end{quote}

\begin{itemize}
\tightlist
\item
  \{stream.Duplex\}
\end{itemize}

See \hyperref[responsesocket]{\texttt{response.socket}}.

\subsubsection{\texorpdfstring{\texttt{response.cork()}}{response.cork()}}\label{response.cork}

See \href{stream.md\#writablecork}{\texttt{writable.cork()}}.

\subsubsection{\texorpdfstring{\texttt{response.end({[}data{[},\ encoding{]}{]}{[},\ callback{]})}}{response.end({[}data{[}, encoding{]}{]}{[}, callback{]})}}\label{response.enddata-encoding-callback}

\begin{itemize}
\tightlist
\item
  \texttt{data} \{string\textbar Buffer\textbar Uint8Array\}
\item
  \texttt{encoding} \{string\}
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{this\}
\end{itemize}

This method signals to the server that all of the response headers and
body have been sent; that server should consider this message complete.
The method, \texttt{response.end()}, MUST be called on each response.

If \texttt{data} is specified, it is similar in effect to calling
\hyperref[responsewritechunk-encoding-callback]{\texttt{response.write(data,\ encoding)}}
followed by \texttt{response.end(callback)}.

If \texttt{callback} is specified, it will be called when the response
stream is finished.

\subsubsection{\texorpdfstring{\texttt{response.finished}}{response.finished}}\label{response.finished}

\begin{quote}
Stability: 0 - Deprecated. Use
\hyperref[responsewritableended]{\texttt{response.writableEnded}}.
\end{quote}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

The \texttt{response.finished} property will be \texttt{true} if
\hyperref[responseenddata-encoding-callback]{\texttt{response.end()}}
has been called.

\subsubsection{\texorpdfstring{\texttt{response.flushHeaders()}}{response.flushHeaders()}}\label{response.flushheaders}

Flushes the response headers. See also:
\hyperref[requestflushheaders]{\texttt{request.flushHeaders()}}.

\subsubsection{\texorpdfstring{\texttt{response.getHeader(name)}}{response.getHeader(name)}}\label{response.getheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  Returns: \{any\}
\end{itemize}

Reads out a header that's already been queued but not sent to the
client. The name is case-insensitive. The type of the return value
depends on the arguments provided to
\hyperref[responsesetheadername-value]{\texttt{response.setHeader()}}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}text/html\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Length\textquotesingle{}}\OperatorTok{,} \BuiltInTok{Buffer}\OperatorTok{.}\FunctionTok{byteLength}\NormalTok{(body))}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Set{-}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}type=ninja\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}language=javascript\textquotesingle{}}\NormalTok{])}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ contentType }\OperatorTok{=}\NormalTok{ response}\OperatorTok{.}\FunctionTok{getHeader}\NormalTok{(}\StringTok{\textquotesingle{}content{-}type\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\CommentTok{// contentType is \textquotesingle{}text/html\textquotesingle{}}
\KeywordTok{const}\NormalTok{ contentLength }\OperatorTok{=}\NormalTok{ response}\OperatorTok{.}\FunctionTok{getHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Length\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\CommentTok{// contentLength is of type number}
\KeywordTok{const}\NormalTok{ setCookie }\OperatorTok{=}\NormalTok{ response}\OperatorTok{.}\FunctionTok{getHeader}\NormalTok{(}\StringTok{\textquotesingle{}set{-}cookie\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\CommentTok{// setCookie is of type string[]}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{response.getHeaderNames()}}{response.getHeaderNames()}}\label{response.getheadernames}

\begin{itemize}
\tightlist
\item
  Returns: \{string{[}{]}\}
\end{itemize}

Returns an array containing the unique names of the current outgoing
headers. All header names are lowercase.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Set{-}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}foo=bar\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar=baz\textquotesingle{}}\NormalTok{])}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ headerNames }\OperatorTok{=}\NormalTok{ response}\OperatorTok{.}\FunctionTok{getHeaderNames}\NormalTok{()}\OperatorTok{;}
\CommentTok{// headerNames === [\textquotesingle{}foo\textquotesingle{}, \textquotesingle{}set{-}cookie\textquotesingle{}]}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{response.getHeaders()}}{response.getHeaders()}}\label{response.getheaders}

\begin{itemize}
\tightlist
\item
  Returns: \{Object\}
\end{itemize}

Returns a shallow copy of the current outgoing headers. Since a shallow
copy is used, array values may be mutated without additional calls to
various header-related http module methods. The keys of the returned
object are the header names and the values are the respective header
values. All header names are lowercase.

The object returned by the \texttt{response.getHeaders()} method
\emph{does not} prototypically inherit from the JavaScript
\texttt{Object}. This means that typical \texttt{Object} methods such as
\texttt{obj.toString()}, \texttt{obj.hasOwnProperty()}, and others are
not defined and \emph{will not work}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Set{-}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}foo=bar\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar=baz\textquotesingle{}}\NormalTok{])}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ headers }\OperatorTok{=}\NormalTok{ response}\OperatorTok{.}\FunctionTok{getHeaders}\NormalTok{()}\OperatorTok{;}
\CommentTok{// headers === \{ foo: \textquotesingle{}bar\textquotesingle{}, \textquotesingle{}set{-}cookie\textquotesingle{}: [\textquotesingle{}foo=bar\textquotesingle{}, \textquotesingle{}bar=baz\textquotesingle{}] \}}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{response.hasHeader(name)}}{response.hasHeader(name)}}\label{response.hasheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  Returns: \{boolean\}
\end{itemize}

Returns \texttt{true} if the header identified by \texttt{name} is
currently set in the outgoing headers. The header name matching is
case-insensitive.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ hasContentType }\OperatorTok{=}\NormalTok{ response}\OperatorTok{.}\FunctionTok{hasHeader}\NormalTok{(}\StringTok{\textquotesingle{}content{-}type\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{response.headersSent}}{response.headersSent}}\label{response.headerssent}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Boolean (read-only). True if headers were sent, false otherwise.

\subsubsection{\texorpdfstring{\texttt{response.removeHeader(name)}}{response.removeHeader(name)}}\label{response.removeheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\end{itemize}

Removes a header that's queued for implicit sending.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\FunctionTok{removeHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Encoding\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{response.req}}{response.req}}\label{response.req}

\begin{itemize}
\tightlist
\item
  \{http.IncomingMessage\}
\end{itemize}

A reference to the original HTTP \texttt{request} object.

\subsubsection{\texorpdfstring{\texttt{response.sendDate}}{response.sendDate}}\label{response.senddate}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

When true, the Date header will be automatically generated and sent in
the response if it is not already present in the headers. Defaults to
true.

This should only be disabled for testing; HTTP requires the Date header
in responses.

\subsubsection{\texorpdfstring{\texttt{response.setHeader(name,\ value)}}{response.setHeader(name, value)}}\label{response.setheadername-value}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  \texttt{value} \{any\}
\item
  Returns: \{http.ServerResponse\}
\end{itemize}

Returns the response object.

Sets a single header value for implicit headers. If this header already
exists in the to-be-sent headers, its value will be replaced. Use an
array of strings here to send multiple headers with the same name.
Non-string values will be stored without modification. Therefore,
\hyperref[responsegetheadername]{\texttt{response.getHeader()}} may
return non-string values. However, the non-string values will be
converted to strings for network transmission. The same response object
is returned to the caller, to enable call chaining.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}text/html\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

or

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Set{-}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}type=ninja\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}language=javascript\textquotesingle{}}\NormalTok{])}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

Attempting to set a header field name or value that contains invalid
characters will result in a
\href{errors.md\#class-typeerror}{\texttt{TypeError}} being thrown.

When headers have been set with
\hyperref[responsesetheadername-value]{\texttt{response.setHeader()}},
they will be merged with any headers passed to
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}},
with the headers passed to
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}
given precedence.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{// Returns content{-}type = text/plain}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}text/html\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}X{-}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}ok\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

If
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}
method is called and this method has not been called, it will directly
write the supplied header values onto the network channel without
caching internally, and the
\hyperref[responsegetheadername]{\texttt{response.getHeader()}} on the
header will not yield the expected result. If progressive population of
headers is desired with potential future retrieval and modification, use
\hyperref[responsesetheadername-value]{\texttt{response.setHeader()}}
instead of
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}.

\subsubsection{\texorpdfstring{\texttt{response.setTimeout(msecs{[},\ callback{]})}}{response.setTimeout(msecs{[}, callback{]})}}\label{response.settimeoutmsecs-callback}

\begin{itemize}
\tightlist
\item
  \texttt{msecs} \{number\}
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{http.ServerResponse\}
\end{itemize}

Sets the Socket's timeout value to \texttt{msecs}. If a callback is
provided, then it is added as a listener on the
\texttt{\textquotesingle{}timeout\textquotesingle{}} event on the
response object.

If no \texttt{\textquotesingle{}timeout\textquotesingle{}} listener is
added to the request, the response, or the server, then sockets are
destroyed when they time out. If a handler is assigned to the request,
the response, or the server's
\texttt{\textquotesingle{}timeout\textquotesingle{}} events, timed out
sockets must be handled explicitly.

\subsubsection{\texorpdfstring{\texttt{response.socket}}{response.socket}}\label{response.socket}

\begin{itemize}
\tightlist
\item
  \{stream.Duplex\}
\end{itemize}

Reference to the underlying socket. Usually users will not want to
access this property. In particular, the socket will not emit
\texttt{\textquotesingle{}readable\textquotesingle{}} events because of
how the protocol parser attaches to the socket. After
\texttt{response.end()}, the property is nulled.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \KeywordTok{const}\NormalTok{ ip }\OperatorTok{=}\NormalTok{ res}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{remoteAddress}\OperatorTok{;}
  \KeywordTok{const}\NormalTok{ port }\OperatorTok{=}\NormalTok{ res}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{remotePort}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}Your IP address is }\SpecialCharTok{$\{}\NormalTok{ip}\SpecialCharTok{\}}\VerbatimStringTok{ and your source port is }\SpecialCharTok{$\{}\NormalTok{port}\SpecialCharTok{\}}\VerbatimStringTok{.\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{3000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \KeywordTok{const}\NormalTok{ ip }\OperatorTok{=}\NormalTok{ res}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{remoteAddress}\OperatorTok{;}
  \KeywordTok{const}\NormalTok{ port }\OperatorTok{=}\NormalTok{ res}\OperatorTok{.}\AttributeTok{socket}\OperatorTok{.}\AttributeTok{remotePort}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}Your IP address is }\SpecialCharTok{$\{}\NormalTok{ip}\SpecialCharTok{\}}\VerbatimStringTok{ and your source port is }\SpecialCharTok{$\{}\NormalTok{port}\SpecialCharTok{\}}\VerbatimStringTok{.\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{3000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

This property is guaranteed to be an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specified a
socket type other than \{net.Socket\}.

\subsubsection{\texorpdfstring{\texttt{response.statusCode}}{response.statusCode}}\label{response.statuscode}

\begin{itemize}
\tightlist
\item
  \{number\} \textbf{Default:} \texttt{200}
\end{itemize}

When using implicit headers (not calling
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}
explicitly), this property controls the status code that will be sent to
the client when the headers get flushed.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\AttributeTok{statusCode} \OperatorTok{=} \DecValTok{404}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

After response header was sent to the client, this property indicates
the status code which was sent out.

\subsubsection{\texorpdfstring{\texttt{response.statusMessage}}{response.statusMessage}}\label{response.statusmessage}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

When using implicit headers (not calling
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}
explicitly), this property controls the status message that will be sent
to the client when the headers get flushed. If this is left as
\texttt{undefined} then the standard message for the status code will be
used.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{response}\OperatorTok{.}\AttributeTok{statusMessage} \OperatorTok{=} \StringTok{\textquotesingle{}Not found\textquotesingle{}}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

After response header was sent to the client, this property indicates
the status message which was sent out.

\subsubsection{\texorpdfstring{\texttt{response.strictContentLength}}{response.strictContentLength}}\label{response.strictcontentlength}

\begin{itemize}
\tightlist
\item
  \{boolean\} \textbf{Default:} \texttt{false}
\end{itemize}

If set to \texttt{true}, Node.js will check whether the
\texttt{Content-Length} header value and the size of the body, in bytes,
are equal. Mismatching the \texttt{Content-Length} header value will
result in an \texttt{Error} being thrown, identified by \texttt{code:}
\href{errors.md\#err_http_content_length_mismatch}{\texttt{\textquotesingle{}ERR\_HTTP\_CONTENT\_LENGTH\_MISMATCH\textquotesingle{}}}.

\subsubsection{\texorpdfstring{\texttt{response.uncork()}}{response.uncork()}}\label{response.uncork}

See \href{stream.md\#writableuncork}{\texttt{writable.uncork()}}.

\subsubsection{\texorpdfstring{\texttt{response.writableEnded}}{response.writableEnded}}\label{response.writableended}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Is \texttt{true} after
\hyperref[responseenddata-encoding-callback]{\texttt{response.end()}}
has been called. This property does not indicate whether the data has
been flushed, for this use
\hyperref[responsewritablefinished]{\texttt{response.writableFinished}}
instead.

\subsubsection{\texorpdfstring{\texttt{response.writableFinished}}{response.writableFinished}}\label{response.writablefinished}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Is \texttt{true} if all data has been flushed to the underlying system,
immediately before the
\hyperref[event-finish]{\texttt{\textquotesingle{}finish\textquotesingle{}}}
event is emitted.

\subsubsection{\texorpdfstring{\texttt{response.write(chunk{[},\ encoding{]}{[},\ callback{]})}}{response.write(chunk{[}, encoding{]}{[}, callback{]})}}\label{response.writechunk-encoding-callback}

\begin{itemize}
\tightlist
\item
  \texttt{chunk} \{string\textbar Buffer\textbar Uint8Array\}
\item
  \texttt{encoding} \{string\} \textbf{Default:}
  \texttt{\textquotesingle{}utf8\textquotesingle{}}
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{boolean\}
\end{itemize}

If this method is called and
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}
has not been called, it will switch to implicit header mode and flush
the implicit headers.

This sends a chunk of the response body. This method may be called
multiple times to provide successive parts of the body.

Writing to the body is not allowed when the request method or response
status do not support content. If an attempt is made to write to the
body for a HEAD request or as part of a \texttt{204} or
\texttt{304}response, a synchronous \texttt{Error} with the code
\texttt{ERR\_HTTP\_BODY\_NOT\_ALLOWED} is thrown.

\texttt{chunk} can be a string or a buffer. If \texttt{chunk} is a
string, the second parameter specifies how to encode it into a byte
stream. \texttt{callback} will be called when this chunk of data is
flushed.

This is the raw HTTP body and has nothing to do with higher-level
multi-part body encodings that may be used.

The first time
\hyperref[responsewritechunk-encoding-callback]{\texttt{response.write()}}
is called, it will send the buffered header information and the first
chunk of the body to the client. The second time
\hyperref[responsewritechunk-encoding-callback]{\texttt{response.write()}}
is called, Node.js assumes data will be streamed, and sends the new data
separately. That is, the response is buffered up to the first chunk of
the body.

Returns \texttt{true} if the entire data was flushed successfully to the
kernel buffer. Returns \texttt{false} if all or part of the data was
queued in user memory.
\texttt{\textquotesingle{}drain\textquotesingle{}} will be emitted when
the buffer is free again.

\subsubsection{\texorpdfstring{\texttt{response.writeContinue()}}{response.writeContinue()}}\label{response.writecontinue}

Sends an HTTP/1.1 100 Continue message to the client, indicating that
the request body should be sent. See the
\hyperref[event-checkcontinue]{\texttt{\textquotesingle{}checkContinue\textquotesingle{}}}
event on \texttt{Server}.

\subsubsection{\texorpdfstring{\texttt{response.writeEarlyHints(hints{[},\ callback{]})}}{response.writeEarlyHints(hints{[}, callback{]})}}\label{response.writeearlyhintshints-callback}

\begin{itemize}
\tightlist
\item
  \texttt{hints} \{Object\}
\item
  \texttt{callback} \{Function\}
\end{itemize}

Sends an HTTP/1.1 103 Early Hints message to the client with a Link
header, indicating that the user agent can preload/preconnect the linked
resources. The \texttt{hints} is an object containing the values of
headers to be sent with early hints message. The optional
\texttt{callback} argument will be called when the response message has
been written.

\textbf{Example}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ earlyHintsLink }\OperatorTok{=} \StringTok{\textquotesingle{}\textless{}/styles.css\textgreater{}; rel=preload; as=style\textquotesingle{}}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{writeEarlyHints}\NormalTok{(\{}
  \StringTok{\textquotesingle{}link\textquotesingle{}}\OperatorTok{:}\NormalTok{ earlyHintsLink}\OperatorTok{,}
\NormalTok{\})}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ earlyHintsLinks }\OperatorTok{=}\NormalTok{ [}
  \StringTok{\textquotesingle{}\textless{}/styles.css\textgreater{}; rel=preload; as=style\textquotesingle{}}\OperatorTok{,}
  \StringTok{\textquotesingle{}\textless{}/scripts.js\textgreater{}; rel=preload; as=script\textquotesingle{}}\OperatorTok{,}
\NormalTok{]}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{writeEarlyHints}\NormalTok{(\{}
  \StringTok{\textquotesingle{}link\textquotesingle{}}\OperatorTok{:}\NormalTok{ earlyHintsLinks}\OperatorTok{,}
  \StringTok{\textquotesingle{}x{-}trace{-}id\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}id for diagnostics\textquotesingle{}}\OperatorTok{,}
\NormalTok{\})}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ earlyHintsCallback }\OperatorTok{=}\NormalTok{ () }\KeywordTok{=\textgreater{}} \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}early hints message sent\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{writeEarlyHints}\NormalTok{(\{}
  \StringTok{\textquotesingle{}link\textquotesingle{}}\OperatorTok{:}\NormalTok{ earlyHintsLinks}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{,}\NormalTok{ earlyHintsCallback)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{response.writeHead(statusCode{[},\ statusMessage{]}{[},\ headers{]})}}{response.writeHead(statusCode{[}, statusMessage{]}{[}, headers{]})}}\label{response.writeheadstatuscode-statusmessage-headers}

\begin{itemize}
\tightlist
\item
  \texttt{statusCode} \{number\}
\item
  \texttt{statusMessage} \{string\}
\item
  \texttt{headers} \{Object\textbar Array\}
\item
  Returns: \{http.ServerResponse\}
\end{itemize}

Sends a response header to the request. The status code is a 3-digit
HTTP status code, like \texttt{404}. The last argument,
\texttt{headers}, are the response headers. Optionally one can give a
human-readable \texttt{statusMessage} as the second argument.

\texttt{headers} may be an \texttt{Array} where the keys and values are
in the same list. It is \emph{not} a list of tuples. So, the
even-numbered offsets are key values, and the odd-numbered offsets are
the associated values. The array is in the same format as
\texttt{request.rawHeaders}.

Returns a reference to the \texttt{ServerResponse}, so that calls can be
chained.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ body }\OperatorTok{=} \StringTok{\textquotesingle{}hello world\textquotesingle{}}\OperatorTok{;}
\NormalTok{response}
  \OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{}
    \StringTok{\textquotesingle{}Content{-}Length\textquotesingle{}}\OperatorTok{:} \BuiltInTok{Buffer}\OperatorTok{.}\FunctionTok{byteLength}\NormalTok{(body)}\OperatorTok{,}
    \StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \})}
  \OperatorTok{.}\FunctionTok{end}\NormalTok{(body)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

This method must only be called once on a message and it must be called
before
\hyperref[responseenddata-encoding-callback]{\texttt{response.end()}} is
called.

If
\hyperref[responsewritechunk-encoding-callback]{\texttt{response.write()}}
or \hyperref[responseenddata-encoding-callback]{\texttt{response.end()}}
are called before calling this, the implicit/mutable headers will be
calculated and call this function.

When headers have been set with
\hyperref[responsesetheadername-value]{\texttt{response.setHeader()}},
they will be merged with any headers passed to
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}},
with the headers passed to
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}
given precedence.

If this method is called and
\hyperref[responsesetheadername-value]{\texttt{response.setHeader()}}
has not been called, it will directly write the supplied header values
onto the network channel without caching internally, and the
\hyperref[responsegetheadername]{\texttt{response.getHeader()}} on the
header will not yield the expected result. If progressive population of
headers is desired with potential future retrieval and modification, use
\hyperref[responsesetheadername-value]{\texttt{response.setHeader()}}
instead.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{// Returns content{-}type = text/plain}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}text/html\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}X{-}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}ok\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\texttt{Content-Length} is read in bytes, not characters. Use
\href{buffer.md\#static-method-bufferbytelengthstring-encoding}{\texttt{Buffer.byteLength()}}
to determine the length of the body in bytes. Node.js will check whether
\texttt{Content-Length} and the length of the body which has been
transmitted are equal or not.

Attempting to set a header field name or value that contains invalid
characters will result in a {[}\texttt{Error}{]}{[}{]} being thrown.

\subsubsection{\texorpdfstring{\texttt{response.writeProcessing()}}{response.writeProcessing()}}\label{response.writeprocessing}

Sends a HTTP/1.1 102 Processing message to the client, indicating that
the request body should be sent.

\subsection{\texorpdfstring{Class:
\texttt{http.IncomingMessage}}{Class: http.IncomingMessage}}\label{class-http.incomingmessage}

\begin{itemize}
\tightlist
\item
  Extends: \{stream.Readable\}
\end{itemize}

An \texttt{IncomingMessage} object is created by
\hyperref[class-httpserver]{\texttt{http.Server}} or
\hyperref[class-httpclientrequest]{\texttt{http.ClientRequest}} and
passed as the first argument to the
\hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
and
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
event respectively. It may be used to access response status, headers,
and data.

Different from its \texttt{socket} value which is a subclass of
\{stream.Duplex\}, the \texttt{IncomingMessage} itself extends
\{stream.Readable\} and is created separately to parse and emit the
incoming HTTP headers and payload, as the underlying socket may be
reused multiple times in case of keep-alive.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}aborted\textquotesingle{}}}{Event: \textquotesingle aborted\textquotesingle{}}}\label{event-aborted}

\begin{quote}
Stability: 0 - Deprecated. Listen for
\texttt{\textquotesingle{}close\textquotesingle{}} event instead.
\end{quote}

Emitted when the request has been aborted.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}close\textquotesingle{}}}{Event: \textquotesingle close\textquotesingle{}}}\label{event-close-3}

Emitted when the request has been completed.

\subsubsection{\texorpdfstring{\texttt{message.aborted}}{message.aborted}}\label{message.aborted}

\begin{quote}
Stability: 0 - Deprecated. Check \texttt{message.destroyed} from
\{stream.Readable\}.
\end{quote}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

The \texttt{message.aborted} property will be \texttt{true} if the
request has been aborted.

\subsubsection{\texorpdfstring{\texttt{message.complete}}{message.complete}}\label{message.complete}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

The \texttt{message.complete} property will be \texttt{true} if a
complete HTTP message has been received and successfully parsed.

This property is particularly useful as a means of determining if a
client or server fully transmitted a message before a connection was
terminated:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(\{}
  \DataTypeTok{host}\OperatorTok{:} \StringTok{\textquotesingle{}127.0.0.1\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{port}\OperatorTok{:} \DecValTok{8080}\OperatorTok{,}
  \DataTypeTok{method}\OperatorTok{:} \StringTok{\textquotesingle{}POST\textquotesingle{}}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{resume}\NormalTok{()}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}end\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \ControlFlowTok{if}\NormalTok{ (}\OperatorTok{!}\NormalTok{res}\OperatorTok{.}\AttributeTok{complete}\NormalTok{)}
      \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(}
        \StringTok{\textquotesingle{}The connection was terminated while the message was still being sent\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{message.connection}}{message.connection}}\label{message.connection}

\begin{quote}
Stability: 0 - Deprecated. Use
\hyperref[messagesocket]{\texttt{message.socket}}.
\end{quote}

Alias for \hyperref[messagesocket]{\texttt{message.socket}}.

\subsubsection{\texorpdfstring{\texttt{message.destroy({[}error{]})}}{message.destroy({[}error{]})}}\label{message.destroyerror}

\begin{itemize}
\tightlist
\item
  \texttt{error} \{Error\}
\item
  Returns: \{this\}
\end{itemize}

Calls \texttt{destroy()} on the socket that received the
\texttt{IncomingMessage}. If \texttt{error} is provided, an
\texttt{\textquotesingle{}error\textquotesingle{}} event is emitted on
the socket and \texttt{error} is passed as an argument to any listeners
on the event.

\subsubsection{\texorpdfstring{\texttt{message.headers}}{message.headers}}\label{message.headers}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

The request/response headers object.

Key-value pairs of header names and values. Header names are
lower-cased.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{// Prints something like:}
\CommentTok{//}
\CommentTok{// \{ \textquotesingle{}user{-}agent\textquotesingle{}: \textquotesingle{}curl/7.22.0\textquotesingle{},}
\CommentTok{//   host: \textquotesingle{}127.0.0.1:8000\textquotesingle{},}
\CommentTok{//   accept: \textquotesingle{}*/*\textquotesingle{} \}}
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(request}\OperatorTok{.}\AttributeTok{headers}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

Duplicates in raw headers are handled in the following ways, depending
on the header name:

\begin{itemize}
\tightlist
\item
  Duplicates of \texttt{age}, \texttt{authorization},
  \texttt{content-length}, \texttt{content-type}, \texttt{etag},
  \texttt{expires}, \texttt{from}, \texttt{host},
  \texttt{if-modified-since}, \texttt{if-unmodified-since},
  \texttt{last-modified}, \texttt{location}, \texttt{max-forwards},
  \texttt{proxy-authorization}, \texttt{referer}, \texttt{retry-after},
  \texttt{server}, or \texttt{user-agent} are discarded. To allow
  duplicate values of the headers listed above to be joined, use the
  option \texttt{joinDuplicateHeaders} in
  \hyperref[httprequestoptions-callback]{\texttt{http.request()}} and
  \hyperref[httpcreateserveroptions-requestlistener]{\texttt{http.createServer()}}.
  See RFC 9110 Section 5.3 for more information.
\item
  \texttt{set-cookie} is always an array. Duplicates are added to the
  array.
\item
  For duplicate \texttt{cookie} headers, the values are joined together
  with \texttt{;}.
\item
  For all other headers, the values are joined together with \texttt{,}.
\end{itemize}

\subsubsection{\texorpdfstring{\texttt{message.headersDistinct}}{message.headersDistinct}}\label{message.headersdistinct}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

Similar to \hyperref[messageheaders]{\texttt{message.headers}}, but
there is no join logic and the values are always arrays of strings, even
for headers received just once.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{// Prints something like:}
\CommentTok{//}
\CommentTok{// \{ \textquotesingle{}user{-}agent\textquotesingle{}: [\textquotesingle{}curl/7.22.0\textquotesingle{}],}
\CommentTok{//   host: [\textquotesingle{}127.0.0.1:8000\textquotesingle{}],}
\CommentTok{//   accept: [\textquotesingle{}*/*\textquotesingle{}] \}}
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(request}\OperatorTok{.}\AttributeTok{headersDistinct}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{message.httpVersion}}{message.httpVersion}}\label{message.httpversion}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

In case of server request, the HTTP version sent by the client. In the
case of client response, the HTTP version of the connected-to server.
Probably either \texttt{\textquotesingle{}1.1\textquotesingle{}} or
\texttt{\textquotesingle{}1.0\textquotesingle{}}.

Also \texttt{message.httpVersionMajor} is the first integer and
\texttt{message.httpVersionMinor} is the second.

\subsubsection{\texorpdfstring{\texttt{message.method}}{message.method}}\label{message.method}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

\textbf{Only valid for request obtained from
\hyperref[class-httpserver]{\texttt{http.Server}}.}

The request method as a string. Read only. Examples:
\texttt{\textquotesingle{}GET\textquotesingle{}},
\texttt{\textquotesingle{}DELETE\textquotesingle{}}.

\subsubsection{\texorpdfstring{\texttt{message.rawHeaders}}{message.rawHeaders}}\label{message.rawheaders}

\begin{itemize}
\tightlist
\item
  \{string{[}{]}\}
\end{itemize}

The raw request/response headers list exactly as they were received.

The keys and values are in the same list. It is \emph{not} a list of
tuples. So, the even-numbered offsets are key values, and the
odd-numbered offsets are the associated values.

Header names are not lowercased, and duplicates are not merged.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{// Prints something like:}
\CommentTok{//}
\CommentTok{// [ \textquotesingle{}user{-}agent\textquotesingle{},}
\CommentTok{//   \textquotesingle{}this is invalid because there can be only one\textquotesingle{},}
\CommentTok{//   \textquotesingle{}User{-}Agent\textquotesingle{},}
\CommentTok{//   \textquotesingle{}curl/7.22.0\textquotesingle{},}
\CommentTok{//   \textquotesingle{}Host\textquotesingle{},}
\CommentTok{//   \textquotesingle{}127.0.0.1:8000\textquotesingle{},}
\CommentTok{//   \textquotesingle{}ACCEPT\textquotesingle{},}
\CommentTok{//   \textquotesingle{}*/*\textquotesingle{} ]}
\BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(request}\OperatorTok{.}\AttributeTok{rawHeaders}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{message.rawTrailers}}{message.rawTrailers}}\label{message.rawtrailers}

\begin{itemize}
\tightlist
\item
  \{string{[}{]}\}
\end{itemize}

The raw request/response trailer keys and values exactly as they were
received. Only populated at the
\texttt{\textquotesingle{}end\textquotesingle{}} event.

\subsubsection{\texorpdfstring{\texttt{message.setTimeout(msecs{[},\ callback{]})}}{message.setTimeout(msecs{[}, callback{]})}}\label{message.settimeoutmsecs-callback}

\begin{itemize}
\tightlist
\item
  \texttt{msecs} \{number\}
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{http.IncomingMessage\}
\end{itemize}

Calls \texttt{message.socket.setTimeout(msecs,\ callback)}.

\subsubsection{\texorpdfstring{\texttt{message.socket}}{message.socket}}\label{message.socket}

\begin{itemize}
\tightlist
\item
  \{stream.Duplex\}
\end{itemize}

The \href{net.md\#class-netsocket}{\texttt{net.Socket}} object
associated with the connection.

With HTTPS support, use
\href{tls.md\#tlssocketgetpeercertificatedetailed}{\texttt{request.socket.getPeerCertificate()}}
to obtain the client's authentication details.

This property is guaranteed to be an instance of the \{net.Socket\}
class, a subclass of \{stream.Duplex\}, unless the user specified a
socket type other than \{net.Socket\} or internally nulled.

\subsubsection{\texorpdfstring{\texttt{message.statusCode}}{message.statusCode}}\label{message.statuscode}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

\textbf{Only valid for response obtained from
\hyperref[class-httpclientrequest]{\texttt{http.ClientRequest}}.}

The 3-digit HTTP response status code. E.G. \texttt{404}.

\subsubsection{\texorpdfstring{\texttt{message.statusMessage}}{message.statusMessage}}\label{message.statusmessage}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

\textbf{Only valid for response obtained from
\hyperref[class-httpclientrequest]{\texttt{http.ClientRequest}}.}

The HTTP response status message (reason phrase). E.G. \texttt{OK} or
\texttt{Internal\ Server\ Error}.

\subsubsection{\texorpdfstring{\texttt{message.trailers}}{message.trailers}}\label{message.trailers}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

The request/response trailers object. Only populated at the
\texttt{\textquotesingle{}end\textquotesingle{}} event.

\subsubsection{\texorpdfstring{\texttt{message.trailersDistinct}}{message.trailersDistinct}}\label{message.trailersdistinct}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

Similar to \hyperref[messagetrailers]{\texttt{message.trailers}}, but
there is no join logic and the values are always arrays of strings, even
for headers received just once. Only populated at the
\texttt{\textquotesingle{}end\textquotesingle{}} event.

\subsubsection{\texorpdfstring{\texttt{message.url}}{message.url}}\label{message.url}

\begin{itemize}
\tightlist
\item
  \{string\}
\end{itemize}

\textbf{Only valid for request obtained from
\hyperref[class-httpserver]{\texttt{http.Server}}.}

Request URL string. This contains only the URL that is present in the
actual HTTP request. Take the following request:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{GET /status?name=ryan HTTP/1.1}
\NormalTok{Accept: text/plain}
\end{Highlighting}
\end{Shaded}

To parse the URL into its parts:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{new} \FunctionTok{URL}\NormalTok{(request}\OperatorTok{.}\AttributeTok{url}\OperatorTok{,} \VerbatimStringTok{\textasciigrave{}http://}\SpecialCharTok{$\{}\NormalTok{request}\OperatorTok{.}\AttributeTok{headers}\OperatorTok{.}\AttributeTok{host}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

When \texttt{request.url} is
\texttt{\textquotesingle{}/status?name=ryan\textquotesingle{}} and
\texttt{request.headers.host} is
\texttt{\textquotesingle{}localhost:3000\textquotesingle{}}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ node}
\NormalTok{\textgreater{} new URL(request.url, \textasciigrave{}http://$\{request.headers.host\}\textasciigrave{})}
\NormalTok{URL \{}
\NormalTok{  href: \textquotesingle{}http://localhost:3000/status?name=ryan\textquotesingle{},}
\NormalTok{  origin: \textquotesingle{}http://localhost:3000\textquotesingle{},}
\NormalTok{  protocol: \textquotesingle{}http:\textquotesingle{},}
\NormalTok{  username: \textquotesingle{}\textquotesingle{},}
\NormalTok{  password: \textquotesingle{}\textquotesingle{},}
\NormalTok{  host: \textquotesingle{}localhost:3000\textquotesingle{},}
\NormalTok{  hostname: \textquotesingle{}localhost\textquotesingle{},}
\NormalTok{  port: \textquotesingle{}3000\textquotesingle{},}
\NormalTok{  pathname: \textquotesingle{}/status\textquotesingle{},}
\NormalTok{  search: \textquotesingle{}?name=ryan\textquotesingle{},}
\NormalTok{  searchParams: URLSearchParams \{ \textquotesingle{}name\textquotesingle{} =\textgreater{} \textquotesingle{}ryan\textquotesingle{} \},}
\NormalTok{  hash: \textquotesingle{}\textquotesingle{}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{Class:
\texttt{http.OutgoingMessage}}{Class: http.OutgoingMessage}}\label{class-http.outgoingmessage}

\begin{itemize}
\tightlist
\item
  Extends: \{Stream\}
\end{itemize}

This class serves as the parent class of
\hyperref[class-httpclientrequest]{\texttt{http.ClientRequest}} and
\hyperref[class-httpserverresponse]{\texttt{http.ServerResponse}}. It is
an abstract outgoing message from the perspective of the participants of
an HTTP transaction.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}drain\textquotesingle{}}}{Event: \textquotesingle drain\textquotesingle{}}}\label{event-drain}

Emitted when the buffer of the message is free again.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}finish\textquotesingle{}}}{Event: \textquotesingle finish\textquotesingle{}}}\label{event-finish-2}

Emitted when the transmission is finished successfully.

\subsubsection{\texorpdfstring{Event:
\texttt{\textquotesingle{}prefinish\textquotesingle{}}}{Event: \textquotesingle prefinish\textquotesingle{}}}\label{event-prefinish}

Emitted after \texttt{outgoingMessage.end()} is called. When the event
is emitted, all data has been processed but not necessarily completely
flushed.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.addTrailers(headers)}}{outgoingMessage.addTrailers(headers)}}\label{outgoingmessage.addtrailersheaders}

\begin{itemize}
\tightlist
\item
  \texttt{headers} \{Object\}
\end{itemize}

Adds HTTP trailers (headers but at the end of the message) to the
message.

Trailers will \textbf{only} be emitted if the message is chunked
encoded. If not, the trailers will be silently discarded.

HTTP requires the \texttt{Trailer} header to be sent to emit trailers,
with a list of header field names in its value, e.g.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{message}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\OperatorTok{,}
                         \StringTok{\textquotesingle{}Trailer\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}Content{-}MD5\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{message}\OperatorTok{.}\FunctionTok{write}\NormalTok{(fileData)}\OperatorTok{;}
\NormalTok{message}\OperatorTok{.}\FunctionTok{addTrailers}\NormalTok{(\{ }\StringTok{\textquotesingle{}Content{-}MD5\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}7895bf4b8828b55ceaf47747b4bca667\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{message}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

Attempting to set a header field name or value that contains invalid
characters will result in a \texttt{TypeError} being thrown.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.appendHeader(name,\ value)}}{outgoingMessage.appendHeader(name, value)}}\label{outgoingmessage.appendheadername-value}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\} Header name
\item
  \texttt{value} \{string\textbar string{[}{]}\} Header value
\item
  Returns: \{this\}
\end{itemize}

Append a single header value for the header object.

If the value is an array, this is equivalent of calling this method
multiple times.

If there were no previous value for the header, this is equivalent of
calling
\hyperref[outgoingmessagesetheadername-value]{\texttt{outgoingMessage.setHeader(name,\ value)}}.

Depending of the value of \texttt{options.uniqueHeaders} when the client
request or the server were created, this will end up in the header being
sent multiple times or a single time with values joined using
\texttt{;}.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.connection}}{outgoingMessage.connection}}\label{outgoingmessage.connection}

\begin{quote}
Stability: 0 - Deprecated: Use
\hyperref[outgoingmessagesocket]{\texttt{outgoingMessage.socket}}
instead.
\end{quote}

Alias of
\hyperref[outgoingmessagesocket]{\texttt{outgoingMessage.socket}}.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.cork()}}{outgoingMessage.cork()}}\label{outgoingmessage.cork}

See \href{stream.md\#writablecork}{\texttt{writable.cork()}}.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.destroy({[}error{]})}}{outgoingMessage.destroy({[}error{]})}}\label{outgoingmessage.destroyerror}

\begin{itemize}
\tightlist
\item
  \texttt{error} \{Error\} Optional, an error to emit with
  \texttt{error} event
\item
  Returns: \{this\}
\end{itemize}

Destroys the message. Once a socket is associated with the message and
is connected, that socket will be destroyed as well.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.end(chunk{[},\ encoding{]}{[},\ callback{]})}}{outgoingMessage.end(chunk{[}, encoding{]}{[}, callback{]})}}\label{outgoingmessage.endchunk-encoding-callback}

\begin{itemize}
\tightlist
\item
  \texttt{chunk} \{string\textbar Buffer\textbar Uint8Array\}
\item
  \texttt{encoding} \{string\} Optional, \textbf{Default}: \texttt{utf8}
\item
  \texttt{callback} \{Function\} Optional
\item
  Returns: \{this\}
\end{itemize}

Finishes the outgoing message. If any parts of the body are unsent, it
will flush them to the underlying system. If the message is chunked, it
will send the terminating chunk
\texttt{0\textbackslash{}r\textbackslash{}n\textbackslash{}r\textbackslash{}n},
and send the trailers (if any).

If \texttt{chunk} is specified, it is equivalent to calling
\texttt{outgoingMessage.write(chunk,\ encoding)}, followed by
\texttt{outgoingMessage.end(callback)}.

If \texttt{callback} is provided, it will be called when the message is
finished (equivalent to a listener of the
\texttt{\textquotesingle{}finish\textquotesingle{}} event).

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.flushHeaders()}}{outgoingMessage.flushHeaders()}}\label{outgoingmessage.flushheaders}

Flushes the message headers.

For efficiency reason, Node.js normally buffers the message headers
until \texttt{outgoingMessage.end()} is called or the first chunk of
message data is written. It then tries to pack the headers and data into
a single TCP packet.

It is usually desired (it saves a TCP round-trip), but not when the
first data is not sent until possibly much later.
\texttt{outgoingMessage.flushHeaders()} bypasses the optimization and
kickstarts the message.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.getHeader(name)}}{outgoingMessage.getHeader(name)}}\label{outgoingmessage.getheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\} Name of header
\item
  Returns \{string \textbar{} undefined\}
\end{itemize}

Gets the value of the HTTP header with the given name. If that header is
not set, the returned value will be \texttt{undefined}.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.getHeaderNames()}}{outgoingMessage.getHeaderNames()}}\label{outgoingmessage.getheadernames}

\begin{itemize}
\tightlist
\item
  Returns \{string{[}{]}\}
\end{itemize}

Returns an array containing the unique names of the current outgoing
headers. All names are lowercase.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.getHeaders()}}{outgoingMessage.getHeaders()}}\label{outgoingmessage.getheaders}

\begin{itemize}
\tightlist
\item
  Returns: \{Object\}
\end{itemize}

Returns a shallow copy of the current outgoing headers. Since a shallow
copy is used, array values may be mutated without additional calls to
various header-related HTTP module methods. The keys of the returned
object are the header names and the values are the respective header
values. All header names are lowercase.

The object returned by the \texttt{outgoingMessage.getHeaders()} method
does not prototypically inherit from the JavaScript \texttt{Object}.
This means that typical \texttt{Object} methods such as
\texttt{obj.toString()}, \texttt{obj.hasOwnProperty()}, and others are
not defined and will not work.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{outgoingMessage}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{outgoingMessage}\OperatorTok{.}\FunctionTok{setHeader}\NormalTok{(}\StringTok{\textquotesingle{}Set{-}Cookie\textquotesingle{}}\OperatorTok{,}\NormalTok{ [}\StringTok{\textquotesingle{}foo=bar\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar=baz\textquotesingle{}}\NormalTok{])}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ headers }\OperatorTok{=}\NormalTok{ outgoingMessage}\OperatorTok{.}\FunctionTok{getHeaders}\NormalTok{()}\OperatorTok{;}
\CommentTok{// headers === \{ foo: \textquotesingle{}bar\textquotesingle{}, \textquotesingle{}set{-}cookie\textquotesingle{}: [\textquotesingle{}foo=bar\textquotesingle{}, \textquotesingle{}bar=baz\textquotesingle{}] \}}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.hasHeader(name)}}{outgoingMessage.hasHeader(name)}}\label{outgoingmessage.hasheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  Returns \{boolean\}
\end{itemize}

Returns \texttt{true} if the header identified by \texttt{name} is
currently set in the outgoing headers. The header name is
case-insensitive.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ hasContentType }\OperatorTok{=}\NormalTok{ outgoingMessage}\OperatorTok{.}\FunctionTok{hasHeader}\NormalTok{(}\StringTok{\textquotesingle{}content{-}type\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.headersSent}}{outgoingMessage.headersSent}}\label{outgoingmessage.headerssent}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Read-only. \texttt{true} if the headers were sent, otherwise
\texttt{false}.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.pipe()}}{outgoingMessage.pipe()}}\label{outgoingmessage.pipe}

Overrides the \texttt{stream.pipe()} method inherited from the legacy
\texttt{Stream} class which is the parent class of
\texttt{http.OutgoingMessage}.

Calling this method will throw an \texttt{Error} because
\texttt{outgoingMessage} is a write-only stream.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.removeHeader(name)}}{outgoingMessage.removeHeader(name)}}\label{outgoingmessage.removeheadername}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\} Header name
\end{itemize}

Removes a header that is queued for implicit sending.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{outgoingMessage}\OperatorTok{.}\FunctionTok{removeHeader}\NormalTok{(}\StringTok{\textquotesingle{}Content{-}Encoding\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.setHeader(name,\ value)}}{outgoingMessage.setHeader(name, value)}}\label{outgoingmessage.setheadername-value}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\} Header name
\item
  \texttt{value} \{any\} Header value
\item
  Returns: \{this\}
\end{itemize}

Sets a single header value. If the header already exists in the
to-be-sent headers, its value will be replaced. Use an array of strings
to send multiple headers with the same name.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.setHeaders(headers)}}{outgoingMessage.setHeaders(headers)}}\label{outgoingmessage.setheadersheaders}

\begin{itemize}
\tightlist
\item
  \texttt{headers} \{Headers\textbar Map\}
\item
  Returns: \{http.ServerResponse\}
\end{itemize}

Returns the response object.

Sets multiple header values for implicit headers. \texttt{headers} must
be an instance of \href{globals.md\#class-headers}{\texttt{Headers}} or
\texttt{Map}, if a header already exists in the to-be-sent headers, its
value will be replaced.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ headers }\OperatorTok{=} \KeywordTok{new} \FunctionTok{Headers}\NormalTok{(\{ }\DataTypeTok{foo}\OperatorTok{:} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{response}\OperatorTok{.}\FunctionTok{setHeaders}\NormalTok{(headers)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

or

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ headers }\OperatorTok{=} \KeywordTok{new} \BuiltInTok{Map}\NormalTok{([[}\StringTok{\textquotesingle{}foo\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}bar\textquotesingle{}}\NormalTok{]])}\OperatorTok{;}
\NormalTok{res}\OperatorTok{.}\FunctionTok{setHeaders}\NormalTok{(headers)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

When headers have been set with
\hyperref[outgoingmessagesetheadersheaders]{\texttt{outgoingMessage.setHeaders()}},
they will be merged with any headers passed to
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}},
with the headers passed to
\hyperref[responsewriteheadstatuscode-statusmessage-headers]{\texttt{response.writeHead()}}
given precedence.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{// Returns content{-}type = text/plain}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \KeywordTok{const}\NormalTok{ headers }\OperatorTok{=} \KeywordTok{new} \FunctionTok{Headers}\NormalTok{(\{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/html\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{setHeaders}\NormalTok{(headers)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}text/plain\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\StringTok{\textquotesingle{}ok\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.setTimeout(msesc{[},\ callback{]})}}{outgoingMessage.setTimeout(msesc{[}, callback{]})}}\label{outgoingmessage.settimeoutmsesc-callback}

\begin{itemize}
\tightlist
\item
  \texttt{msesc} \{number\}
\item
  \texttt{callback} \{Function\} Optional function to be called when a
  timeout occurs. Same as binding to the \texttt{timeout} event.
\item
  Returns: \{this\}
\end{itemize}

Once a socket is associated with the message and is connected,
\href{net.md\#socketsettimeouttimeout-callback}{\texttt{socket.setTimeout()}}
will be called with \texttt{msecs} as the first parameter.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.socket}}{outgoingMessage.socket}}\label{outgoingmessage.socket}

\begin{itemize}
\tightlist
\item
  \{stream.Duplex\}
\end{itemize}

Reference to the underlying socket. Usually, users will not want to
access this property.

After calling \texttt{outgoingMessage.end()}, this property will be
nulled.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.uncork()}}{outgoingMessage.uncork()}}\label{outgoingmessage.uncork}

See \href{stream.md\#writableuncork}{\texttt{writable.uncork()}}

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.writableCorked}}{outgoingMessage.writableCorked}}\label{outgoingmessage.writablecorked}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

The number of times \texttt{outgoingMessage.cork()} has been called.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.writableEnded}}{outgoingMessage.writableEnded}}\label{outgoingmessage.writableended}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Is \texttt{true} if \texttt{outgoingMessage.end()} has been called. This
property does not indicate whether the data has been flushed. For that
purpose, use \texttt{message.writableFinished} instead.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.writableFinished}}{outgoingMessage.writableFinished}}\label{outgoingmessage.writablefinished}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Is \texttt{true} if all data has been flushed to the underlying system.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.writableHighWaterMark}}{outgoingMessage.writableHighWaterMark}}\label{outgoingmessage.writablehighwatermark}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

The \texttt{highWaterMark} of the underlying socket if assigned.
Otherwise, the default buffer level when
\href{stream.md\#writablewritechunk-encoding-callback}{\texttt{writable.write()}}
starts returning false (\texttt{16384}).

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.writableLength}}{outgoingMessage.writableLength}}\label{outgoingmessage.writablelength}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

The number of buffered bytes.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.writableObjectMode}}{outgoingMessage.writableObjectMode}}\label{outgoingmessage.writableobjectmode}

\begin{itemize}
\tightlist
\item
  \{boolean\}
\end{itemize}

Always \texttt{false}.

\subsubsection{\texorpdfstring{\texttt{outgoingMessage.write(chunk{[},\ encoding{]}{[},\ callback{]})}}{outgoingMessage.write(chunk{[}, encoding{]}{[}, callback{]})}}\label{outgoingmessage.writechunk-encoding-callback}

\begin{itemize}
\tightlist
\item
  \texttt{chunk} \{string\textbar Buffer\textbar Uint8Array\}
\item
  \texttt{encoding} \{string\} \textbf{Default}: \texttt{utf8}
\item
  \texttt{callback} \{Function\}
\item
  Returns \{boolean\}
\end{itemize}

Sends a chunk of the body. This method can be called multiple times.

The \texttt{encoding} argument is only relevant when \texttt{chunk} is a
string. Defaults to \texttt{\textquotesingle{}utf8\textquotesingle{}}.

The \texttt{callback} argument is optional and will be called when this
chunk of data is flushed.

Returns \texttt{true} if the entire data was flushed successfully to the
kernel buffer. Returns \texttt{false} if all or part of the data was
queued in the user memory. The
\texttt{\textquotesingle{}drain\textquotesingle{}} event will be emitted
when the buffer is free again.

\subsection{\texorpdfstring{\texttt{http.METHODS}}{http.METHODS}}\label{http.methods}

\begin{itemize}
\tightlist
\item
  \{string{[}{]}\}
\end{itemize}

A list of the HTTP methods that are supported by the parser.

\subsection{\texorpdfstring{\texttt{http.STATUS\_CODES}}{http.STATUS\_CODES}}\label{http.status_codes}

\begin{itemize}
\tightlist
\item
  \{Object\}
\end{itemize}

A collection of all the standard HTTP response status codes, and the
short description of each. For example,
\texttt{http.STATUS\_CODES{[}404{]}\ ===\ \textquotesingle{}Not\ Found\textquotesingle{}}.

\subsection{\texorpdfstring{\texttt{http.createServer({[}options{]}{[},\ requestListener{]})}}{http.createServer({[}options{]}{[}, requestListener{]})}}\label{http.createserveroptions-requestlistener}

\begin{itemize}
\item
  \texttt{options} \{Object\}

  \begin{itemize}
  \tightlist
  \item
    \texttt{connectionsCheckingInterval}: Sets the interval value in
    milliseconds to check for request and headers timeout in incomplete
    requests. \textbf{Default:} \texttt{30000}.
  \item
    \texttt{headersTimeout}: Sets the timeout value in milliseconds for
    receiving the complete HTTP headers from the client. See
    \hyperref[serverheaderstimeout]{\texttt{server.headersTimeout}} for
    more information. \textbf{Default:} \texttt{60000}.
  \item
    \texttt{highWaterMark} \{number\} Optionally overrides all
    \texttt{socket}s' \texttt{readableHighWaterMark} and
    \texttt{writableHighWaterMark}. This affects \texttt{highWaterMark}
    property of both \texttt{IncomingMessage} and
    \texttt{ServerResponse}. \textbf{Default:} See
    \href{stream.md\#streamgetdefaulthighwatermarkobjectmode}{\texttt{stream.getDefaultHighWaterMark()}}.
  \item
    \texttt{insecureHTTPParser} \{boolean\} If set to \texttt{true}, it
    will use a HTTP parser with leniency flags enabled. Using the
    insecure parser should be avoided. See
    \href{cli.md\#--insecure-http-parser}{\texttt{-\/-insecure-http-parser}}
    for more information. \textbf{Default:} \texttt{false}.
  \item
    \texttt{IncomingMessage} \{http.IncomingMessage\} Specifies the
    \texttt{IncomingMessage} class to be used. Useful for extending the
    original \texttt{IncomingMessage}. \textbf{Default:}
    \texttt{IncomingMessage}.
  \item
    \texttt{joinDuplicateHeaders} \{boolean\} If set to \texttt{true},
    this option allows joining the field line values of multiple headers
    in a request with a comma (\texttt{,}) instead of discarding the
    duplicates. For more information, refer to
    \hyperref[messageheaders]{\texttt{message.headers}}.
    \textbf{Default:} \texttt{false}.
  \item
    \texttt{keepAlive} \{boolean\} If set to \texttt{true}, it enables
    keep-alive functionality on the socket immediately after a new
    incoming connection is received, similarly on what is done in
    {[}\texttt{socket.setKeepAlive({[}enable{]}{[},\ initialDelay{]})}{]}{[}\texttt{socket.setKeepAlive(enable,\ initialDelay)}{]}.
    \textbf{Default:} \texttt{false}.
  \item
    \texttt{keepAliveInitialDelay} \{number\} If set to a positive
    number, it sets the initial delay before the first keepalive probe
    is sent on an idle socket. \textbf{Default:} \texttt{0}.
  \item
    \texttt{keepAliveTimeout}: The number of milliseconds of inactivity
    a server needs to wait for additional incoming data, after it has
    finished writing the last response, before a socket will be
    destroyed. See
    \hyperref[serverkeepalivetimeout]{\texttt{server.keepAliveTimeout}}
    for more information. \textbf{Default:} \texttt{5000}.
  \item
    \texttt{maxHeaderSize} \{number\} Optionally overrides the value of
    \href{cli.md\#--max-http-header-sizesize}{\texttt{-\/-max-http-header-size}}
    for requests received by this server, i.e. the maximum length of
    request headers in bytes. \textbf{Default:} 16384 (16 KiB).
  \item
    \texttt{noDelay} \{boolean\} If set to \texttt{true}, it disables
    the use of Nagle's algorithm immediately after a new incoming
    connection is received. \textbf{Default:} \texttt{true}.
  \item
    \texttt{requestTimeout}: Sets the timeout value in milliseconds for
    receiving the entire request from the client. See
    \hyperref[serverrequesttimeout]{\texttt{server.requestTimeout}} for
    more information. \textbf{Default:} \texttt{300000}.
  \item
    \texttt{requireHostHeader} \{boolean\} If set to \texttt{true}, it
    forces the server to respond with a 400 (Bad Request) status code to
    any HTTP/1.1 request message that lacks a Host header (as mandated
    by the specification). \textbf{Default:} \texttt{true}.
  \item
    \texttt{ServerResponse} \{http.ServerResponse\} Specifies the
    \texttt{ServerResponse} class to be used. Useful for extending the
    original \texttt{ServerResponse}. \textbf{Default:}
    \texttt{ServerResponse}.
  \item
    \texttt{uniqueHeaders} \{Array\} A list of response headers that
    should be sent only once. If the header's value is an array, the
    items will be joined using \texttt{;}.
  \end{itemize}
\item
  \texttt{requestListener} \{Function\}
\item
  Returns: \{http.Server\}
\end{itemize}

Returns a new instance of
\hyperref[class-httpserver]{\texttt{http.Server}}.

The \texttt{requestListener} is a function which is automatically added
to the
\hyperref[event-request]{\texttt{\textquotesingle{}request\textquotesingle{}}}
event.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}

\CommentTok{// Create a local server to receive data from}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(\{}
    \DataTypeTok{data}\OperatorTok{:} \StringTok{\textquotesingle{}Hello World!\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \}))}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{8000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\CommentTok{// Create a local server to receive data from}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(\{}
    \DataTypeTok{data}\OperatorTok{:} \StringTok{\textquotesingle{}Hello World!\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \}))}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{8000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}

\CommentTok{// Create a local server to receive data from}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{()}\OperatorTok{;}

\CommentTok{// Listen to the request event}
\NormalTok{server}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}request\textquotesingle{}}\OperatorTok{,}\NormalTok{ (request}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(\{}
    \DataTypeTok{data}\OperatorTok{:} \StringTok{\textquotesingle{}Hello World!\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \}))}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{8000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\CommentTok{// Create a local server to receive data from}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{()}\OperatorTok{;}

\CommentTok{// Listen to the request event}
\NormalTok{server}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}request\textquotesingle{}}\OperatorTok{,}\NormalTok{ (request}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(\{}
    \DataTypeTok{data}\OperatorTok{:} \StringTok{\textquotesingle{}Hello World!\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \}))}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{8000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{\texttt{http.get(options{[},\ callback{]})}}{http.get(options{[}, callback{]})}}\label{http.getoptions-callback}

\subsection{\texorpdfstring{\texttt{http.get(url{[},\ options{]}{[},\ callback{]})}}{http.get(url{[}, options{]}{[}, callback{]})}}\label{http.geturl-options-callback}

\begin{itemize}
\tightlist
\item
  \texttt{url} \{string \textbar{} URL\}
\item
  \texttt{options} \{Object\} Accepts the same \texttt{options} as
  \hyperref[httprequestoptions-callback]{\texttt{http.request()}}, with
  the method set to GET by default.
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{http.ClientRequest\}
\end{itemize}

Since most requests are GET requests without bodies, Node.js provides
this convenience method. The only difference between this method and
\hyperref[httprequestoptions-callback]{\texttt{http.request()}} is that
it sets the method to GET by default and calls \texttt{req.end()}
automatically. The callback must take care to consume the response data
for reasons stated in
\hyperref[class-httpclientrequest]{\texttt{http.ClientRequest}} section.

The \texttt{callback} is invoked with a single argument that is an
instance of
\hyperref[class-httpincomingmessage]{\texttt{http.IncomingMessage}}.

JSON fetching example:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{http}\OperatorTok{.}\FunctionTok{get}\NormalTok{(}\StringTok{\textquotesingle{}http://localhost:8000/\textquotesingle{}}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \KeywordTok{const}\NormalTok{ \{ statusCode \} }\OperatorTok{=}\NormalTok{ res}\OperatorTok{;}
  \KeywordTok{const}\NormalTok{ contentType }\OperatorTok{=}\NormalTok{ res}\OperatorTok{.}\AttributeTok{headers}\NormalTok{[}\StringTok{\textquotesingle{}content{-}type\textquotesingle{}}\NormalTok{]}\OperatorTok{;}

  \KeywordTok{let}\NormalTok{ error}\OperatorTok{;}
  \CommentTok{// Any 2xx status code signals a successful response but}
  \CommentTok{// here we\textquotesingle{}re only checking for 200.}
  \ControlFlowTok{if}\NormalTok{ (statusCode }\OperatorTok{!==} \DecValTok{200}\NormalTok{) \{}
\NormalTok{    error }\OperatorTok{=} \KeywordTok{new} \BuiltInTok{Error}\NormalTok{(}\StringTok{\textquotesingle{}Request Failed.}\SpecialCharTok{\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                      \VerbatimStringTok{\textasciigrave{}Status Code: }\SpecialCharTok{$\{}\NormalTok{statusCode}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \} }\ControlFlowTok{else} \ControlFlowTok{if}\NormalTok{ (}\OperatorTok{!}\SpecialStringTok{/}\SpecialCharTok{\^{}}\SpecialStringTok{application}\SpecialCharTok{\textbackslash{}/}\SpecialStringTok{json/}\OperatorTok{.}\FunctionTok{test}\NormalTok{(contentType)) \{}
\NormalTok{    error }\OperatorTok{=} \KeywordTok{new} \BuiltInTok{Error}\NormalTok{(}\StringTok{\textquotesingle{}Invalid content{-}type.}\SpecialCharTok{\textbackslash{}n}\StringTok{\textquotesingle{}} \OperatorTok{+}
                      \VerbatimStringTok{\textasciigrave{}Expected application/json but received }\SpecialCharTok{$\{}\NormalTok{contentType}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \}}
  \ControlFlowTok{if}\NormalTok{ (error) \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(error}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;}
    \CommentTok{// Consume response data to free up memory}
\NormalTok{    res}\OperatorTok{.}\FunctionTok{resume}\NormalTok{()}\OperatorTok{;}
    \ControlFlowTok{return}\OperatorTok{;}
\NormalTok{  \}}

\NormalTok{  res}\OperatorTok{.}\FunctionTok{setEncoding}\NormalTok{(}\StringTok{\textquotesingle{}utf8\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
  \KeywordTok{let}\NormalTok{ rawData }\OperatorTok{=} \StringTok{\textquotesingle{}\textquotesingle{}}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}data\textquotesingle{}}\OperatorTok{,}\NormalTok{ (chunk) }\KeywordTok{=\textgreater{}}\NormalTok{ \{ rawData }\OperatorTok{+=}\NormalTok{ chunk}\OperatorTok{;}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}end\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \ControlFlowTok{try}\NormalTok{ \{}
      \KeywordTok{const}\NormalTok{ parsedData }\OperatorTok{=} \BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{parse}\NormalTok{(rawData)}\OperatorTok{;}
      \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(parsedData)}\OperatorTok{;}
\NormalTok{    \} }\ControlFlowTok{catch}\NormalTok{ (e) \{}
      \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(e}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;}
\NormalTok{    \}}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}error\textquotesingle{}}\OperatorTok{,}\NormalTok{ (e) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}Got error: }\SpecialCharTok{$\{}\NormalTok{e}\OperatorTok{.}\AttributeTok{message}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\CommentTok{// Create a local server to receive data from}
\KeywordTok{const}\NormalTok{ server }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{createServer}\NormalTok{((req}\OperatorTok{,}\NormalTok{ res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{writeHead}\NormalTok{(}\DecValTok{200}\OperatorTok{,}\NormalTok{ \{ }\StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\NormalTok{ \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{end}\NormalTok{(}\BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(\{}
    \DataTypeTok{data}\OperatorTok{:} \StringTok{\textquotesingle{}Hello World!\textquotesingle{}}\OperatorTok{,}
\NormalTok{  \}))}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\NormalTok{server}\OperatorTok{.}\FunctionTok{listen}\NormalTok{(}\DecValTok{8000}\NormalTok{)}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{\texttt{http.globalAgent}}{http.globalAgent}}\label{http.globalagent}

\begin{itemize}
\tightlist
\item
  \{http.Agent\}
\end{itemize}

Global instance of \texttt{Agent} which is used as the default for all
HTTP client requests.

\subsection{\texorpdfstring{\texttt{http.maxHeaderSize}}{http.maxHeaderSize}}\label{http.maxheadersize}

\begin{itemize}
\tightlist
\item
  \{number\}
\end{itemize}

Read-only property specifying the maximum allowed size of HTTP headers
in bytes. Defaults to 16 KiB. Configurable using the
\href{cli.md\#--max-http-header-sizesize}{\texttt{-\/-max-http-header-size}}
CLI option.

This can be overridden for servers and client requests by passing the
\texttt{maxHeaderSize} option.

\subsection{\texorpdfstring{\texttt{http.request(options{[},\ callback{]})}}{http.request(options{[}, callback{]})}}\label{http.requestoptions-callback}

\subsection{\texorpdfstring{\texttt{http.request(url{[},\ options{]}{[},\ callback{]})}}{http.request(url{[}, options{]}{[}, callback{]})}}\label{http.requesturl-options-callback}

\begin{itemize}
\tightlist
\item
  \texttt{url} \{string \textbar{} URL\}
\item
  \texttt{options} \{Object\}

  \begin{itemize}
  \tightlist
  \item
    \texttt{agent} \{http.Agent \textbar{} boolean\} Controls
    \hyperref[class-httpagent]{\texttt{Agent}} behavior. Possible
    values:

    \begin{itemize}
    \tightlist
    \item
      \texttt{undefined} (default): use
      \hyperref[httpglobalagent]{\texttt{http.globalAgent}} for this
      host and port.
    \item
      \texttt{Agent} object: explicitly use the passed in
      \texttt{Agent}.
    \item
      \texttt{false}: causes a new \texttt{Agent} with default values to
      be used.
    \end{itemize}
  \item
    \texttt{auth} \{string\} Basic authentication
    (\texttt{\textquotesingle{}user:password\textquotesingle{}}) to
    compute an Authorization header.
  \item
    \texttt{createConnection} \{Function\} A function that produces a
    socket/stream to use for the request when the \texttt{agent} option
    is not used. This can be used to avoid creating a custom
    \texttt{Agent} class just to override the default
    \texttt{createConnection} function. See
    \hyperref[agentcreateconnectionoptions-callback]{\texttt{agent.createConnection()}}
    for more details. Any
    \href{stream.md\#class-streamduplex}{\texttt{Duplex}} stream is a
    valid return value.
  \item
    \texttt{defaultPort} \{number\} Default port for the protocol.
    \textbf{Default:} \texttt{agent.defaultPort} if an \texttt{Agent} is
    used, else \texttt{undefined}.
  \item
    \texttt{family} \{number\} IP address family to use when resolving
    \texttt{host} or \texttt{hostname}. Valid values are \texttt{4} or
    \texttt{6}. When unspecified, both IP v4 and v6 will be used.
  \item
    \texttt{headers} \{Object\} An object containing request headers.
  \item
    \texttt{hints} \{number\} Optional
    \href{dns.md\#supported-getaddrinfo-flags}{\texttt{dns.lookup()}
    hints}.
  \item
    \texttt{host} \{string\} A domain name or IP address of the server
    to issue the request to. \textbf{Default:}
    \texttt{\textquotesingle{}localhost\textquotesingle{}}.
  \item
    \texttt{hostname} \{string\} Alias for \texttt{host}. To support
    \href{url.md\#urlparseurlstring-parsequerystring-slashesdenotehost}{\texttt{url.parse()}},
    \texttt{hostname} will be used if both \texttt{host} and
    \texttt{hostname} are specified.
  \item
    \texttt{insecureHTTPParser} \{boolean\} If set to \texttt{true}, it
    will use a HTTP parser with leniency flags enabled. Using the
    insecure parser should be avoided. See
    \href{cli.md\#--insecure-http-parser}{\texttt{-\/-insecure-http-parser}}
    for more information. \textbf{Default:} \texttt{false}
  \item
    \texttt{joinDuplicateHeaders} \{boolean\} It joins the field line
    values of multiple headers in a request with \texttt{,} instead of
    discarding the duplicates. See
    \hyperref[messageheaders]{\texttt{message.headers}} for more
    information. \textbf{Default:} \texttt{false}.
  \item
    \texttt{localAddress} \{string\} Local interface to bind for network
    connections.
  \item
    \texttt{localPort} \{number\} Local port to connect from.
  \item
    \texttt{lookup} \{Function\} Custom lookup function.
    \textbf{Default:}
    \href{dns.md\#dnslookuphostname-options-callback}{\texttt{dns.lookup()}}.
  \item
    \texttt{maxHeaderSize} \{number\} Optionally overrides the value of
    \href{cli.md\#--max-http-header-sizesize}{\texttt{-\/-max-http-header-size}}
    (the maximum length of response headers in bytes) for responses
    received from the server. \textbf{Default:} 16384 (16 KiB).
  \item
    \texttt{method} \{string\} A string specifying the HTTP request
    method. \textbf{Default:}
    \texttt{\textquotesingle{}GET\textquotesingle{}}.
  \item
    \texttt{path} \{string\} Request path. Should include query string
    if any. E.G.
    \texttt{\textquotesingle{}/index.html?page=12\textquotesingle{}}. An
    exception is thrown when the request path contains illegal
    characters. Currently, only spaces are rejected but that may change
    in the future. \textbf{Default:}
    \texttt{\textquotesingle{}/\textquotesingle{}}.
  \item
    \texttt{port} \{number\} Port of remote server. \textbf{Default:}
    \texttt{defaultPort} if set, else \texttt{80}.
  \item
    \texttt{protocol} \{string\} Protocol to use. \textbf{Default:}
    \texttt{\textquotesingle{}http:\textquotesingle{}}.
  \item
    \texttt{setHost} \{boolean\}: Specifies whether or not to
    automatically add the \texttt{Host} header. Defaults to
    \texttt{true}.
  \item
    \texttt{signal} \{AbortSignal\}: An AbortSignal that may be used to
    abort an ongoing request.
  \item
    \texttt{socketPath} \{string\} Unix domain socket. Cannot be used if
    one of \texttt{host} or \texttt{port} is specified, as those specify
    a TCP Socket.
  \item
    \texttt{timeout} \{number\}: A number specifying the socket timeout
    in milliseconds. This will set the timeout before the socket is
    connected.
  \item
    \texttt{uniqueHeaders} \{Array\} A list of request headers that
    should be sent only once. If the header's value is an array, the
    items will be joined using \texttt{;}.
  \end{itemize}
\item
  \texttt{callback} \{Function\}
\item
  Returns: \{http.ClientRequest\}
\end{itemize}

\texttt{options} in
\href{net.md\#socketconnectoptions-connectlistener}{\texttt{socket.connect()}}
are also supported.

Node.js maintains several connections per server to make HTTP requests.
This function allows one to transparently issue requests.

\texttt{url} can be a string or a
\href{url.md\#the-whatwg-url-api}{\texttt{URL}} object. If \texttt{url}
is a string, it is automatically parsed with
\href{url.md\#new-urlinput-base}{\texttt{new\ URL()}}. If it is a
\href{url.md\#the-whatwg-url-api}{\texttt{URL}} object, it will be
automatically converted to an ordinary \texttt{options} object.

If both \texttt{url} and \texttt{options} are specified, the objects are
merged, with the \texttt{options} properties taking precedence.

The optional \texttt{callback} parameter will be added as a one-time
listener for the
\hyperref[event-response]{\texttt{\textquotesingle{}response\textquotesingle{}}}
event.

\texttt{http.request()} returns an instance of the
\hyperref[class-httpclientrequest]{\texttt{http.ClientRequest}} class.
The \texttt{ClientRequest} instance is a writable stream. If one needs
to upload a file with a POST request, then write to the
\texttt{ClientRequest} object.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ http }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}
\ImportTok{import}\NormalTok{ \{ }\BuiltInTok{Buffer}\NormalTok{ \} }\ImportTok{from} \StringTok{\textquotesingle{}node:buffer\textquotesingle{}}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ postData }\OperatorTok{=} \BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(\{}
  \StringTok{\textquotesingle{}msg\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}Hello World!\textquotesingle{}}\OperatorTok{,}
\NormalTok{\})}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
  \DataTypeTok{hostname}\OperatorTok{:} \StringTok{\textquotesingle{}www.google.com\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{port}\OperatorTok{:} \DecValTok{80}\OperatorTok{,}
  \DataTypeTok{path}\OperatorTok{:} \StringTok{\textquotesingle{}/upload\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{method}\OperatorTok{:} \StringTok{\textquotesingle{}POST\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{headers}\OperatorTok{:}\NormalTok{ \{}
    \StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\OperatorTok{,}
    \StringTok{\textquotesingle{}Content{-}Length\textquotesingle{}}\OperatorTok{:} \BuiltInTok{Buffer}\OperatorTok{.}\FunctionTok{byteLength}\NormalTok{(postData)}\OperatorTok{,}
\NormalTok{  \}}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}STATUS: }\SpecialCharTok{$\{}\NormalTok{res}\OperatorTok{.}\AttributeTok{statusCode}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}HEADERS: }\SpecialCharTok{$\{}\BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(res}\OperatorTok{.}\AttributeTok{headers}\NormalTok{)}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{setEncoding}\NormalTok{(}\StringTok{\textquotesingle{}utf8\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}data\textquotesingle{}}\OperatorTok{,}\NormalTok{ (chunk) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}BODY: }\SpecialCharTok{$\{}\NormalTok{chunk}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}end\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}No more data in response.\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\NormalTok{req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}error\textquotesingle{}}\OperatorTok{,}\NormalTok{ (e) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}problem with request: }\SpecialCharTok{$\{}\NormalTok{e}\OperatorTok{.}\AttributeTok{message}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\CommentTok{// Write data to request body}
\NormalTok{req}\OperatorTok{.}\FunctionTok{write}\NormalTok{(postData)}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ http }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ postData }\OperatorTok{=} \BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(\{}
  \StringTok{\textquotesingle{}msg\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}Hello World!\textquotesingle{}}\OperatorTok{,}
\NormalTok{\})}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ options }\OperatorTok{=}\NormalTok{ \{}
  \DataTypeTok{hostname}\OperatorTok{:} \StringTok{\textquotesingle{}www.google.com\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{port}\OperatorTok{:} \DecValTok{80}\OperatorTok{,}
  \DataTypeTok{path}\OperatorTok{:} \StringTok{\textquotesingle{}/upload\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{method}\OperatorTok{:} \StringTok{\textquotesingle{}POST\textquotesingle{}}\OperatorTok{,}
  \DataTypeTok{headers}\OperatorTok{:}\NormalTok{ \{}
    \StringTok{\textquotesingle{}Content{-}Type\textquotesingle{}}\OperatorTok{:} \StringTok{\textquotesingle{}application/json\textquotesingle{}}\OperatorTok{,}
    \StringTok{\textquotesingle{}Content{-}Length\textquotesingle{}}\OperatorTok{:} \BuiltInTok{Buffer}\OperatorTok{.}\FunctionTok{byteLength}\NormalTok{(postData)}\OperatorTok{,}
\NormalTok{  \}}\OperatorTok{,}
\NormalTok{\}}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}STATUS: }\SpecialCharTok{$\{}\NormalTok{res}\OperatorTok{.}\AttributeTok{statusCode}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}HEADERS: }\SpecialCharTok{$\{}\BuiltInTok{JSON}\OperatorTok{.}\FunctionTok{stringify}\NormalTok{(res}\OperatorTok{.}\AttributeTok{headers}\NormalTok{)}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{setEncoding}\NormalTok{(}\StringTok{\textquotesingle{}utf8\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}data\textquotesingle{}}\OperatorTok{,}\NormalTok{ (chunk) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}BODY: }\SpecialCharTok{$\{}\NormalTok{chunk}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{  res}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}end\textquotesingle{}}\OperatorTok{,}\NormalTok{ () }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
    \BuiltInTok{console}\OperatorTok{.}\FunctionTok{log}\NormalTok{(}\StringTok{\textquotesingle{}No more data in response.\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{  \})}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\NormalTok{req}\OperatorTok{.}\FunctionTok{on}\NormalTok{(}\StringTok{\textquotesingle{}error\textquotesingle{}}\OperatorTok{,}\NormalTok{ (e) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(}\VerbatimStringTok{\textasciigrave{}problem with request: }\SpecialCharTok{$\{}\NormalTok{e}\OperatorTok{.}\AttributeTok{message}\SpecialCharTok{\}}\VerbatimStringTok{\textasciigrave{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\})}\OperatorTok{;}

\CommentTok{// Write data to request body}
\NormalTok{req}\OperatorTok{.}\FunctionTok{write}\NormalTok{(postData)}\OperatorTok{;}
\NormalTok{req}\OperatorTok{.}\FunctionTok{end}\NormalTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

In the example \texttt{req.end()} was called. With
\texttt{http.request()} one must always call \texttt{req.end()} to
signify the end of the request - even if there is no data being written
to the request body.

If any error is encountered during the request (be that with DNS
resolution, TCP level errors, or actual HTTP parse errors) an
\texttt{\textquotesingle{}error\textquotesingle{}} event is emitted on
the returned request object. As with all
\texttt{\textquotesingle{}error\textquotesingle{}} events, if no
listeners are registered the error will be thrown.

There are a few special headers that should be noted.

\begin{itemize}
\item
  Sending a `Connection: keep-alive' will notify Node.js that the
  connection to the server should be persisted until the next request.
\item
  Sending a `Content-Length' header will disable the default chunked
  encoding.
\item
  Sending an `Expect' header will immediately send the request headers.
  Usually, when sending `Expect: 100-continue', both a timeout and a
  listener for the \texttt{\textquotesingle{}continue\textquotesingle{}}
  event should be set. See RFC 2616 Section 8.2.3 for more information.
\item
  Sending an Authorization header will override using the \texttt{auth}
  option to compute basic authentication.
\end{itemize}

Example using a \href{url.md\#the-whatwg-url-api}{\texttt{URL}} as
\texttt{options}:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ options }\OperatorTok{=} \KeywordTok{new} \FunctionTok{URL}\NormalTok{(}\StringTok{\textquotesingle{}http://abc:xyz@example.com\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\KeywordTok{const}\NormalTok{ req }\OperatorTok{=}\NormalTok{ http}\OperatorTok{.}\FunctionTok{request}\NormalTok{(options}\OperatorTok{,}\NormalTok{ (res) }\KeywordTok{=\textgreater{}}\NormalTok{ \{}
  \CommentTok{// ...}
\NormalTok{\})}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

In a successful request, the following events will be emitted in the
following order:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  \texttt{\textquotesingle{}response\textquotesingle{}}

  \begin{itemize}
  \tightlist
  \item
    \texttt{\textquotesingle{}data\textquotesingle{}} any number of
    times, on the \texttt{res} object
    (\texttt{\textquotesingle{}data\textquotesingle{}} will not be
    emitted at all if the response body is empty, for instance, in most
    redirects)
  \item
    \texttt{\textquotesingle{}end\textquotesingle{}} on the \texttt{res}
    object
  \end{itemize}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\end{itemize}

In the case of a connection error, the following events will be emitted:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  \texttt{\textquotesingle{}error\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\end{itemize}

In the case of a premature connection close before the response is
received, the following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  \texttt{\textquotesingle{}error\textquotesingle{}} with an error with
  message
  \texttt{\textquotesingle{}Error:\ socket\ hang\ up\textquotesingle{}}
  and code \texttt{\textquotesingle{}ECONNRESET\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\end{itemize}

In the case of a premature connection close after the response is
received, the following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  \texttt{\textquotesingle{}response\textquotesingle{}}

  \begin{itemize}
  \tightlist
  \item
    \texttt{\textquotesingle{}data\textquotesingle{}} any number of
    times, on the \texttt{res} object
  \end{itemize}
\item
  (connection closed here)
\item
  \texttt{\textquotesingle{}aborted\textquotesingle{}} on the
  \texttt{res} object
\item
  \texttt{\textquotesingle{}error\textquotesingle{}} on the \texttt{res}
  object with an error with message
  \texttt{\textquotesingle{}Error:\ aborted\textquotesingle{}} and code
  \texttt{\textquotesingle{}ECONNRESET\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}} on the \texttt{res}
  object
\end{itemize}

If \texttt{req.destroy()} is called before a socket is assigned, the
following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  (\texttt{req.destroy()} called here)
\item
  \texttt{\textquotesingle{}error\textquotesingle{}} with an error with
  message
  \texttt{\textquotesingle{}Error:\ socket\ hang\ up\textquotesingle{}}
  and code \texttt{\textquotesingle{}ECONNRESET\textquotesingle{}}, or
  the error with which \texttt{req.destroy()} was called
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\end{itemize}

If \texttt{req.destroy()} is called before the connection succeeds, the
following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  (\texttt{req.destroy()} called here)
\item
  \texttt{\textquotesingle{}error\textquotesingle{}} with an error with
  message
  \texttt{\textquotesingle{}Error:\ socket\ hang\ up\textquotesingle{}}
  and code \texttt{\textquotesingle{}ECONNRESET\textquotesingle{}}, or
  the error with which \texttt{req.destroy()} was called
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\end{itemize}

If \texttt{req.destroy()} is called after the response is received, the
following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  \texttt{\textquotesingle{}response\textquotesingle{}}

  \begin{itemize}
  \tightlist
  \item
    \texttt{\textquotesingle{}data\textquotesingle{}} any number of
    times, on the \texttt{res} object
  \end{itemize}
\item
  (\texttt{req.destroy()} called here)
\item
  \texttt{\textquotesingle{}aborted\textquotesingle{}} on the
  \texttt{res} object
\item
  \texttt{\textquotesingle{}error\textquotesingle{}} on the \texttt{res}
  object with an error with message
  \texttt{\textquotesingle{}Error:\ aborted\textquotesingle{}} and code
  \texttt{\textquotesingle{}ECONNRESET\textquotesingle{}}, or the error
  with which \texttt{req.destroy()} was called
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}} on the \texttt{res}
  object
\end{itemize}

If \texttt{req.abort()} is called before a socket is assigned, the
following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  (\texttt{req.abort()} called here)
\item
  \texttt{\textquotesingle{}abort\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\end{itemize}

If \texttt{req.abort()} is called before the connection succeeds, the
following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  (\texttt{req.abort()} called here)
\item
  \texttt{\textquotesingle{}abort\textquotesingle{}}
\item
  \texttt{\textquotesingle{}error\textquotesingle{}} with an error with
  message
  \texttt{\textquotesingle{}Error:\ socket\ hang\ up\textquotesingle{}}
  and code \texttt{\textquotesingle{}ECONNRESET\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\end{itemize}

If \texttt{req.abort()} is called after the response is received, the
following events will be emitted in the following order:

\begin{itemize}
\tightlist
\item
  \texttt{\textquotesingle{}socket\textquotesingle{}}
\item
  \texttt{\textquotesingle{}response\textquotesingle{}}

  \begin{itemize}
  \tightlist
  \item
    \texttt{\textquotesingle{}data\textquotesingle{}} any number of
    times, on the \texttt{res} object
  \end{itemize}
\item
  (\texttt{req.abort()} called here)
\item
  \texttt{\textquotesingle{}abort\textquotesingle{}}
\item
  \texttt{\textquotesingle{}aborted\textquotesingle{}} on the
  \texttt{res} object
\item
  \texttt{\textquotesingle{}error\textquotesingle{}} on the \texttt{res}
  object with an error with message
  \texttt{\textquotesingle{}Error:\ aborted\textquotesingle{}} and code
  \texttt{\textquotesingle{}ECONNRESET\textquotesingle{}}.
\item
  \texttt{\textquotesingle{}close\textquotesingle{}}
\item
  \texttt{\textquotesingle{}close\textquotesingle{}} on the \texttt{res}
  object
\end{itemize}

Setting the \texttt{timeout} option or using the \texttt{setTimeout()}
function will not abort the request or do anything besides add a
\texttt{\textquotesingle{}timeout\textquotesingle{}} event.

Passing an \texttt{AbortSignal} and then calling \texttt{abort()} on the
corresponding \texttt{AbortController} will behave the same way as
calling \texttt{.destroy()} on the request. Specifically, the
\texttt{\textquotesingle{}error\textquotesingle{}} event will be emitted
with an error with the message
\texttt{\textquotesingle{}AbortError:\ The\ operation\ was\ aborted\textquotesingle{}},
the code \texttt{\textquotesingle{}ABORT\_ERR\textquotesingle{}} and the
\texttt{cause}, if one was provided.

\subsection{\texorpdfstring{\texttt{http.validateHeaderName(name{[},\ label{]})}}{http.validateHeaderName(name{[}, label{]})}}\label{http.validateheadernamename-label}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  \texttt{label} \{string\} Label for error message. \textbf{Default:}
  \texttt{\textquotesingle{}Header\ name\textquotesingle{}}.
\end{itemize}

Performs the low-level validations on the provided \texttt{name} that
are done when \texttt{res.setHeader(name,\ value)} is called.

Passing illegal value as \texttt{name} will result in a
\href{errors.md\#class-typeerror}{\texttt{TypeError}} being thrown,
identified by
\texttt{code:\ \textquotesingle{}ERR\_INVALID\_HTTP\_TOKEN\textquotesingle{}}.

It is not necessary to use this method before passing headers to an HTTP
request or response. The HTTP module will automatically validate such
headers.

Example:

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ \{ validateHeaderName \} }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}

\ControlFlowTok{try}\NormalTok{ \{}
  \FunctionTok{validateHeaderName}\NormalTok{(}\StringTok{\textquotesingle{}\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\} }\ControlFlowTok{catch}\NormalTok{ (err) \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err }\KeywordTok{instanceof} \BuiltInTok{TypeError}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{code}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}ERR\_INVALID\_HTTP\_TOKEN\textquotesingle{}}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}Header name must be a valid HTTP token [""]\textquotesingle{}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ \{ validateHeaderName \} }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\ControlFlowTok{try}\NormalTok{ \{}
  \FunctionTok{validateHeaderName}\NormalTok{(}\StringTok{\textquotesingle{}\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\} }\ControlFlowTok{catch}\NormalTok{ (err) \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err }\KeywordTok{instanceof} \BuiltInTok{TypeError}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{code}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}ERR\_INVALID\_HTTP\_TOKEN\textquotesingle{}}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}Header name must be a valid HTTP token [""]\textquotesingle{}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{\texttt{http.validateHeaderValue(name,\ value)}}{http.validateHeaderValue(name, value)}}\label{http.validateheadervaluename-value}

\begin{itemize}
\tightlist
\item
  \texttt{name} \{string\}
\item
  \texttt{value} \{any\}
\end{itemize}

Performs the low-level validations on the provided \texttt{value} that
are done when \texttt{res.setHeader(name,\ value)} is called.

Passing illegal value as \texttt{value} will result in a
\href{errors.md\#class-typeerror}{\texttt{TypeError}} being thrown.

\begin{itemize}
\tightlist
\item
  Undefined value error is identified by
  \texttt{code:\ \textquotesingle{}ERR\_HTTP\_INVALID\_HEADER\_VALUE\textquotesingle{}}.
\item
  Invalid value character error is identified by
  \texttt{code:\ \textquotesingle{}ERR\_INVALID\_CHAR\textquotesingle{}}.
\end{itemize}

It is not necessary to use this method before passing headers to an HTTP
request or response. The HTTP module will automatically validate such
headers.

Examples:

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ \{ validateHeaderValue \} }\ImportTok{from} \StringTok{\textquotesingle{}node:http\textquotesingle{}}\OperatorTok{;}

\ControlFlowTok{try}\NormalTok{ \{}
  \FunctionTok{validateHeaderValue}\NormalTok{(}\StringTok{\textquotesingle{}x{-}my{-}header\textquotesingle{}}\OperatorTok{,} \KeywordTok{undefined}\NormalTok{)}\OperatorTok{;}
\NormalTok{\} }\ControlFlowTok{catch}\NormalTok{ (err) \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err }\KeywordTok{instanceof} \BuiltInTok{TypeError}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{code} \OperatorTok{===} \StringTok{\textquotesingle{}ERR\_HTTP\_INVALID\_HEADER\_VALUE\textquotesingle{}}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}Invalid value "undefined" for header "x{-}my{-}header"\textquotesingle{}}
\NormalTok{\}}

\ControlFlowTok{try}\NormalTok{ \{}
  \FunctionTok{validateHeaderValue}\NormalTok{(}\StringTok{\textquotesingle{}x{-}my{-}header\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}om\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\} }\ControlFlowTok{catch}\NormalTok{ (err) \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err }\KeywordTok{instanceof} \BuiltInTok{TypeError}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{code} \OperatorTok{===} \StringTok{\textquotesingle{}ERR\_INVALID\_CHAR\textquotesingle{}}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}Invalid character in header content ["x{-}my{-}header"]\textquotesingle{}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{const}\NormalTok{ \{ validateHeaderValue \} }\OperatorTok{=} \PreprocessorTok{require}\NormalTok{(}\StringTok{\textquotesingle{}node:http\textquotesingle{}}\NormalTok{)}\OperatorTok{;}

\ControlFlowTok{try}\NormalTok{ \{}
  \FunctionTok{validateHeaderValue}\NormalTok{(}\StringTok{\textquotesingle{}x{-}my{-}header\textquotesingle{}}\OperatorTok{,} \KeywordTok{undefined}\NormalTok{)}\OperatorTok{;}
\NormalTok{\} }\ControlFlowTok{catch}\NormalTok{ (err) \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err }\KeywordTok{instanceof} \BuiltInTok{TypeError}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{code} \OperatorTok{===} \StringTok{\textquotesingle{}ERR\_HTTP\_INVALID\_HEADER\_VALUE\textquotesingle{}}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}Invalid value "undefined" for header "x{-}my{-}header"\textquotesingle{}}
\NormalTok{\}}

\ControlFlowTok{try}\NormalTok{ \{}
  \FunctionTok{validateHeaderValue}\NormalTok{(}\StringTok{\textquotesingle{}x{-}my{-}header\textquotesingle{}}\OperatorTok{,} \StringTok{\textquotesingle{}om\textquotesingle{}}\NormalTok{)}\OperatorTok{;}
\NormalTok{\} }\ControlFlowTok{catch}\NormalTok{ (err) \{}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err }\KeywordTok{instanceof} \BuiltInTok{TypeError}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{code} \OperatorTok{===} \StringTok{\textquotesingle{}ERR\_INVALID\_CHAR\textquotesingle{}}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} true}
  \BuiltInTok{console}\OperatorTok{.}\FunctionTok{error}\NormalTok{(err}\OperatorTok{.}\AttributeTok{message}\NormalTok{)}\OperatorTok{;} \CommentTok{// {-}{-}\textgreater{} \textquotesingle{}Invalid character in header content ["x{-}my{-}header"]\textquotesingle{}}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subsection{\texorpdfstring{\texttt{http.setMaxIdleHTTPParsers(max)}}{http.setMaxIdleHTTPParsers(max)}}\label{http.setmaxidlehttpparsersmax}

\begin{itemize}
\tightlist
\item
  \texttt{max} \{number\} \textbf{Default:} \texttt{1000}.
\end{itemize}

Set the maximum number of idle HTTP parsers.
